### 2022-12-26 paper.tex
Initial commit

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\usepackage{cleveref}

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

\begin{document}
\preprint{APS/123-QED}

\author{Vasily Postnicov\textsuperscript{1}}
\author{Marina Karsanina\textsuperscript{1}}
\author{Efim Lavrukhin\textsuperscript{1,2}}
\author{Dina Gafurova\textsuperscript{3}}
\author{Aleksey Khlyupin\textsuperscript{1}}
\author{Kirill Gerke\textsuperscript{1}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
  Lomonosov Moscow State University, Moscow, 119991, Russia}
\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}

\title{We did an amazing thing}

\begin{abstract}
  Here we are again.
\end{abstract}
\keywords {3D images; correlation functions; surface-surface function;
  surface-void function; image analysis; image scaling}

\maketitle

\section{Introduction}
\label{sec:intro}
AAA

\section{Definitions}
\label{sec:def}
Let $A$ be a set in Euclidean space $\mathbb{R}^n$. A function
$\chi_S(\mathbf{x})$ is called an indicator function for the set $A$ and is
defined as follows:
\begin{equation*}
  \chi_S(\bm{x}) = \left\{
  \begin{array}{ll}
    1 & \quad \bm{x} \in A \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}

Now define two disjoint sets in a homogeneous porous medium: a set of solid
phase $S$ and a set of void phase $V$. Surface-surface correlation function
$F_{ss}$ and surface-void correlation function $F_{sv}$ are defined as follows:
\begin{align}
  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
  \bm{r})| \rangle \label{eq:fss} \\
  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
  \bm{r}) \rangle \label{eq:fsv}
\end{align}
Here angles $\langle \dots \rangle$ denote ensemble average. For isotropic media
vector values $\bm{x}$ and $\bm{r}$ can be replaced with scalars, but in this
paper we will consider anisotropic media as well as isotropic.

More detailed information on surface correlation functions can be found in a
book of Salvatore Torquato\cite{Torquato_book}.

\section{Algorithm for computation of surface functions}
\label{sec:algo}
Here we briefly describe an algorithm for computation of surface-surface and
surface-void correlation functions for digital images of porous media. A more
detailed description can be found in a paper of Samarin
et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
correlation functions for all possible directions and correlation lengths. It
consists of two stages: edge detection stage and computation of
autocorrelation.

We give an image of porous medium in the form of two- or threedimensional bit
array $A$ as the input to our algorithm. In the first stage, we convolve the
input with high-pass filter to extract edges from the image. We use the
following filter kernel $H$ \textcolor{red}{Is there notation for 3x3x3
  ``matrices''?}:
\begin{align}
  H_{ij} &= \frac{1}{6} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -8 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-2d} \\
  H_{ijk} &= \frac{1}{18} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -24 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-3d}
\end{align}
Here symbol $;$ denotes concatenation along the third dimension. Edge extraction
is performed as follows:
\begin{align*}
  A'_{lm}  &= \left| \sum_i\sum_j A_{l-i, m-j}H_{ij} \right| \quad \text{for 2D} \\
  A'_{lmn} &= \left| \sum_i\sum_j\sum_k A_{l-i, m-j, n-k}H_{ijk} \right| \quad
  \text{for 3D}
\end{align*}
Therefore $A'$ has non-zero elements only in a small area around interface
between phases in $A$.

In the second stage we calculate autocorrelation for $A'$ and divide it by a
total number of elements in $A$:
\begin{align*}
  F_{{ss}_{lm}} &= \frac{1}{N} \sum_i \sum_j A'_{ij}A'_{i+l, j+m} \quad
  \text{for 2D} \\
  F_{{ss}_{lmn}} &= \frac{1}{N} \sum_i \sum_j \sum_k A'_{ijk}A'_{i+l, j+m, k+n}
  \quad \text{for 3D}
\end{align*}
Calculation of sums in the latter equations can be performed using the following
properties of Fourier transform:
\begin{equation*}
  F[f(x) \star f(x)] = F[f(x) * f(-x)] = \hat{f}(z)\overline{\hat{f}(z)} = |\hat{f}(z)|^2
\end{equation*}

All in all we get the following algorithm for calculation of $F_{ss}$ function:
\begin{algorithmic}[1]
  \Procedure{surfsurf}{$A$}
  \State $A' \gets A*H$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $\hat{A'} \gets F[A']$
  \Comment{Apply DFT to $A'$.}
  \State \textbf{return} $F^{-1}[ |\hat{A}|^2 / N]$
  \Comment{$N$ is a number of elements in $A$}
  \EndProcedure
\end{algorithmic}

Algorithm for surface-void function $F_{sv}$ is similar:
\begin{algorithmic}[1]
  \Procedure{surfvoid}{$A$}
  \State $A' \gets A*H$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $V \gets \chi_V(A)$
  \Comment{Apply an indicator function for void phase element-wise to $A$.}
  \State $\hat{A'} \gets F[A']$
  \Comment{Apply DFT to $A'$.}
  \State $\hat{V} \gets F[V]$
  \Comment{Apply DFT to $V$.}
  \State \textbf{return} $F^{-1}[ \hat{A}\overline{\hat{V}} / N]$
  \Comment{$N$ is a number of elements in $A$}
  \EndProcedure
\end{algorithmic}

A result $R_{ij}$ (resp. $R_{ijk}$) of either of two algorithms is an array of
the same shape as $A$ which contains values of correlation function for the
vector $r = (i, j)$ (resp. $r = (i, j, k)$). This result can be averaged over
all directions if needed.

\section{Problem of verification}
\label{sec:verify}
In paper\textcolor{red}{our paper} we tested these algorithms against known
analytic solutions. Although we obtained acceptable results in the cases of
overlapping balls and disks, we were not sure if our algorithm performs good in
general and searched for more test cases. Here we present one such case:
two-dimensional sets with smooth boundary.

\subsection{Surface-surface function in two-dimensional case}
\label{sec:fss-2d}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/Fss.png}
  \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
    between solid and void phases is a solid black curve. This interface
    translated by the vector $\bm{r}$ is show as a red solid curve. Support of
    $f_\Gamma(\bm{x}; \Delta)$ is a dashed ring. Shaded regions contribute to
    the surface-surface function.}
  \label{fig:Fss-explained}
\end{figure}
Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
the sense that the boundary has a tangent line at every point. Now we introduce
a function $f_\Gamma(\bm{x}; \Delta)$:
\begin{equation*}
  f_\Gamma(\bm{x}; \Delta) = \left\{
  \begin{array}{ll}
    1/\epsilon & \quad \rho(\bm{x}, \Gamma) < \Delta \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
boundary $\Gamma$.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fss-zoomed.png}
  \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
    translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
  \label{fig:fss-zoomed}
\end{figure}
Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
\begin{align*}
  F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
  + \bm{r}; \Delta) dx dy \\
  &= \sum_{k=1}^N S_k/\Delta^2
\end{align*}
Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
vector $\bm{r}$ and $S_k$ is a surface of each such intersection (see
\cref{fig:Fss-explained}).
When $\Delta$ tends to zero, the boundary at the point of intersection can
be replaced with a tangent line at the point of intersection
(\cref{fig:fss-zoomed}). We get an expression for a surface of
intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
acute angle between tangent lines. Hence, we get the following equation:
\begin{equation}
  F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
\end{equation}
It's easy to show that
$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_S(\bm{x})|$
and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.

\subsection{Dual numbers and automatic differentiation}
\label{sec:dual}
A ring of dual numbers $D$ is a set of pairs of real numbers $(x, y)$ with two
binary operations: $+$ (addition) and $\cdot$ (multiplication) where
multiplication work according to the following law:
\begin{equation*}
  (x_1, y_1)\cdot(x_2, y_2) = (x_1x_2, x_1y_2 + y_1x_2)
\end{equation*}
It's easy to see that $D$ is commutative.

It's useful to introduce an imaginary unit $\varepsilon$ and write a dual number
$(x, y)$ as $x + y\varepsilon$. As you can see from multiplication law,
$1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
integral domain and division is not defined for all dual numbers with exception
of $0$. Namely it's defined only if divisor has non-zero real part:
\begin{align*}
  \frac{a+b\varepsilon}{c+d\varepsilon} &=
  \frac{(a+b\varepsilon)(c-d\varepsilon)}{(c+d\varepsilon)(c-d\varepsilon)} \\
  &= \frac{ac-ad\varepsilon+bc\varepsilon}{c^2} \\
  &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
\end{align*}

Power function $(a + b\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined
using binomial formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
\begin{equation*}
  (a + b\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} a^k (b\varepsilon)^{n-k} =
  a^n + n a^{n-1} b \varepsilon
\end{equation*}
This formula can be extended on $n \in \mathbb{Q}$ as well.

Elementary functions can be extended to dual numbers using Taylor series. For
example, the exponent function is extended as:
\begin{align*}
  e^{a + b\varepsilon} &= \sum_{k=0}^{\infty}\frac{(a + b\varepsilon)^k}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k + bka^{k-1}\varepsilon}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}
  \frac{a^{k-1}}{(k-1)!} \\
  &= e^a + e^ab\varepsilon
\end{align*}

Here are some basic rules for working with dual numbers:
\begin{itemize}
\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + b) + (c + d)\varepsilon$
\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
\end{itemize}

It's easy to see, that there is a connection between dual numbers and
differentiation. Indeed, if functions $f(x)$ and $g(x)$
are differentiable at the point $a$ and $h(x) = f(x)g(x)$ is their product then
$h(a + b\varepsilon) = h(a) + b\varepsilon(f'(a)g(a) + f(a)g'(a))$.
If $h(x) = f(x)/g(x)$ and $g(a) \ne 0$ then
$h(a + b\varepsilon) = h(a) + b\varepsilon\frac{f'(a)g(a) - f(a)g'(a)}{f^2(a)}$.
More generally, we can see that $f(a + b\varepsilon) = f(a) + bf'(a)\varepsilon$.

So, using dual numbers we can compute two values at once: one of the function at
the point $x = a$ and the other of its derivative at this point:
$f(a + \varepsilon) = f(a) + \varepsilon f'(a)$. Also we can compute a partial
derivative of a multivariate function. For example:
\begin{align*}
  \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
  b) \\
  \frac{\partial}{\partial y} f(x, y) \vert_{x = a, y = b} &= f(a, b +
  \varepsilon)
\end{align*}

\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
\label{sec:cool-algo}
Here we examine two-dimensional sets with smooth boundary described in
\cref{sec:fss-2d} more closely. Suppose a set $S$ is defined as
$S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some function
differentiable in points where $f(x, y) = T$ and $T$ is some threshold. Let's
calculate surface-surface function for this set at a point $(a, b)$. We find all
intersections between a boundary $\Gamma$ and its translated version by solving a
system of equations
\begin{equation*}
  \left\{
  \begin{array}{l}
    f(x, y) = T \\
    f(x-a, y-b) = T    
  \end{array}
  \right.
\end{equation*}
which can be replaced by one equation
\begin{equation}
  (f(x, y) - T)^2 + (f(x-a, y-b) - T)^2 = 0 \label{eq:inter}
\end{equation}
We denote a set of solutions of this equation as $X$. For every $\bm{x}_i \in X$
we find an angle $\phi_i$ between a normal to the boundary and a normal to
the translated boundary as
\begin{equation}
  \cos \phi_i = \frac{(\nabla f(x,y) \vert_{\bm{x}_i}, \nabla f(x-a,y-b)
    \vert_{\bm{x}_i})}{|\nabla f(x,y) \vert_{\bm{x}_i}| |\nabla f(x-a,y-b)
    \vert_{\bm{x}_i}|} \label{eq:angle}
\end{equation}
Here $(\cdot, \cdot)$ denotes a scalar product. Gradient of $f$ at the point
$x_i$ can be found using automatic differentiation and dual numbers described in
\cref{sec:dual}. Note that acute angle between tangent lines equals to acute
angle between normals, therefore we can find correlation function $F_{ss}(a, b)$
using the following formula:
\begin{equation}
  F_{ss}(a, b) = \sum_i \frac{1}{\sqrt{1 - \cos^2 \phi_i}} \label{eq:fss-method}
\end{equation}

The algorithm of calculating $F_{ss}(a, b)$ is the following:
\begin{enumerate}
\item Find $X$ which is a set of soulutions of \cref{eq:inter}.
\item For all points in $X$ find cosines between normals to the boundaries using
  \cref{eq:angle}.
\item Calculate $F_{ss}(a, b)$ using \cref{eq:fss-method}.
\end{enumerate}

The set $X$ can be found by firstly evaluating $f(x, y)$ in some regular grid
searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \varepsilon$ 
and $|f(x_i - a, y_i - b) - T| < \varepsilon$ for some positive $\varepsilon$
and then using these points as starting points for some gradient descent based
algorithm like ADAM to solve \cref{eq:inter}.

\section{Examples of two-dimensional sets with smooth boundary}
\label{seq:examples}
\subsection{A square}
Let's define a function $f(x, y) = \max(|x|, |y|)$. A set $f(x, y) \le T$ is a
square with side $2T$. The function $f$ is differentiable at all points where
$f(x, y) = T$ with exception of points $(-T, -T)$, $(-T, T)$, $(T, -T)$ and
$(T, T)$. The surface-surface correlation function for a square is equal to:
\begin{equation*}
  F_{ss}(x, y) = \left\{
  \begin{array}{ll}
    2 & \quad \max(|x|, |y|) < T \ \text{and}\ x\ne0, y\ne0 \\
    0 & \quad \max(|x|, |y|) > T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
this case the algorithm described in \cref{sec:algo} gives a correct result in
any point which is few pixels away from where $F_{ss}$ is undefined.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fss-square.png}
  \caption[]{$F_{ss}$ function for a square with side $T$. The function is
    undefined along red segments. Its value is $2$ inside a shaded area and $0$
    outside.}
  \label{fig:fss-square}
\end{figure}

\subsection{A disk}
If we define $f(x, y) = x^2 + y^2$ then an inequation $f(x, y) \le R^2$ defines
a disk of radius $R$ with center at the origin. In this case $F_{ss}$ depends
only on distance $r$ from the origin:
\begin{equation*}
  F_{ss}(r) = \left\{
  \begin{array}{ll}
    \frac{4R^2}{r\sqrt{4R^2-r^2}} & \quad r < 2R \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A comparison of the algorithm described in \cref{sec:algo} applied to images
with different resolution with a theory is shown on \cref{fig:fss-disk-3x3}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-3x3.png}
    \label{fig:fss-disk-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-5x5.png}
    \label{fig:fss-disk-5x5}}
  \caption[]{Plot of surface-surface function for a disk with radius
    $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
    $3100\times 3100$.}
  \label{fig:fss-disk}
\end{figure*}

\subsection{Gaussian mixture}
\label{sec:gauss}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\textcolor{red}{insert picture}. We can use the algorithm developed in
\cref{sec:cool-algo} to compute precise values of $F_{ss}$ for this blob and
compare them with values obtained by using the fast algorithm in section
\cref{sec:algo}. The result of this comparison is on \textcolor{red}{Insert
  picture}. The maximal relative error for values obtained with the fast
algorithm is \textcolor{red}{insert value}.

\section{Improvement of the fast algorithm}
\label{sec:improvement}
Take two 2D images like the ones on \textcolor{red}{insert image}. The
boundaries between black and white cross each other at the angle $\phi$. We
apply the filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
element-wise and sum all elements of the product. An obtained value must
approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
surface-surface function. With filter described in \cref{sec:algo} we get the
following picture \textcolor{red}{insert picture}. We see that $H$ approximates
$1/\sin \phi$ not very good.

Now, let's try a wider filter $H'$:
\begin{align}
  H'_{ij} &= \frac{1}{30} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -24 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-2d} \\
  H'_{ijk} &= \frac{1}{150} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -124 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-3d}
\end{align}
With this filter we get a different picture \textcolor{red}{insert image}. A
comparison of the fast algorithm with a wider filter kernel with a precise
calculation for a ``blob'' show in \cref{sec:gauss} is show on
\textcolor{red}{insert image}. The maximal relative error is reduced to
\textcolor{red}{insert image}.

\section{Results}
\textcolor{red}{insert many pictures, also with different quality}

Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
$H$ has faster convergence with increase of image resolution. Our
acceptance criterion developed in \textcolor{red}{cite our paper again} works
also for $H'$, but sometimes it's possible to calculate a poor estimate of
$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
of discontinuity of $F_{ss}$ as can be seen on \textcolor{red}{reference a
  picture where $F_{ss}$ is discontinuous}.

\section{Conclusion}
In this paper we develop an algorithm for precise calculation of surface-surface
correlation function for two-dimensional sets with smooth boundary and checked
our fast algorithm using these new cases. The fast algorithm was improved using
a wider filter $H'$.

\end{document}

### 2022-12-26 scripts/calc-disk.jl

@@ -1,0 +1,37 @@
+module Torquatsky
+using DelimitedFiles
+import CorrelationFunctions.Map as M
+import CorrelationFunctions.Utilities as U
+export do_it!
+
+function draw_ball(s, r)
+    array = falses(s)
+	center = @. (s ÷ 2) |> floor |> Int
+
+    for idx in CartesianIndices(array)
+        dist = sum((Tuple(idx) .- center) .^ 2)
+        if dist <= r^2
+            array[idx] = true
+        end
+    end
+
+    return array
+end
+
+function do_it!()
+    R = 0.0334
+    flt = U.EdgeFilter(U.BCPeriodic(), U.Kernel3x3())
+    for side in 100:100:3100
+        disk = draw_ball((side, side), R*side)
+        println(side)
+        println(U.lowfreq_energy_ratio(disk))
+
+        ss = M.surfsurf(disk, false; periodic = true, filter = flt) |> M.average_directions
+
+        open("disks-$(side)-we-ss.dat", "w") do out
+            writedlm(out, ss)
+        end
+    end
+end
+
+end

### 2022-12-26 scripts/plot-ss.py

@@ -1,0 +1,25 @@
+#!/usr/bin/env python
+import numpy as np
+import matplotlib.pyplot as plt
+
+def ss(x, R):
+    return np.where(x < 2*R, 4*R**2/(x * np.sqrt(4*R**2 - x**2)), 0)
+
+legend = []
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+
+for side in range(100, 3200, 500):
+    data = np.loadtxt('disks-%i-we-ss.dat' % side)
+    plt.plot(np.linspace(0, 0.5, data.size), data * side**2, linewidth = (side == 3100 and 1.2 or 0.5))
+    legend = legend + [str(side)]
+
+xs = np.linspace(0, 0.5, 1000)
+plt.xlim([0, 0.1])
+plt.ylim([0, 4])
+plt.plot(xs, ss(xs, 0.0334), linewidth = 1.2)
+plt.ticklabel_format(axis = "x", scilimits = (0, 0))
+plt.legend(legend + ['Theory'])
+plt.xlabel('Correlation length $r$, m')
+plt.ylabel('$F_{ss}(r)$, $m^{-2}$')
+plt.savefig('../images/fss-disk-3x3.png')

### 2022-12-28 paper.tex
More images

@@
 \label{sec:gauss}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth, frame]{images/blob.png}
+  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
+    which consists of four Gaussian functions. White area is where
+    $f(x,y) \le 3$.}
+  \label{fig:blob}
+\end{figure}
 Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
@@
 Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
-\textcolor{red}{insert picture}. We can use the algorithm developed in
-\cref{sec:cool-algo} to compute precise values of $F_{ss}$ for this blob and
-compare them with values obtained by using the fast algorithm in section
-\cref{sec:algo}. The result of this comparison is on \textcolor{red}{Insert
-  picture}. The maximal relative error for values obtained with the fast
-algorithm is \textcolor{red}{insert value}.
+\cref{fig:blob}. We can use the algorithm developed in \cref{sec:cool-algo} to
+compute precise values of $F_{ss}$ for this blob and compare them with values
+obtained by using the fast algorithm in section \cref{sec:algo}. The result of
+this comparison is on \cref{fig:fss-blob}. The maximal relative error for values
+obtained with the fast algorithm is \textcolor{red}{insert value}.
+\begin{figure*}[!pt]
+  \centering
+  \subfigure[$3\times 3$ kernel $H$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
+    \label{fig:fss-blob-3x3}}
+  \hfill
+  \subfigure[$5\times 5$ kernel $H'$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
+    \label{fig:fss-blob-5x5}}
+  \caption[]{Plot of the surface-surface function for the blob on
+    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
+    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
+    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
+  \label{fig:fss-blob}
+\end{figure*}
 
@@
 \label{sec:improvement}
-Take two 2D images like the ones on \textcolor{red}{insert image}. The
-boundaries between black and white cross each other at the angle $\phi$. We
-apply the filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/experiment-setup.png}
+  \caption[]{Left, center: images $A$ and $B$ used in the experiment described
+    in \cref{sec:improvement}. Right: Interfaces between phases are line
+    segments which intersect each other at angle $\phi$. Shaded area is where
+    $(H*A)\cdot(H*B)$ has non-zero values.}
+  \label{fig:experiment-setup}
+\end{figure}
+Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
+between black and white cross each other at the angle $\phi$. We apply the
+filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
 element-wise and sum all elements of the product. An obtained value must
 approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
-surface-surface function. With filter described in \cref{sec:algo} we get the
-following picture \textcolor{red}{insert picture}. We see that $H$ approximates
+surface-surface function. With filter described in \cref{sec:algo} we get a
+picture as on \cref{fig:angles-3x3}. We see that $H$ approximates
 $1/\sin \phi$ not very good.
@@
 \end{align}
-With this filter we get a different picture \textcolor{red}{insert image}. A
+With this filter we get a different picture (\cref{fig:angles-5x5}). A
 comparison of the fast algorithm with a wider filter kernel with a precise
 calculation for a ``blob'' show in \cref{sec:gauss} is show on
-\textcolor{red}{insert image}. The maximal relative error is reduced to
+\cref{fig:fss-blob-5x5}. The maximal relative error is reduced to
 \textcolor{red}{insert image}.
+\begin{figure*}[!pt]
+  \centering
+  \subfigure[$3\times 3$ kernel $H$]{
+    \includegraphics[width=0.45\linewidth]{images/angles-3x3.png}
+    \label{fig:angles-3x3}}
+  \hfill
+  \subfigure[$5\times 5$ kernel $H'$]{
+    \includegraphics[width=0.45\linewidth]{images/angles-5x5.png}
+    \label{fig:angles-5x5}}
+  \caption[]{dfdfdfdf}
+  \label{fig:angles}
+\end{figure*}
 

### 2022-12-28 scripts/angles.jl

@@ -1,0 +1,22 @@
+import CorrelationFunctions.Utilities as U
+using DelimitedFiles
+
+f(x, y, ny, nx) = nx * x + ny * y
+
+function f(α; n, method)
+    x = range(-1, 1, length=n)
+    A = [f(x, y, sincos(α)...) > 0 for x in x, y in x]
+    An = U.extract_edges(A, method)
+
+    B = [f(x, y, sincos(0)...) > 0 for x in x, y in x]
+    Bn = U.extract_edges(B, method)
+
+    return sum(An .* Bn)
+end
+
+ϵ = 0.1
+αs = (0+ϵ):0.001:(π-ϵ)
+approx = f.(αs; n = 400, method = U.EdgeFilter(U.BCReflect(), U.Kernel5x5()))
+open("angles-5x5.dat", "w") do out
+    writedlm(out, hcat(αs, approx))
+end

### 2022-12-28 scripts/calc-blob.jl

@@ -1,0 +1,13 @@
+using NPZ
+using FileIO
+using Images
+using FFTW
+import CorrelationFunctions.Map as M
+import CorrelationFunctions.Utilities as U
+
+flt = U.EdgeFilter(U.BCPeriodic(), U.Kernel3x3())
+for side in 500:500:3000
+    data = load("field-$(side).pbm") .|> Gray |> BitArray;
+    npzwrite("field-ss-$(side).npy",
+             fftshift(M.surfsurf(data, false; periodic = true, filter = flt)) * side^2)
+end

### 2022-12-28 scripts/compare-blob.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp2d
+
+data_def = np.load('ss-precise.npy')
+legend = []
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+phi = np.arctan(data_def[:,1]/ data_def[:,2]) + np.pi/2
+
+for side in range(500, 3500, 500):
+    data_julia = np.load('field-ss-%i.npy' % side)
+    x = np.linspace(-1, 1, side)
+    f = interp2d(x, x, data_julia)
+    slice_julia = []
+    for n in range(data_def.shape[0]):
+        slice_julia = slice_julia + [f(data_def[n, 2], data_def[n, 1])[0]]
+    slice_julia = np.array(slice_julia)
+    plt.plot(phi, slice_julia, linewidth = (side == 3000 and 1.2 or 0.5))
+    legend = legend + [str(side)]
+    err = (slice_julia - data_def[:, 0])**2
+    print(side, np.sqrt(sum(err)))
+
+plt.plot(phi, data_def[:, 0], linewidth = 1.2)
+plt.xlabel('$\phi$')
+plt.ylabel('$F_{ss}(R, \phi)$')
+plt.ylim([1,13])
+plt.legend(legend + ['Precise'])
+plt.savefig('../images/fss-blob-3x3.png')

### 2022-12-28 scripts/plot-angles.py

@@ -1,0 +1,16 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = np.loadtxt('angles-5x5.dat')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+
+plt.plot(data[:,0], data[:,1])
+plt.plot(data[:,0], 1/np.sin(data[:,0]))
+plt.legend(["Approximation with filter $H'$", 'Exact'])
+plt.xlabel('$\phi$')
+plt.ylabel('$1/\sin \phi$')
+plt.savefig('../images/angles-5x5.png')

### 2023-01-10 paper.tex
Add another example (ellipses)

@@
 \label{sec:verify}
-In paper\textcolor{red}{our paper} we tested these algorithms against known
+In paper \textcolor{red}{our paper} we tested these algorithms against known
 analytic solutions. Although we obtained acceptable results in the cases of
@@
   \centering
-  \includegraphics[width=\linewidth]{images/Fss.png}
+  \includegraphics[width=0.8\linewidth]{images/Fss.png}
   \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
@@
   \centering
-  \includegraphics[width=\linewidth]{images/fss-zoomed.png}
+  \includegraphics[width=0.8\linewidth]{images/fss-zoomed.png}
   \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
@@
 \label{seq:examples}
+In this section we will provide few examples of sets for which the developed
+precise algorithm is applicable and compare the surface-surface function
+calculated with the fast algorithm (\cref{sec:algo}) with results of the new
+algorithm. We will use the filter $H$ (\ref{eq:filter-3x3-2d}) for edge
+detection along with a new filter $H'$ (\ref{eq:filter-5x5-2d}) described in
+\cref{sec:improvement}.
+
 \subsection{A square}
@@
   \centering
-  \includegraphics[width=\linewidth]{images/fss-square.png}
+  \includegraphics[width=0.8\linewidth]{images/fss-square.png}
   \caption[]{$F_{ss}$ function for a square with side $T$. The function is
@@
   \centering
-  \includegraphics[width=\linewidth, frame]{images/blob.png}
+  \includegraphics[width=0.8\linewidth, frame]{images/blob.png}
   \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
@@
 obtained by using the fast algorithm in section \cref{sec:algo}. The result of
-this comparison is on \cref{fig:fss-blob}. The maximal relative error for values
-obtained with the fast algorithm is \textcolor{red}{insert value}.
+this comparison is on \cref{fig:fss-blob}.
 \begin{figure*}[!pt]
@@
 
+\subsection{Ellipses}
+\label{sec:ellipses}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth, frame]{images/ellipses.png}
+  \caption[]{An example of generated ellipses.}
+  \label{fig:ellipses}
+\end{figure}
+Take $N$ random values $a_i$, $b_i$, $c_i$, $x^c_i$ and $y^c_i$ and define
+\begin{equation*}
+  f_i(x, y) = a_i(x-x^c_i)^2 + b(x-x^c_i)(y-y^c_i) + c_i(y-y^c_i)^2
+\end{equation*}
+with $a_ic_i - b_i^2 > 0$. Inequation
+\begin{equation*}
+  \min_i f_i(x, y) < A^2
+\end{equation*}
+defines $N$ ellipses like those which can be seen on \cref{fig:ellipses}. A
+comparison between two algorithms is on \cref{fig:fss-ellipses}.
+\begin{figure*}[!pt]
+  \centering
+  \subfigure[$3\times 3$ kernel $H$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-3x3.png}
+    \label{fig:fss-ellipses-3x3}}
+  \hfill
+  \subfigure[$5\times 5$ kernel $H'$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-5x5.png}
+    \label{fig:fss-ellipses-5x5}}
+  \caption[]{Plot of the surface-surface function for ellipses on
+    \cref{fig:ellipses}. Values of $F_{ss}$ were calculated in semi-circle with
+    radius $R = 0.1$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
+    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
+  \label{fig:fss-ellipses}
+\end{figure*}
+
 \section{Improvement of the fast algorithm}
@@
   \centering
-  \includegraphics[width=\linewidth]{images/experiment-setup.png}
+  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
   \caption[]{Left, center: images $A$ and $B$ used in the experiment described
@@
 comparison of the fast algorithm with a wider filter kernel with a precise
-calculation for a ``blob'' show in \cref{sec:gauss} is show on
-\cref{fig:fss-blob-5x5}. The maximal relative error is reduced to
-\textcolor{red}{insert image}.
+calculation for a ``blob'' described in \cref{sec:gauss} is show on
+\cref{fig:fss-blob-5x5}. A case with ellipses from \cref{sec:ellipses} is on
+\cref{fig:fss-ellipses-5x5}.
 \begin{figure*}[!pt]
@@
     \label{fig:angles-5x5}}
-  \caption[]{dfdfdfdf}
+  \caption[]{Estimation of $1/\sin\phi$ where $\phi$ is the angle between
+    tangent lines to the interface by filters $H$ and $H'$.}
   \label{fig:angles}
@@
 \section{Results}
-\textcolor{red}{insert many pictures, also with different quality}
+With the new filter calculation of $F_{ss}$ becomes more precise, even for
+three-dimensional images. This can be seen in comparison with theoretical values
+for known cases like the one of overlapping balls \textcolor{red}{insert plot}.
 
@@
 $F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
-of discontinuity of $F_{ss}$ as can be seen on \textcolor{red}{reference a
-  picture where $F_{ss}$ is discontinuous}.
+of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
 

### 2023-01-12 paper.tex
Describe 3D case

@@
 \section{Results}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/ball-3d-ss.png}
+  \caption[]{Surface-surface function calculated for a three-dimensional ball
+    with radius $R = 0.24$ using filters $H$ and $H'$. Theoretical curve is
+    provided for a comparison. Image dimensions are $450 \times 450 \times 450$.}
+  \label{fig:fss-ball}
+\end{figure}
 With the new filter calculation of $F_{ss}$ becomes more precise, even for
 three-dimensional images. This can be seen in comparison with theoretical values
-for known cases like the one of overlapping balls \textcolor{red}{insert plot}.
+for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
+of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
+theoretical curve. It can be verified that filter $H'$ is better indeed by
+calculating
+\begin{equation*}
+  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
+      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
+\end{equation*}
+where $x_i$ belong to a set
+$(\varepsilon, 2R - \varepsilon) \cup (2R + \varepsilon, 1)$ (here we assume
+image dimensions to be $1 \times 1 \times 1$ length units). Taking
+$\varepsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
+for filter $H'$.
 

### 2023-01-12 scripts/ball.py

@@ -1,0 +1,39 @@
+#!/usr/bin/env python
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+data3 = np.loadtxt('ball-3x3.dat')
+data5 = np.loadtxt('ball-5x5.dat')
+
+def ss(x, R):
+    return np.where(x < 2*R, 2*np.pi*R**2/x, 0)
+
+def sv(x, R):
+    return np.where(x < 2*R, np.pi*R*x + 2*np.pi*R**2, 4*np.pi*R**2)
+
+
+R = 0.24
+
+x = np.linspace(0.01, 0.5, 1000)
+th = ss(x, R)
+d3i = interp1d(np.linspace(0, 0.5, data3.size), data3 * 450**2)
+d3s = d3i(x)
+print(np.sum((d3s - th)**2) / np.sum(th**2))
+d5i = interp1d(np.linspace(0, 0.5, data5.size), data5 * 450**2)
+d5s = d5i(x)
+print(np.sum((d5s - th)**2) / np.sum(th**2))
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+
+x = np.linspace(0, 0.5, 1000)
+plt.plot(np.linspace(0, 0.5, data3.size), data3 * 450**2, 'b', linewidth = 1.2)
+plt.plot(np.linspace(0, 0.5, data5.size), data5 * 450**2, 'g', linewidth = 1.2)
+plt.plot(x, ss(x, R), 'r', linewidth = 1.2)
+plt.ylim([0, 10])
+plt.xlim([0.03, 0.5])
+plt.xlabel('$r$')
+plt.ylabel('$F_{ss}(r)$')
+plt.legend(['Filter 3x3', 'Filter 5x5', 'Therory'])
+plt.savefig('../images/ball-3d-ss.png')

### 2023-01-12 paper.tex
Fix some errors, typos and so on

@@
 Let $A$ be a set in Euclidean space $\mathbb{R}^n$. A function
-$\chi_S(\mathbf{x})$ is called an indicator function for the set $A$ and is
+$\chi_A(\mathbf{x})$ is called an indicator function for the set $A$ and is
 defined as follows:
 \begin{equation*}
-  \chi_S(\bm{x}) = \left\{
+  \chi_A(\bm{x}) = \left\{
   \begin{array}{ll}
@@
 
-We give an image of porous medium in the form of two- or threedimensional bit
+We give an image of porous medium in the form of two- or three-dimensional bit
 array $A$ as the input to our algorithm. In the first stage, we convolve the
@@
   \Procedure{surfsurf}{$A$}
-  \State $A' \gets A*H$
+  \State $A' \gets H*A$
   \Comment{$A'$ becomes an interface of $A$.}
@@
 Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
-the sense that the boundary has a tangent line at every point. Now we introduce
-a function $f_\Gamma(\bm{x}; \Delta)$:
+the sense that the boundary has a tangent line almost at every point. Now we
+introduce a function $f_\Gamma(\bm{x}; \Delta)$:
 \begin{equation*}
@@
   \begin{array}{ll}
-    1/\epsilon & \quad \rho(\bm{x}, \Gamma) < \Delta \\
+    1/\Delta & \quad \rho(\bm{x}, \Gamma) < \Delta \\
     0 & \quad \text{otherwise}
@@
 It's easy to show that
-$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_S(\bm{x})|$
+$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_A(\bm{x})|$
 and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.
@@
 binary operations: $+$ (addition) and $\cdot$ (multiplication) where
-multiplication work according to the following law:
+multiplication works according to the following law:
 \begin{equation*}
@@
   &= \sum_{k=0}^{\infty} \frac{a^k + bka^{k-1}\varepsilon}{k!} \\
-  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}
+  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}^{\infty}
   \frac{a^{k-1}}{(k-1)!} \\
@@
 
-Here are some basic rules for working with dual numbers:
+Here are some basic rules for working with dual numbers (some of which we have
+already described):
 \begin{itemize}
-\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + b) + (c + d)\varepsilon$
+\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
 \item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
@@
 $S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some function
-differentiable in points where $f(x, y) = T$ and $T$ is some threshold. Let's
+differentiable at points where $f(x, y) = T$ and $T$ is some threshold. Let's
 calculate surface-surface function for this set at a point $(a, b)$. We find all
@@
 \end{equation}
-Here $(\cdot, \cdot)$ denotes a scalar product. Gradient of $f$ at the point
-$x_i$ can be found using automatic differentiation and dual numbers described in
-\cref{sec:dual}. Note that acute angle between tangent lines equals to acute
-angle between normals, therefore we can find correlation function $F_{ss}(a, b)$
-using the following formula:
+Here $(\cdot, \cdot)$ denotes a dot product. Gradient of $f$ at the point
+$\bm{x_i}$ can be found using automatic differentiation and dual numbers
+described in \cref{sec:dual}. Note that acute angle between tangent lines equals
+to acute angle between normals, therefore we can find correlation function
+$F_{ss}(a, b)$ using the following formula:
 \begin{equation}
@@
 The set $X$ can be found by firstly evaluating $f(x, y)$ in some regular grid
-searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \varepsilon$ 
-and $|f(x_i - a, y_i - b) - T| < \varepsilon$ for some positive $\varepsilon$
-and then using these points as starting points for some gradient descent based
-algorithm like ADAM to solve \cref{eq:inter}.
+searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \epsilon$
+and $|f(x_i - a, y_i - b) - T| < \epsilon$ for some positive $\epsilon$
+and then using these points as starting points for some algorithm based on
+gradient descent like ADAM to solve \cref{eq:inter}.
 
@@
 A comparison of the algorithm described in \cref{sec:algo} applied to images
-with different resolution with a theory is shown on \cref{fig:fss-disk-3x3}.
+with different resolution with a theory is shown on \cref{fig:fss-disk}.
 \begin{figure*}[!pt]
@@
 where $x_i$ belong to a set
-$(\varepsilon, 2R - \varepsilon) \cup (2R + \varepsilon, 1)$ (here we assume
-image dimensions to be $1 \times 1 \times 1$ length units). Taking
-$\varepsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
+$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$ (here we assume image
+dimensions to be $1 \times 1 \times 1$ length units). Taking
+$\epsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
 for filter $H'$.

### 2023-03-02 paper.tex
Very important commentary
Add bibliography
Add a note about isotropic medium
Introduction

@@
 \author{Vasily Postnicov\textsuperscript{1}}
-\author{Marina Karsanina\textsuperscript{1}}
-\author{Efim Lavrukhin\textsuperscript{1,2}}
-\author{Dina Gafurova\textsuperscript{3}}
+\author{Marina V. Karsanina\textsuperscript{1}}
 \author{Aleksey Khlyupin\textsuperscript{1}}
-\author{Kirill Gerke\textsuperscript{1}}
+\author{Kirill M. Gerke\textsuperscript{1}}
 \email{kg@ifz.ru}
@@
   Russian Academy of Sciences, Moscow, 107031, Russia}
-\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
-  Lomonosov Moscow State University, Moscow, 119991, Russia}
-\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
-  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}
+%\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
+%  Lomonosov Moscow State University, Moscow, 119991, Russia}
+%\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
+%  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}
 
-\title{We did an amazing thing}
+\title{Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach}
 
@@
 \label{sec:intro}
-AAA
+Correlation functions (CFs) to describe structures arose from scattering experiments \cite{debye1957scattering} and
+found their way into numerous disciplines and applications: from material sciences \cite{Cecen,chen2022quantifying}, to rock
+\cite{ledesma2018effect} and soil physics \cite{Euras2012,PLoS_ONE,KarsaninaEJSS}, cosmology \cite{TakadaJain} and food
+engineering \cite{Derossi2019}. In particular, correlation functions as computed from structural images were used for:
+\begin{enumerate}
+  \item characterization of morphology \cite{tensorPRE} and representativeness via
+  correlation lengths \cite{vcapek2011transport,thovert2011grain} at which CFs reach plateau;
+  \item comparison of different structures \cite{jiao2014chawla,EPL1,REVpaper}, usually by computing L-2 norm difference between CFs for two or more images,
+  \item compressing structural information \cite{SciRep1,Havelka} by representing huge datasets in the form of a limited set of CFs that can be further squeezed into parameters for a number of basis functions \cite{jiao_basis,KarsaninaEJSS},
+  \item describing structural dynamics and evolution \cite{chen2015dynamic,PLoS_ONE,xu2022correlation},
+  \item extracting features for deep learning \cite{Miao2017,kamrava2020linking,roding2020predicting,KarsaninaEJSS},
+  \item performing stochastic reconstructions \cite{Adler_recon,Y-T,EPL2,tahmasebiPRL,karsaninaPRL} based on limited input data such as, for example, CFs obtained from 2D cuts,
+  \item fusing multi-scale images \cite{SciRep1,chen2016stochastic,Geoderma2018} into a single representation,
+  \item evaluation of image replica quality, e.g., stochastic reconstructions \cite{deeep_papers_or_somethingelse},
+  \item assessing stationarity of the structure at hand \cite{REVpaper}.
+\end{enumerate}
+
+In majority, if not all, cases mentioned above, surface functions - namely, $F_{ss}$ and $F_{sv}$ - were underrepresented due to our inability to compute them in a robust way.
+While known for a long time \cite{theory_in_MT}, only somewhat crude approximate approaches \cite{crude_approx_inMT} were developed until Ma and Torquato laid foundation for such a robust computational methodology \cite{ma2018SS}.
+They proposed an elegant solution for infinite resolution Gaussian random fields, or "continouos" approach.
+They also assumed that the same approach can be readily applied to discrete experimental images if grey-scale values are thresholded in a similar way to continuious Gaussian field.
+Samarin et al.
+\cite{our_SS_paper} argued that experimental images needs to be segmented first using current cutting edge techniques \cite{NNseg} and proposed "discrete" approach.
+The latter allowed to obtain surface functions closer to analytical solutions for overlapping disks/spheres and to supress noise, in particular for $F_{ss}$.
+The noise in Ma and Torquato method resulted from $1/cos(\theta)$ computations during random line segment placement - this leaves a room for improvements.
+While Samarin et al.
+obtained better convergence with analytical solution, this was demostrated only for overlapping disks image of limited size (that can potentially introduce some differences between computations and analytical solution for infinite size structure).
+Moreover, good agreement was achieved by manually fitting the values of edge-detecting filter that could lack accuracy for arbitrary structure different from overlapping disks.
+In other words, we still lack robustness in surface CFs evaluation due to inability to directly compare "discrete" versus "continuous" methodology, and verify both approaches for arbitrary geometries.
+
+If computed accurately for any arbitrary structure at hand, surface CFs can be utilized in a multitude of applications:
+\begin{enumerate}
+  \item describing real surfaces resulting from different mechanical processes, e.g., cracking \cite{some_examples},
+  \item delineating surface evolution \cite{chen2022} during such mechanical cracking events or reactive transport in porous media \cite{godinho2016,noiriel2021,prokhorov2022},
+  \item representing surface features in super-resolution and stochastic reconstruction techniques \cite{chen2020super,janssens2020,karimpouli2022}.
+\end{enumerate}
+The examples above a just a few potential applications that, due to ability for surface CFs to establish themselves as universal interface/surface descriptors, highlight the necessity to establish robust techniques for $F_{ss}$ and $F_{sv}$ evaluation.
+
+In this contribution we continue to build upon foundational work of Ma and Torquato \cite{ma2018SS}
+and recent findings of Samarin et al.
+\cite{our_SS} to develop a robust and efficient approach to compute surface correlation functions from digital 2D and 3D images.
+In partiuclar, here our aim is to establish a direct verification of "discrete" methodology (that is easily parallelizable on CPU and GPU architectures) using exact noiseless "continuous" approach for arbitrary structures (still described by some continuous function).
+The rest of the manuscript is organized
+as follows: in \cref{sec:def} we introduce some major definitions of CFs necessary for establishing algorithms, in \cref{sec:algo} we describe the all methodological details for "discrete" method for digital images.
+Next, in
+\cref{sec:verify} we explain in detail why verification of computational approaches for digital images is currently hampered, and then introduce
+novel exact "continuous" methodology in \cref{sec:cool-algo}.
+The choice of verification cases is presented in \cref{sec:fss-2d} followed by improvements in methodology of Samarin et al.
+The paper concludes with discussion, outline and summary in \cref{sec:summary}.
 
@@
 
-Now define two disjoint sets in a homogeneous porous medium: a set of solid
+Now we define two disjoint sets in a homogeneous porous medium: a set of solid
 phase $S$ and a set of void phase $V$. Surface-surface correlation function
-$F_{ss}$ and surface-void correlation function $F_{sv}$ are defined as follows:
+$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
 \begin{align}
@@
 \end{align}
-Here angles $\langle \dots \rangle$ denote ensemble average. For isotropic media
-vector values $\bm{x}$ and $\bm{r}$ can be replaced with scalars, but in this
-paper we will consider anisotropic media as well as isotropic.
+Here the brackets $\langle \dots \rangle$ denote ensemble average. For isotropic homogeneous media
+vector values $\bm{x}$ and $\bm{r}$ can be replaced with scalars. In case correlation functions are computed
+in predefined directions, scalar values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.
 
-More detailed information on surface correlation functions can be found in a
-book of Salvatore Torquato\cite{Torquato_book}.
+More detailed information on surface correlation functions can be found in comprehensive
+Torquato's book \cite{Torquato_book}.
 
@@
 
+From now on we will work with square images with dimensions $1 \times 1$ square
+length units, so we can omit division by $N$ in described algorithms and
+ensemble average in \cref{eq:fss} and \cref{eq:fsv} becomes a double integral
+over a square $[0, 1]^2$.
+
 \section{Problem of verification}
@@
 Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
-the sense that the boundary has a tangent line almost at every point. Now we
+the sense that the boundary has a tangent line almost everywhere. Now we
 introduce a function $f_\Gamma(\bm{x}; \Delta)$:
@@
 $1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
-integral domain and division is not defined for all dual numbers with exception
-of $0$. Namely it's defined only if divisor has non-zero real part:
+integral domain and division is not defined \textcolor{red}{for all dual numbers with exception
+of $0$.} Namely it's defined only if divisor has non-zero real part:
 \begin{align*}
@@
 
+\bibliography{paper}
+
 \end{document}

### 2023-03-23 paper.tex
Fix formatting

@@
 
-\title{Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach}
+\title{Surface correlation functions calculations: improving methodology for
+  discrete images with novel exact continuous approach}
 
@@
 \label{sec:intro}
-Correlation functions (CFs) to describe structures arose from scattering experiments \cite{debye1957scattering} and
-found their way into numerous disciplines and applications: from material sciences \cite{Cecen,chen2022quantifying}, to rock
-\cite{ledesma2018effect} and soil physics \cite{Euras2012,PLoS_ONE,KarsaninaEJSS}, cosmology \cite{TakadaJain} and food
-engineering \cite{Derossi2019}. In particular, correlation functions as computed from structural images were used for:
+Correlation functions (CFs) to describe structures arose from scattering
+experiments \cite{debye1957scattering} and found their way into numerous
+disciplines and applications: from material sciences
+\cite{Cecen,chen2022quantifying}, to rock \cite{ledesma2018effect} and soil
+physics \cite{Euras2012,PLoS_ONE,KarsaninaEJSS}, cosmology \cite{TakadaJain} and
+food engineering \cite{Derossi2019}. In particular, correlation functions as
+computed from structural images were used for:
 \begin{enumerate}
-  \item characterization of morphology \cite{tensorPRE} and representativeness via
-  correlation lengths \cite{vcapek2011transport,thovert2011grain} at which CFs reach plateau;
-  \item comparison of different structures \cite{jiao2014chawla,EPL1,REVpaper}, usually by computing L-2 norm difference between CFs for two or more images,
-  \item compressing structural information \cite{SciRep1,Havelka} by representing huge datasets in the form of a limited set of CFs that can be further squeezed into parameters for a number of basis functions \cite{jiao_basis,KarsaninaEJSS},
-  \item describing structural dynamics and evolution \cite{chen2015dynamic,PLoS_ONE,xu2022correlation},
-  \item extracting features for deep learning \cite{Miao2017,kamrava2020linking,roding2020predicting,KarsaninaEJSS},
-  \item performing stochastic reconstructions \cite{Adler_recon,Y-T,EPL2,tahmasebiPRL,karsaninaPRL} based on limited input data such as, for example, CFs obtained from 2D cuts,
-  \item fusing multi-scale images \cite{SciRep1,chen2016stochastic,Geoderma2018} into a single representation,
-  \item evaluation of image replica quality, e.g., stochastic reconstructions \cite{deeep_papers_or_somethingelse},
+  \item characterization of morphology \cite{tensorPRE} and representativeness
+    via correlation lengths \cite{vcapek2011transport,thovert2011grain} at which
+    CFs reach plateau;
+  \item comparison of different structures \cite{jiao2014chawla,EPL1,REVpaper},
+    usually by computing L-2 norm difference between CFs for two or more images,
+  \item compressing structural information \cite{SciRep1,Havelka} by
+    representing huge datasets in the form of a limited set of CFs that can be
+    further squeezed into parameters for a number of basis functions
+    \cite{jiao_basis,KarsaninaEJSS},
+  \item describing structural dynamics and evolution
+    \cite{chen2015dynamic,PLoS_ONE,xu2022correlation},
+  \item extracting features for deep learning
+    \cite{Miao2017,kamrava2020linking,roding2020predicting,KarsaninaEJSS},
+  \item performing stochastic reconstructions
+    \cite{Adler_recon,Y-T,EPL2,tahmasebiPRL,karsaninaPRL} based on limited input
+    data such as, for example, CFs obtained from 2D cuts,
+  \item fusing multi-scale images \cite{SciRep1,chen2016stochastic,Geoderma2018}
+    into a single representation,
+  \item evaluation of image replica quality, e.g., stochastic reconstructions
+    \cite{deeep_papers_or_somethingelse},
   \item assessing stationarity of the structure at hand \cite{REVpaper}.
@@
 
-In majority, if not all, cases mentioned above, surface functions - namely, $F_{ss}$ and $F_{sv}$ - were underrepresented due to our inability to compute them in a robust way.
-While known for a long time \cite{theory_in_MT}, only somewhat crude approximate approaches \cite{crude_approx_inMT} were developed until Ma and Torquato laid foundation for such a robust computational methodology \cite{ma2018SS}.
-They proposed an elegant solution for infinite resolution Gaussian random fields, or "continouos" approach.
-They also assumed that the same approach can be readily applied to discrete experimental images if grey-scale values are thresholded in a similar way to continuious Gaussian field.
-Samarin et al.
-\cite{our_SS_paper} argued that experimental images needs to be segmented first using current cutting edge techniques \cite{NNseg} and proposed "discrete" approach.
-The latter allowed to obtain surface functions closer to analytical solutions for overlapping disks/spheres and to supress noise, in particular for $F_{ss}$.
-The noise in Ma and Torquato method resulted from $1/cos(\theta)$ computations during random line segment placement - this leaves a room for improvements.
-While Samarin et al.
-obtained better convergence with analytical solution, this was demostrated only for overlapping disks image of limited size (that can potentially introduce some differences between computations and analytical solution for infinite size structure).
-Moreover, good agreement was achieved by manually fitting the values of edge-detecting filter that could lack accuracy for arbitrary structure different from overlapping disks.
-In other words, we still lack robustness in surface CFs evaluation due to inability to directly compare "discrete" versus "continuous" methodology, and verify both approaches for arbitrary geometries.
+In majority, if not all, cases mentioned above, surface functions - namely,
+$F_{ss}$ and $F_{sv}$ - were underrepresented due to our inability to compute
+them in a robust way. While known for a long time \cite{theory_in_MT}, only
+somewhat crude approximate approaches \cite{crude_approx_inMT} were developed
+until Ma and Torquato laid foundation for such a robust computational
+methodology \cite{ma2018SS}. They proposed an elegant solution for infinite
+resolution Gaussian random fields, or "continouos" approach. They also assumed
+that the same approach can be readily applied to discrete experimental images if
+grey-scale values are thresholded in a similar way to continuious Gaussian
+field. Samarin et al. \cite{our_SS_paper} argued that experimental images needs
+to be segmented first using current cutting edge techniques \cite{NNseg} and
+proposed "discrete" approach. The latter allowed to obtain surface functions
+closer to analytical solutions for overlapping disks/spheres and to supress
+noise, in particular for $F_{ss}$. The noise in Ma and Torquato method resulted
+from $1/cos(\theta)$ computations during random line segment placement - this
+leaves a room for improvements. While Samarin et al. obtained better convergence
+with analytical solution, this was demostrated only for overlapping disks image
+of limited size (that can potentially introduce some differences between
+computations and analytical solution for infinite size structure). Moreover,
+good agreement was achieved by manually fitting the values of edge-detecting
+filter that could lack accuracy for arbitrary structure different from
+overlapping disks. In other words, we still lack robustness in surface CFs
+evaluation due to inability to directly compare "discrete" versus "continuous"
+methodology, and verify both approaches for arbitrary geometries.
 
-If computed accurately for any arbitrary structure at hand, surface CFs can be utilized in a multitude of applications:
+If computed accurately for any arbitrary structure at hand, surface CFs can be
+utilized in a multitude of applications:
 \begin{enumerate}
-  \item describing real surfaces resulting from different mechanical processes, e.g., cracking \cite{some_examples},
-  \item delineating surface evolution \cite{chen2022} during such mechanical cracking events or reactive transport in porous media \cite{godinho2016,noiriel2021,prokhorov2022},
-  \item representing surface features in super-resolution and stochastic reconstruction techniques \cite{chen2020super,janssens2020,karimpouli2022}.
+  \item describing real surfaces resulting from different mechanical processes,
+    e.g., cracking \cite{some_examples},
+  \item delineating surface evolution \cite{chen2022} during such mechanical
+    cracking events or reactive transport in porous media
+    \cite{godinho2016,noiriel2021,prokhorov2022},
+  \item representing surface features in super-resolution and stochastic
+    reconstruction techniques \cite{chen2020super,janssens2020,karimpouli2022}.
 \end{enumerate}
-The examples above a just a few potential applications that, due to ability for surface CFs to establish themselves as universal interface/surface descriptors, highlight the necessity to establish robust techniques for $F_{ss}$ and $F_{sv}$ evaluation.
+The examples above a just a few potential applications that, due to ability for
+surface CFs to establish themselves as universal interface/surface descriptors,
+highlight the necessity to establish robust techniques for $F_{ss}$ and $F_{sv}$
+evaluation.
 
-In this contribution we continue to build upon foundational work of Ma and Torquato \cite{ma2018SS}
-and recent findings of Samarin et al.
-\cite{our_SS} to develop a robust and efficient approach to compute surface correlation functions from digital 2D and 3D images.
-In partiuclar, here our aim is to establish a direct verification of "discrete" methodology (that is easily parallelizable on CPU and GPU architectures) using exact noiseless "continuous" approach for arbitrary structures (still described by some continuous function).
-The rest of the manuscript is organized
-as follows: in \cref{sec:def} we introduce some major definitions of CFs necessary for establishing algorithms, in \cref{sec:algo} we describe the all methodological details for "discrete" method for digital images.
-Next, in
-\cref{sec:verify} we explain in detail why verification of computational approaches for digital images is currently hampered, and then introduce
-novel exact "continuous" methodology in \cref{sec:cool-algo}.
-The choice of verification cases is presented in \cref{sec:fss-2d} followed by improvements in methodology of Samarin et al.
-The paper concludes with discussion, outline and summary in \cref{sec:summary}.
+In this contribution we continue to build upon foundational work of Ma and
+Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{our_SS} to
+develop a robust and efficient approach to compute surface correlation functions
+from digital 2D and 3D images. In partiuclar, here our aim is to establish a
+direct verification of "discrete" methodology (that is easily parallelizable on
+CPU and GPU architectures) using exact noiseless "continuous" approach for
+arbitrary structures (still described by some continuous function). The rest of
+the manuscript is organized as follows: in \cref{sec:def} we introduce some
+major definitions of CFs necessary for establishing algorithms, in
+\cref{sec:algo} we describe the all methodological details for "discrete" method
+for digital images. Next, in \cref{sec:verify} we explain in detail why
+verification of computational approaches for digital images is currently
+hampered, and then introduce novel exact "continuous" methodology in
+\cref{sec:cool-algo}. The choice of verification cases is presented in
+\cref{sec:fss-2d} followed by improvements in methodology of Samarin et al. The
+paper concludes with discussion, outline and summary in \cref{sec:summary}.
 
@@
 \end{align}
-Here the brackets $\langle \dots \rangle$ denote ensemble average. For isotropic homogeneous media
-vector values $\bm{x}$ and $\bm{r}$ can be replaced with scalars. In case correlation functions are computed
-in predefined directions, scalar values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.
+Here the brackets $\langle \dots \rangle$ denote ensemble average. For isotropic
+homogeneous media vector values $\bm{x}$ and $\bm{r}$ can be replaced with
+scalars. In case correlation functions are computed in predefined directions,
+scalar values can be also used for anisotropic structures
+\cite{jiao2014chawla,EPL1}.
 
-More detailed information on surface correlation functions can be found in comprehensive
-Torquato's book \cite{Torquato_book}.
+More detailed information on surface correlation functions can be found in
+comprehensive Torquato's book \cite{Torquato_book}.
 

### 2023-03-23 paper.tex
A little clarification regarding isotropic media

@@
 \end{align}
-Here the brackets $\langle \dots \rangle$ denote ensemble average. For isotropic
-homogeneous media vector values $\bm{x}$ and $\bm{r}$ can be replaced with
-scalars. In case correlation functions are computed in predefined directions,
-scalar values can be also used for anisotropic structures
-\cite{jiao2014chawla,EPL1}.
+Here the brackets $\langle \dots \rangle$ denote ensemble average. If the medium
+under consideration is also isotropic, the argument in functions $F_{ss}$ and
+$F_{sv}$ can be replaced with a scalar:
+\begin{align*}
+  F_{ss}(r) &= F_{ss}(|\bm{r}|) \\
+  F_{sv}(r) &= F_{sv}(|\bm{r}|)
+\end{align*}
+In case correlation functions are computed in predefined directions, scalar
+values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.
 
@@
 \section{Conclusion}
+% Is this a right label?
+\label{sec:summary}
 In this paper we develop an algorithm for precise calculation of surface-surface

### 2023-03-23 paper.tex
Definition of F_{sss}

@@
 under consideration is also isotropic, the argument in functions $F_{ss}$ and
-$F_{sv}$ can be replaced with a scalar:
+$F_{sv}$ can be replaced with a scalar $r = |\bm{r}|$:
 \begin{align*}
-  F_{ss}(r) &= F_{ss}(|\bm{r}|) \\
-  F_{sv}(r) &= F_{sv}(|\bm{r}|)
+  F_{ss}(r) &= F_{ss}(\bm{r}) \\
+  F_{sv}(r) &= F_{sv}(\bm{r})
 \end{align*}
 In case correlation functions are computed in predefined directions, scalar
-values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.
+values can be also used for anisotropic structures
+\cite{jiao2014chawla,EPL1}. These functions are defined for media with
+dimensionality of 2 and higher and have units of measurement $m^{-1}$ for
+$F_{sv}$ and $m^{-2}$ for $F_{ss}$.
+
+Another function studied in this paper is surface-surface-surface function
+$F_{sss}$. It is defined as follows:
+\begin{equation}
+  F_{sss}(\bm{r_1}, \bm{r_2}) = \langle |\nabla \chi_S(\bm{x})|
+  |\nabla \chi_S(\bm{x} + \bm{r_1})|
+  |\nabla \chi_S(\bm{x} + \bm{r_2})|
+  \rangle \label{eq:fsss}
+\end{equation}
+This function is defined for media with dimensionality 3 or higher and has unit
+of measurement $m^{-3}$. For three-dimensional media $F_{sss}$ is a function of
+six scalar arguments: $\bm{r_1} = (r_{1x}, r_{1y}, r_{1z})$ and
+$\bm{r_2} = (r_{2x}, r_{2y}, r_{2z})$. However if the medium under consideration
+is isotropic, only three scalar arguments $r_1 = |\bm{r_1}|$, $r_2 = |\bm{r_2}|$
+and $r_3 = |\bm{r_1} - \bm{r_2}|$ are required. The last argument can be
+replaced with an angle $\theta$ between vectors $\bm{r_1}$ and $\bm{r_2}$:
+\begin{equation*}
+  F_{sss}(r_1, r_2, r_3) = F_{sss}(r_1, r_2, \theta) = F_{sss}(\bm{r_1}, \bm{r_2})
+\end{equation*}
 
 More detailed information on surface correlation functions can be found in
-comprehensive Torquato's book \cite{Torquato_book}.
+\cref{sec:verify} and comprehensive Torquato's book \cite{Torquato_book}.
 

### 2023-03-23 paper.tex
Add an algorithm for F_{sss}

@@
 \label{sec:algo}
-Here we briefly describe an algorithm for computation of surface-surface and
-surface-void correlation functions for digital images of porous media. A more
-detailed description can be found in a paper of Samarin
-et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
+Here we briefly describe an algorithm for computation of surface-surface,
+surface-void and surface-surface-surface correlation functions for digital
+images of porous media. A more detailed description can be found in a paper of
+Samarin et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
 correlation functions for all possible directions and correlation lengths. It
-consists of two stages: edge detection stage and computation of
-autocorrelation.
+consists of two stages: edge detection stage and computation of autocorrelation.
 
@@
 Therefore $A'$ has non-zero elements only in a small area around interface
-between phases in $A$.
+between phases in $A$. This operation is convolution of a filter $H$ with an
+image $A$ and can be performed using Fourier transform:
+\begin{equation*}
+  A' = H*A = F^{-1}[F[H] F[A]]
+\end{equation*}
+Here $F$ is a forward Fourier transform and $F^{-1}$ is its inverse.
 
@@
 Calculation of sums in the latter equations can be performed using the following
-properties of Fourier transform:
+properties of Fourier transform (here $\hat{f}(z) = F[f(x)]$):
 \begin{equation*}
@@
 
-From now on we will work with square images with dimensions $1 \times 1$ square
-length units, so we can omit division by $N$ in described algorithms and
-ensemble average in \cref{eq:fss} and \cref{eq:fsv} becomes a double integral
-over a square $[0, 1]^2$.
+For surface-surface-surface function $F_{sss}$ the former approach can also be
+used, but it would be highly inefficient memory-wise because for three
+dimensional case $F_{sss}$ is a function of six scalar coordinates which leads
+to a very large output array. Instead of this approach we use a slower approach
+which computes $F_{sss}$ at a specified point calculating a convolution using
+its definition:
+\begin{algorithmic}[1]
+  \Procedure{surfsurfsurf}{$A$, $\bm{r_1}$, $\bm{r_2}$}
+  \State $A' \gets A*H$
+  \Comment{$A'$ becomes an interface of $A$.}
+  \State $A'_1 \gets shift(A', \bm{r_1})$
+  \Comment{Shift $A$ in $i$-th dimension by $r_{1i}$ for all $i \in \overline{1, ndim(A)}$}
+  \State $A'_2 \gets shift(A', \bm{r_2})$
+  \Comment{Shift $A$ in $i$-th dimension by $r_{2i}$ for all $i \in \overline{1, ndim(A)}$}
+  \State $M \gets A' \cdot A'_1 \cdot A'_2$
+  \Comment{Multiplicate three arrays element-wise}
+  \State \textbf{return} $\sum_{i} M_{i} / N$
+  \Comment{Sum all elements in $M$ and divide by a number of elements in $A$}
+  \EndProcedure
+\end{algorithmic}
+This algorithm can be vectorized and therefore benefits from the usage of
+GPUs. Shift function in this algorithm must be a circular shift which
+``rotates'' content of the array, if periodic boundary conditions are
+desired. For our purpose we use $F_{sss}$ function in the form
+$F_{sss}(r_1, r_2, \theta)$ and fix $\theta = \pi/2$. This leads us to a
+sampling pattern shown on \cref{fig:Fsss-pattern}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/pattern.png}
+  \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
+    implementation is a right triangle with varying catets $r_1$ and
+    $r_2$. Patterns can lie in planes $XY$ (as on the picture), $XZ$ or
+    $YZ$. Black dots depict elements of $A'$}
+  \label{fig:Fsss-pattern}
+\end{figure}
+
+From now on when considering $F_{ss}$ and $F_{sv}$ functions we will work with
+square images which have unit area, so we can omit division by $N$ in described
+algorithms and ensemble average in \cref{eq:fss} and \cref{eq:fsv} becomes a
+double integral over a square $[0, 1]^2$. When considering $F_{sss}$ function we
+will work with cubic images which have unit volume. Then we can also omit
+division by $N$ and ensemble average in \cref{eq:fsss} becomes a triple integral
+over a cube $[0, 1]^3$.
 

### 2023-03-23 paper.tex
Schluss mit den Winkeln!

@@
     translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
-    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
+    the interfaces. Surface of dashed area is
+    $\frac{\Delta^2}{\sin \phi}$. Vectors $\bm{a}$ and $\bm{b}$ are unit vectors
+    parallel to normals to $\Gamma$ and $\Gamma'$ respectively in the point of
+    their intersection.}
   \label{fig:fss-zoomed}
@@
   F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
-  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
+  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d-sin}
 \end{equation}
@@
 $\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_A(\bm{x})|$
-and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.
+and therefore \cref{eq:fss-2d-sin} and \cref{eq:fss} define the same function.
+
+A less illustrative but more practical way to calculate an expression
+$\frac{S_k}{\Delta}$ is the following. Take two vectors $\bm{a}$ and $\bm{b}$
+parallel to normals to $\Gamma$ and $\Gamma'$ in $k$-th point of their
+intersection such as $|a| = |b| = 1$. If $F_{ss}$ is defined at the point of
+consideration then $\bm{a} \ne k\bm{b}$. The pair $(a, b)$ may serve as a basis
+with the following transformation from the basis $(0,1), (1,0)$:
+\begin{align*}
+  x' &= f(x, y) = a_x x + a_y y \\
+  y' &= g(x, y) = b_x x + b_y y
+\end{align*}
+where $\bm{a} = (a_x, a_y)$, $\bm{b} = (b_x, b_y)$. Jacobian determinant for
+this transformation is
+\begin{equation*}
+  J = \left|
+  \begin{array}{cc}
+    \frac{\partial f}{\partial x} & \frac{\partial f}{\partial y} \\
+    \frac{\partial g}{\partial x} & \frac{\partial g}{\partial y} \\
+  \end{array}
+  \right| =
+  \left|
+  \begin{array}{cc}
+    a_x & a_y \\
+    b_x & b_y
+  \end{array}
+  \right| = a_x b_y - a_y b_x
+\end{equation*}
+
+We can rewritte \cref{eq:fss-2d-sin} using $J$ as follows:
+\begin{equation}
+  F_{ss}(\bm{r}) = \sum_{k=1}^N \frac{1}{|J_k|} \label{eq:fss-2d}
+\end{equation}
+where $J_k$ is Jacobian determinant computed at $k$-th point of
+intersection. This form proves to be much more useful than the version which
+contains the angle $\phi$.
 
@@
 We denote a set of solutions of this equation as $X$. For every $\bm{x}_i \in X$
-we find an angle $\phi_i$ between a normal to the boundary and a normal to
-the translated boundary as
-\begin{equation}
-  \cos \phi_i = \frac{(\nabla f(x,y) \vert_{\bm{x}_i}, \nabla f(x-a,y-b)
-    \vert_{\bm{x}_i})}{|\nabla f(x,y) \vert_{\bm{x}_i}| |\nabla f(x-a,y-b)
-    \vert_{\bm{x}_i}|} \label{eq:angle}
-\end{equation}
-Here $(\cdot, \cdot)$ denotes a dot product. Gradient of $f$ at the point
-$\bm{x_i}$ can be found using automatic differentiation and dual numbers
-described in \cref{sec:dual}. Note that acute angle between tangent lines equals
-to acute angle between normals, therefore we can find correlation function
-$F_{ss}(a, b)$ using the following formula:
-\begin{equation}
-  F_{ss}(a, b) = \sum_i \frac{1}{\sqrt{1 - \cos^2 \phi_i}} \label{eq:fss-method}
-\end{equation}
+we find normals to the boundary and the boundary translated by a vector
+$(a, b)$. These normals can be found using automatic differentiation and dual
+numbers described in \cref{sec:dual}. Then we normalize these normals (i.e. make
+their length equal to $1$) and use \cref{eq:fss-2d} to calculate $F_{ss}$.
 
-The algorithm of calculating $F_{ss}(a, b)$ is the following:
+Summarizing, the algorithm of calculating $F_{ss}(a, b)$ is the following:
 \begin{enumerate}
 \item Find $X$ which is a set of soulutions of \cref{eq:inter}.
-\item For all points in $X$ find cosines between normals to the boundaries using
-  \cref{eq:angle}.
-\item Calculate $F_{ss}(a, b)$ using \cref{eq:fss-method}.
+\item For all points in $X$ find normals to the boundaries using automatic
+  differentiation.
+\item Calculate $F_{ss}(a, b)$ using \cref{eq:fss-2d}.
 \end{enumerate}

### 2023-03-24 paper.tex
Improve section about dual numbers

@@
 \label{sec:dual}
-A ring of dual numbers $D$ is a set of pairs of real numbers $(x, y)$ with two
+A ring of dual numbers $D$ is a set of pairs of real numbers $(a, b)$ with two
 binary operations: $+$ (addition) and $\cdot$ (multiplication) where
@@
 \begin{equation*}
-  (x_1, y_1)\cdot(x_2, y_2) = (x_1x_2, x_1y_2 + y_1x_2)
+  (a, b)\cdot(c, d) = (ac, ad + bc)
 \end{equation*}
@@
 It's useful to introduce an imaginary unit $\varepsilon$ and write a dual number
-$(x, y)$ as $x + y\varepsilon$. As you can see from multiplication law,
+$(a, b)$ as $a + b\varepsilon$. As you can see from multiplication law,
 $1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
-integral domain and division is not defined \textcolor{red}{for all dual numbers with exception
-of $0$.} Namely it's defined only if divisor has non-zero real part:
+integral domain and division is defined only if divisor has non-zero real part:
 \begin{align*}
@@
 
-Power function $(a + b\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined
-using binomial formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
+Now we consider functions of dual variable $x + y\varepsilon$. Power function
+$(x + y\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined using binomial
+formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
 \begin{equation*}
-  (a + b\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} a^k (b\varepsilon)^{n-k} =
-  a^n + n a^{n-1} b \varepsilon
+  (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
+  x^n + n x^{n-1} y \varepsilon
 \end{equation*}
-This formula can be extended on $n \in \mathbb{Q}$ as well.
+This formula can be extended to $n \in \mathbb{Q}$ as well.
 
-Elementary functions can be extended to dual numbers using Taylor series. For
-example, the exponent function is extended as:
+Elementary functions can be extended to dual numbers using Taylor series (here
+$a$ is some point at which $f$ is differentiable):
 \begin{align*}
-  e^{a + b\varepsilon} &= \sum_{k=0}^{\infty}\frac{(a + b\varepsilon)^k}{k!} \\
-  &= \sum_{k=0}^{\infty} \frac{a^k + bka^{k-1}\varepsilon}{k!} \\
-  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}^{\infty}
-  \frac{a^{k-1}}{(k-1)!} \\
-  &= e^a + e^ab\varepsilon
+  f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
+  & \qquad + \frac{f'''(a)}{3!}(x + y\varepsilon)^3 + \dots \\
+  &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x^2 + 2xy\varepsilon) \\
+  & \qquad + \frac{f'''(a)}{3!}(x^3 + 3x^2y\varepsilon) + \dots \\
+  &= f(a) + f'(a)x + \frac{f''(a)}{2!}x^2 + \frac{f'''(a)}{3!}x^3 + \dots \\
+  & \quad y\varepsilon(f'(a) + f''(a)x + \frac{f'''(a)}{2!}x^2 + \dots) \\
+  &= f(x) + yf'(x)\varepsilon
 \end{align*}
@@
 
-It's easy to see, that there is a connection between dual numbers and
-differentiation. Indeed, if functions $f(x)$ and $g(x)$
-are differentiable at the point $a$ and $h(x) = f(x)g(x)$ is their product then
-$h(a + b\varepsilon) = h(a) + b\varepsilon(f'(a)g(a) + f(a)g'(a))$.
-If $h(x) = f(x)/g(x)$ and $g(a) \ne 0$ then
-$h(a + b\varepsilon) = h(a) + b\varepsilon\frac{f'(a)g(a) - f(a)g'(a)}{f^2(a)}$.
-More generally, we can see that $f(a + b\varepsilon) = f(a) + bf'(a)\varepsilon$.
-
-So, using dual numbers we can compute two values at once: one of the function at
-the point $x = a$ and the other of its derivative at this point:
-$f(a + \varepsilon) = f(a) + \varepsilon f'(a)$. Also we can compute a partial
+As you can see, dual numbers are connected with differentiation. Using a dual
+argument $a + \varepsilon$ we can compute a value of a function at point $x = a$
+and its derivative at that point:
+$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also we can compute a partial
 derivative of a multivariate function. For example:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
@@
     \varepsilon)
-\end{align*}
+  \end{aligned}
+  \label{eq:autonormals}
+\end{equation}
+The last equation will be useful for computation of normals to the interface in
+next sections.
 
@@
 \item Find $X$ which is a set of soulutions of \cref{eq:inter}.
-\item For all points in $X$ find normals to the boundaries using automatic
-  differentiation.
+\item For all points in $X$ find normals to the boundaries using
+  \cref{eq:autonormals}.
 \item Calculate $F_{ss}(a, b)$ using \cref{eq:fss-2d}.

### 2023-03-24 paper.tex
Merge two sections and reorganize the order

@@
 hampered, and then introduce novel exact "continuous" methodology in
-\cref{sec:cool-algo}. The choice of verification cases is presented in
-\cref{sec:fss-2d} followed by improvements in methodology of Samarin et al. The
-paper concludes with discussion, outline and summary in \cref{sec:summary}.
+\cref{sec:fss-2d}. The choice of verification cases is presented in
+\textcolor{red}{Fix reference} followed by improvements in methodology of
+Samarin et al. The paper concludes with discussion, outline and summary in
+\cref{sec:summary}.
 
@@
 overlapping balls and disks, we were not sure if our algorithm performs good in
-general and searched for more test cases. Here we present one such case:
-two-dimensional sets with smooth boundary.
+general and searched for more test cases. Here we briefly discuss dual numbers
+and autodifferentiation technique and present another case: two- and
+three-dimensional sets with smooth boundary.
 
-\subsection{Surface-surface function in two-dimensional case}
+\subsection{Dual numbers and automatic differentiation}
+\label{sec:dual}
+A ring of dual numbers $D$ is a set of pairs of real numbers $(a, b)$ with two
+binary operations: $+$ (addition) and $\cdot$ (multiplication) where
+multiplication works according to the following law:
+\begin{equation*}
+  (a, b)\cdot(c, d) = (ac, ad + bc)
+\end{equation*}
+It's easy to see that $D$ is commutative.
+
+It's useful to introduce an imaginary unit $\varepsilon$ and write a dual number
+$(a, b)$ as $a + b\varepsilon$. As you can see from multiplication law,
+$1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
+integral domain and division is defined only if divisor has non-zero real part:
+\begin{align*}
+  \frac{a+b\varepsilon}{c+d\varepsilon} &=
+  \frac{(a+b\varepsilon)(c-d\varepsilon)}{(c+d\varepsilon)(c-d\varepsilon)} \\
+  &= \frac{ac-ad\varepsilon+bc\varepsilon}{c^2} \\
+  &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
+\end{align*}
+
+Now we consider functions of dual variable $x + y\varepsilon$. Power function
+$(x + y\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined using binomial
+formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
+\begin{equation*}
+  (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
+  x^n + n x^{n-1} y \varepsilon
+\end{equation*}
+This formula can be extended to $n \in \mathbb{Q}$ as well.
+
+Elementary functions can be extended to dual numbers using Taylor series (here
+$a$ is some point at which $f$ is differentiable):
+\begin{align*}
+  f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
+  & \qquad + \frac{f'''(a)}{3!}(x + y\varepsilon)^3 + \dots \\
+  &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x^2 + 2xy\varepsilon) \\
+  & \qquad + \frac{f'''(a)}{3!}(x^3 + 3x^2y\varepsilon) + \dots \\
+  &= f(a) + f'(a)x + \frac{f''(a)}{2!}x^2 + \frac{f'''(a)}{3!}x^3 + \dots \\
+  & \quad y\varepsilon(f'(a) + f''(a)x + \frac{f'''(a)}{2!}x^2 + \dots) \\
+  &= f(x) + yf'(x)\varepsilon
+\end{align*}
+
+Here are some basic rules for working with dual numbers (some of which we have
+already described):
+\begin{itemize}
+\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
+\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
+\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
+\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
+\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
+\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
+\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
+\end{itemize}
+
+As you can see, dual numbers are connected with differentiation. Using a dual
+argument $a + \varepsilon$ we can compute a value of a function at point $x = a$
+and its derivative at that point:
+$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also we can compute a partial
+derivative of a multivariate function. For example:
+\begin{equation}
+  \begin{aligned}
+    \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
+    b) \\
+    \frac{\partial}{\partial y} f(x, y) \vert_{x = a, y = b} &= f(a, b +
+    \varepsilon)
+  \end{aligned}
+  \label{eq:autonormals}
+\end{equation}
+The last equation will be useful for computation of normals to the interface in
+next sections.
+
+\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
 \label{sec:fss-2d}
@@
 
-\subsection{Dual numbers and automatic differentiation}
-\label{sec:dual}
-A ring of dual numbers $D$ is a set of pairs of real numbers $(a, b)$ with two
-binary operations: $+$ (addition) and $\cdot$ (multiplication) where
-multiplication works according to the following law:
-\begin{equation*}
-  (a, b)\cdot(c, d) = (ac, ad + bc)
-\end{equation*}
-It's easy to see that $D$ is commutative.
-
-It's useful to introduce an imaginary unit $\varepsilon$ and write a dual number
-$(a, b)$ as $a + b\varepsilon$. As you can see from multiplication law,
-$1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
-integral domain and division is defined only if divisor has non-zero real part:
-\begin{align*}
-  \frac{a+b\varepsilon}{c+d\varepsilon} &=
-  \frac{(a+b\varepsilon)(c-d\varepsilon)}{(c+d\varepsilon)(c-d\varepsilon)} \\
-  &= \frac{ac-ad\varepsilon+bc\varepsilon}{c^2} \\
-  &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
-\end{align*}
-
-Now we consider functions of dual variable $x + y\varepsilon$. Power function
-$(x + y\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined using binomial
-formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
-\begin{equation*}
-  (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
-  x^n + n x^{n-1} y \varepsilon
-\end{equation*}
-This formula can be extended to $n \in \mathbb{Q}$ as well.
-
-Elementary functions can be extended to dual numbers using Taylor series (here
-$a$ is some point at which $f$ is differentiable):
-\begin{align*}
-  f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
-  & \qquad + \frac{f'''(a)}{3!}(x + y\varepsilon)^3 + \dots \\
-  &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x^2 + 2xy\varepsilon) \\
-  & \qquad + \frac{f'''(a)}{3!}(x^3 + 3x^2y\varepsilon) + \dots \\
-  &= f(a) + f'(a)x + \frac{f''(a)}{2!}x^2 + \frac{f'''(a)}{3!}x^3 + \dots \\
-  & \quad y\varepsilon(f'(a) + f''(a)x + \frac{f'''(a)}{2!}x^2 + \dots) \\
-  &= f(x) + yf'(x)\varepsilon
-\end{align*}
-
-Here are some basic rules for working with dual numbers (some of which we have
-already described):
-\begin{itemize}
-\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
-\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
-\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
-\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
-\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
-\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
-\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
-\end{itemize}
-
-As you can see, dual numbers are connected with differentiation. Using a dual
-argument $a + \varepsilon$ we can compute a value of a function at point $x = a$
-and its derivative at that point:
-$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also we can compute a partial
-derivative of a multivariate function. For example:
-\begin{equation}
-  \begin{aligned}
-    \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
-    b) \\
-    \frac{\partial}{\partial y} f(x, y) \vert_{x = a, y = b} &= f(a, b +
-    \varepsilon)
-  \end{aligned}
-  \label{eq:autonormals}
-\end{equation}
-The last equation will be useful for computation of normals to the interface in
-next sections.
-
-\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
-\label{sec:cool-algo}
-Here we examine two-dimensional sets with smooth boundary described in
-\cref{sec:fss-2d} more closely. Suppose a set $S$ is defined as
-$S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some function
-differentiable at points where $f(x, y) = T$ and $T$ is some threshold. Let's
-calculate surface-surface function for this set at a point $(a, b)$. We find all
-intersections between a boundary $\Gamma$ and its translated version by solving a
-system of equations
+Now we get to practical algorithm for computation of $F_{ss}$ for sets with a
+smooth boundary. Suppose a set $S$ is defined as
+$S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some
+function differentiable at points where $f(x, y) = T$ and $T$ is some
+threshold. Let's calculate surface-surface function for this set at a point
+$(a, b)$. We find all intersections between a boundary $\Gamma$ and its
+translated version by solving a system of equations
 \begin{equation*}
@@
 Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
-\cref{fig:blob}. We can use the algorithm developed in \cref{sec:cool-algo} to
+\cref{fig:blob}. We can use the algorithm developed in \cref{sec:fss-2d} to
 compute precise values of $F_{ss}$ for this blob and compare them with values

### 2023-03-24 paper.tex
Add precise algorithm for F_{sss}

@@
 introduce a function $f_\Gamma(\bm{x}; \Delta)$:
-\begin{equation*}
+\begin{equation}
   f_\Gamma(\bm{x}; \Delta) = \left\{
@@
   \end{array}
-  \right.
-\end{equation*}
+  \right. \label{eq:delta-sequence}
+\end{equation}
 Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
@@
 \end{figure}
-Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
+Now define a functional sequence $F_{ss}(\bm{r}; \Delta)$:
 \begin{align*}
@@
 intersection such as $|a| = |b| = 1$. If $F_{ss}$ is defined at the point of
-consideration then $\bm{a} \ne k\bm{b}$. The pair $(a, b)$ may serve as a basis
-with the following transformation from the basis $(0,1), (1,0)$:
+consideration then $\bm{a} \ne \pm \bm{b}$. The pair $(\bm{a}, \bm{b})$ may
+serve as a basis with the following transformation from the basis
+$(1,0), (0,1)$:
 \begin{align*}
@@
 threshold. Let's calculate surface-surface function for this set at a point
-$(a, b)$. We find all intersections between a boundary $\Gamma$ and its
-translated version by solving a system of equations
+$\bm{r} = (r_x, r_y)$. We find all intersections between a boundary $\Gamma$ and
+its translated version by solving a system of equations
 \begin{equation*}
@@
     f(x, y) = T \\
-    f(x-a, y-b) = T    
+    f(x-r_x, y-r_y) = T
   \end{array}
@@
 \begin{equation}
-  (f(x, y) - T)^2 + (f(x-a, y-b) - T)^2 = 0 \label{eq:inter}
+  (f(x, y) - T)^2 + (f(x-r_x, y-r_y) - T)^2 = 0 \label{eq:inter}
 \end{equation}
@@
 we find normals to the boundary and the boundary translated by a vector
-$(a, b)$. These normals can be found using automatic differentiation and dual
+$\bm{r}$. These normals can be found using automatic differentiation and dual
 numbers described in \cref{sec:dual}. Then we normalize these normals (i.e. make
@@
 
-Summarizing, the algorithm of calculating $F_{ss}(a, b)$ is the following:
+Summarizing, the algorithm of calculating $F_{ss}(\bm{r})$ is the following:
 \begin{enumerate}
@@
 \item For all points in $X$ find normals to the boundaries using
-  \cref{eq:autonormals}.
-\item Calculate $F_{ss}(a, b)$ using \cref{eq:fss-2d}.
+  \cref{eq:autonormals} and normalize them.
+\item Calculate $F_{ss}(\bm{r})$ using \cref{eq:fss-2d}.
 \end{enumerate}
@@
 searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \epsilon$
-and $|f(x_i - a, y_i - b) - T| < \epsilon$ for some positive $\epsilon$
+and $|f(x_i - r_x, y_i - r_y) - T| < \epsilon$ for some positive $\epsilon$
 and then using these points as starting points for some algorithm based on
 gradient descent like ADAM to solve \cref{eq:inter}.
+
+\subsection{Surface-surface-surface function for three-dimensional sets with
+  smooth boundary}
+\label{sec:fsss-3d}
+Results of this section are made by analogy with \cref{sec:fss-2d}. Again, let
+$S$ be some set in $\mathbb{R}^3$ which has a smooth boundary, i.e. has a
+tangent plane at almost every point of its boundary. Using the function
+\cref{eq:delta-sequence} we define a functional sequence
+$F_{sss}(\bm{r_1}, \bm{r_2}; \Delta)$:
+\begin{align*}
+  F_{sss}(\bm{r_1}, \bm{r_2}; \Delta) &= \int\int\int dx dy dz \times \\
+  &\qquad \times f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x} + \bm{r_1}; \Delta)
+  f_\Gamma(\bm{x} + \bm{r_2}; \Delta) \\
+  &= \sum_{k=1}^N V_k/\Delta^3
+\end{align*}
+$V_k$ is a volume of parallelepiped where all three multiplicands under integral
+are non-zero. $N$ is a number of these parallelepipeds, i.e. number of points
+where all three boundaries (one ``original'' boundary and two translated
+versions) have an intersection. With $\Delta$ going to zero we get a convergence
+to $F_{sss}$:
+\begin{equation*}
+  \lim_{\Delta \to 0} F_{sss}(\bm{r_1}, \bm{r_2}; \Delta) = F_{sss}(\bm{r_1},
+  \bm{r_2})
+\end{equation*}
+
+Let $\bm{a}$, $\bm{b}$ and $\bm{c}$ be normalized normals to each boundary in
+the point of intersection. The corresponding $V_k$ is finite if and only if
+$\bm{a} \ne \pm \bm{b} \ne \pm \bm{c}$. In this case we can use a triplet
+$(\bm{a}, \bm{b}, \bm{c})$ as basis for $\mathbb{R}^3$ with the following
+transformation from the basis $(1,0,0), (0,1,0), (0, 0, 1)$:
+\begin{align*}
+  x' &= f(x, y) = a_x x + a_y y + a_z z \\
+  y' &= g(x, y) = b_x x + b_y y + b_z z \\
+  z' &= h(x, y) = c_x x + c_y y + c_z z \\
+\end{align*}
+Jacobian determinant for this transformation is
+\begin{equation*}
+  J = \left|
+  \begin{array}{ccc}
+    a_x & a_y & a_z \\
+    b_x & b_y & b_z \\
+    c_x & c_y & c_z \\
+  \end{array}
+  \right|
+\end{equation*}
+and the expression for $F_{sss}$ becomes
+\begin{equation}
+  F_{sss}(\bm{r_1}, \bm{r_2}) = \sum_{k=1}^N \frac{1}{|J_k|} \label{eq:fsss-3d}
+\end{equation}
+where $J_k$ is Jacobian determinant computed at $k$-th point of
+intersection.
 

### 2023-03-27 paper.tex
Add another test case: a cube

@@
 
-\subsection{A square}
-Let's define a function $f(x, y) = \max(|x|, |y|)$. A set $f(x, y) \le T$ is a
-square with side $2T$. The function $f$ is differentiable at all points where
-$f(x, y) = T$ with exception of points $(-T, -T)$, $(-T, T)$, $(T, -T)$ and
-$(T, T)$. The surface-surface correlation function for a square is equal to:
+\subsection{A square and a cube}
+Define a function $f(\bm{x}) = \max\limits_i |x_i|$. A set $f(\bm{x}) \le T$
+where $\bm{x} \in \mathbb{R}^2$ is a square with side $2T$. The function $f$ is
+differentiable at all points where $f(\bm{x}) = T$ with exception of points
+$(-T, -T)$, $(-T, T)$, $(T, -T)$ and $(T, T)$. The surface-surface correlation
+function for a square is equal to:
 \begin{equation*}
-  F_{ss}(x, y) = \left\{
+  F_{ss}(\bm{r}) = \left\{
   \begin{array}{ll}
-    2 & \quad \max(|x|, |y|) < T \ \text{and}\ x\ne0, y\ne0 \\
-    0 & \quad \max(|x|, |y|) > T \\
+    2 & \quad f(\bm{r}) < 2T \ \text{and}\ r_i \ne 0, \forall i \in \overline{1,2} \\
+    0 & \quad f(\bm{r}) > 2T \\
     \text{undefined} & \quad \text{otherwise}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/fss-square.png}
-  \caption[]{$F_{ss}$ function for a square with side $T$. The function is
-    undefined along red segments. Its value is $2$ inside a shaded area and $0$
-    outside.}
+  \includegraphics[width=0.45\linewidth]{images/fss-square.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{images/fss-square-julia.png}
+  \caption[]{$F_{ss}$ function for a square with side $T = 0.3$. On the left:
+    Theoretical results. The function is undefined along red segments. Its value
+    is $2$ inside a shaded area and $0$ outside. On the right: Calculation with
+    the algorithm described in \cref{sec:algo}.}
   \label{fig:fss-square}
 \end{figure}
+
+A set $f(\bm{x}) \le T$ where $\bm{x} \in \mathbb{R}^3$ is a cube with the same
+side $2T$.
+The surface-surface-surface correlation function for this cube is equal to:
+\begin{equation*}
+  F_{sss}(\bm{r}) = \left\{
+  \begin{array}{ll}
+    2 & \quad f(\bm{r}) < 2T \ \text{and}\ r_i \ne 0, \forall i \in \overline{1,3} \\
+    0 & \quad f(\bm{r}) > 2T \\
+    \text{undefined} & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation*}
+This case is also handled good by the algorithm described in
+\cref{sec:algo}. \textcolor{red}{Any picture/plot here?}.
 

### 2023-03-27 scripts/plot-square.py

@@ -1,0 +1,12 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = np.load('square.npy')
+data = np.where((data > 1.0) * (data < 2.3), 5*data, data)
+
+plt.figure(figsize = (8, 8), dpi = 300)
+plt.rc('font', size = 18)
+plt.imshow(data, extent = (-1/2,1/2,-1/2,1/2))
+plt.savefig('../images/fss-square-julia.png', bbox_inches = 'tight')

### 2023-03-28 scripts&data/plot-sss-error.py
Add sss function for a ball

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy.interpolate as inter
+
+julia   = np.load("ball-sss-julia.npy")
+precise = np.load("ball-sss-precise.npy")
+
+julia_x = np.linspace(0, julia.shape[0]/200, julia.shape[0])
+f = inter.RegularGridInterpolator((julia_x, julia_x),  julia)
+x = np.linspace(0.02, 0.61, precise.shape[0])
+x, y = np.meshgrid(x, x)
+julia = f(np.stack((x, y), axis = 2))
+
+error = np.abs(precise - julia)
+error = error / np.clip(precise, 1e-8, 1e8)
+
+x, y, error = x.flatten(), y.flatten(), error.flatten()
+indices = (x**2 + y**2) < 0.575**2
+
+plt.figure(figsize = (12, 10), dpi = 300)
+plt.rc('font', size = 16)
+ax = plt.axes((0, 0, 1, 1,), projection = "3d")
+ax.azim = -32
+ax.elev =  35
+ax.plot_trisurf(x[indices], y[indices], error[indices])
+ax.set_xlabel('x')
+ax.set_ylabel('y')
+ax.set_zlabel('Relative error')
+ax.ticklabel_format(scilimits = (0, 0))
+plt.savefig('../images/ball-sss-error.png', bbox_inches = 'tight')

### 2023-03-28 scripts&data/plot-sss.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+julia   = np.load("ball-sss-julia.npy")
+x = np.linspace(0, julia.shape[0]/200, julia.shape[0])
+x, y = np.meshgrid(x, x)
+x, y, julia = x.flatten(), y.flatten(), julia.flatten()
+indices = julia < 40
+
+plt.figure(figsize = (12, 10), dpi = 300)
+plt.rc('font', size = 16)
+ax = plt.axes((0, 0, 1, 1,), projection = "3d")
+ax.azim = -32
+ax.elev =  35
+ax.plot_trisurf(x[indices], y[indices], julia[indices])
+ax.set_xlabel('x')
+ax.set_ylabel('y')
+ax.set_zlabel("$F_{sss}(x\mathbf{i}, y\mathbf{j})$")
+ax.ticklabel_format(scilimits = (0, 0))
+plt.savefig('../images/ball-sss.png', bbox_inches = 'tight')

### 2023-03-29 paper.tex
Fix a typo
Add an example with a ball

@@
 
-\subsection{A disk}
-If we define $f(x, y) = x^2 + y^2$ then an inequation $f(x, y) \le R^2$ defines
-a disk of radius $R$ with center at the origin. In this case $F_{ss}$ depends
-only on distance $r$ from the origin:
+\subsection{A disk and a ball}
+Define $f(\bm{x}) = \sum_i x_i^2$. If $\bm{x} \in \mathbb{R}^2$ when an
+inequation $f(\bm{x}) \le R^2$ defines a disk of radius $R$ with the center at
+the origin. In this case $F_{ss}$ depends only on distance $r$ from the origin:
 \begin{equation*}
@@
 with different resolution with a theory is shown on \cref{fig:fss-disk}.
-\begin{figure*}[!pt]
+\begin{figure*}[!hpt]
   \centering
@@
   \caption[]{Plot of surface-surface function for a disk with radius
-    $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
+    $R = 0.334$. Resolution of the image varies from $100\times 100$ pixels to
     $3100\times 3100$.}
   \label{fig:fss-disk}
+\end{figure*}
+
+If $\bm{x} \in \mathbb{R}^3$ then an inequation $f(\bm{x}) \le R^2$ defines a
+ball. In this case we provide a comparison (\cref{fig:fsss-ball}) of the
+algorithm in \cref{sec:algo} with the precise algorithm in
+\cref{sec:fsss-3d}. There is no known analytic solution for this case.
+\begin{figure*}[!hpt]
+  \centering
+  \includegraphics[width=0.45\linewidth]{images/ball-sss.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{images/ball-sss-error.png}
+  \caption[]{On the left: Plot of $F_{sss}(\bm{r_1}, \bm{r_2})$ function
+    obtained by algorithm \cref{sec:algo} for a ball with radius
+    $R = 0.3$. $\bm{r_1}$ is parallel to a vector $\bm{i} = (1, 0, 0)$ and
+    $\bm{r_2}$ is parallel to a vector $\bm{j} = (0, 1, 0)$. Vectors $\bm{i}$
+    and $\bm{j}$ constitute a two dimensional parameter space for $F_{sss}$. On
+    the right: Relative error of computation. True values for $F_{sss}$ are
+    obtained by algorithm in \cref{sec:fsss-3d}.}
+  \label{fig:fsss-ball}
 \end{figure*}
@@
 this comparison is on \cref{fig:fss-blob}.
-\begin{figure*}[!pt]
+\begin{figure*}[!hpt]
   \centering
@@
 comparison between two algorithms is on \cref{fig:fss-ellipses}.
-\begin{figure*}[!pt]
+\begin{figure*}[!hpt]
   \centering
@@
 \cref{fig:fss-ellipses-5x5}.
-\begin{figure*}[!pt]
+\begin{figure*}[!hpt]
   \centering
@@
 \bibliography{paper}
-
 \end{document}

### 2023-03-29 paper.tex
Remove an old remark
Reorganize sections

@@
 \usepackage{cleveref}
+\usepackage[inline]{enumitem}
+\usepackage{resizegather}
 
@@
 
-\section{Algorithm for computation of surface functions}
+\section{Algorithm for computation of surface functions for digital images}
 \label{sec:algo}
@@
 input with high-pass filter to extract edges from the image. We use the
-following filter kernel $H$ \textcolor{red}{Is there notation for 3x3x3
-  ``matrices''?}:
-\begin{align}
+following filter kernel $H$:
+\begin{equation}
+  \begin{aligned}
     H_{ij} &= \frac{1}{6} \left[
@@
       \end{array}
-    \right] \label{eq:filter-3x3-2d} \\
+      \right] \\
     H_{ijk} &= \frac{1}{18} \left[
@@
       \end{array}
-    \right] \label{eq:filter-3x3-3d}
-\end{align}
+      \right]
+  \end{aligned}
+  \label{eq:filter-3x3}
+\end{equation}
 Here symbol $;$ denotes concatenation along the third dimension. Edge extraction
@@
   \label{fig:Fsss-pattern}
+\end{figure}
+
+In addition to filter $H$ we propose an improved filter $H'$. The rationale
+behind this improvement is that
+\begin{enumerate*}[label=\alph*)]
+\item A filter of width 3 is too narrow to give a good approximation for surface
+  functions.
+\item Filter $H$ is not invariant under rotations, i.e.
+  $H*\phi(A) \ne \phi(H*A)$ where $\phi$ is a rotation operator.
+\end{enumerate*}
+Filter $H'$ has a length $7$ and all coefficients with exception of the central
+coefficient are inversely proportional to the distance from the center:
+\begin{equation}
+  \begin{aligned}
+    H'_{ij} &= S \left\{
+    \begin{array}{cc}
+      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2}} & \quad i \ne 3, j \ne 3 \\
+      C & \quad \text{otherwise}
+    \end{array}
+    \right. \\
+    H'_{ijk} &= S \left\{
+    \begin{array}{cc}
+      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2 + (k-3)^3}} & \quad i \ne 3, j \ne 3, k
+      \ne 3 \\
+      C & \quad \text{otherwise}
+    \end{array}
+    \right.
+  \end{aligned}
+  \label{eq:filter-7x7}
+\end{equation}
+where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
+$30.45849$ in 2D and $172.96232$ in 3D case.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
+  \caption[]{Left, center: images $A$ and $B$ used in the experiment for
+    approximation of $1 / \sin \phi$. Right: Interfaces between phases are
+    line segments which intersect each other at angle $\phi$. Shaded area is
+    where $|(H*A)\cdot(H*B)|$ has non-zero values. Sum of all values in this
+    area equals to $1 / \sin \phi$.}
+  \label{fig:experiment-setup}
+\end{figure}
+Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
+between black and white areas cross each other at the angle $\phi$. We apply a
+edge detection filter to each image, multiply results element-wise and sum all
+elements of the product. We want an obtained value to approximate
+$1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
+better than $H$. Why it's so important will be explained in the next section.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
+  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ in the
+    experiment on \cref{fig:experiment-setup}.}
+  \label{fig:filter-comparison}
 \end{figure}
@@
 $\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_A(\bm{x})|$
-and therefore \cref{eq:fss-2d-sin} and \cref{eq:fss} define the same function.
+and therefore \cref{eq:fss-2d-sin} and \cref{eq:fss} define the same
+function. This equation for $F_{ss}$ also explains why edge detection filters
+need to approximate $1/\sin \phi_k$ and why the filter \cref{eq:filter-7x7} is
+better than \cref{eq:filter-3x3}.
 
@@
 calculated with the fast algorithm (\cref{sec:algo}) with results of the new
-algorithm. We will use the filter $H$ (\ref{eq:filter-3x3-2d}) for edge
-detection along with a new filter $H'$ (\ref{eq:filter-5x5-2d}) described in
-\cref{sec:improvement}.
+algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
+detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
+paper.
 
@@
 
-\section{Improvement of the fast algorithm}
-\label{sec:improvement}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
-  \caption[]{Left, center: images $A$ and $B$ used in the experiment described
-    in \cref{sec:improvement}. Right: Interfaces between phases are line
-    segments which intersect each other at angle $\phi$. Shaded area is where
-    $(H*A)\cdot(H*B)$ has non-zero values.}
-  \label{fig:experiment-setup}
-\end{figure}
-Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
-between black and white cross each other at the angle $\phi$. We apply the
-filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
-element-wise and sum all elements of the product. An obtained value must
-approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
-surface-surface function. With filter described in \cref{sec:algo} we get a
-picture as on \cref{fig:angles-3x3}. We see that $H$ approximates
-$1/\sin \phi$ not very good.
-
-Now, let's try a wider filter $H'$:
-\begin{align}
-  H'_{ij} &= \frac{1}{30} \left[
-    \begin{array}{ccccc}
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & -24 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-    \end{array}
-    \right] \label{eq:filter-5x5-2d} \\
-  H'_{ijk} &= \frac{1}{150} \left[
-    \begin{array}{ccccc}
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-    \end{array} ;
-    \begin{array}{ccccc}
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & -124 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-    \end{array} ;
-    \begin{array}{ccccc}
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-      1 & 1 & 1 & 1 & 1 \\
-    \end{array}
-    \right] \label{eq:filter-5x5-3d}
-\end{align}
-With this filter we get a different picture (\cref{fig:angles-5x5}). A
-comparison of the fast algorithm with a wider filter kernel with a precise
-calculation for a ``blob'' described in \cref{sec:gauss} is show on
-\cref{fig:fss-blob-5x5}. A case with ellipses from \cref{sec:ellipses} is on
-\cref{fig:fss-ellipses-5x5}.
-\begin{figure*}[!hpt]
-  \centering
-  \subfigure[$3\times 3$ kernel $H$]{
-    \includegraphics[width=0.45\linewidth]{images/angles-3x3.png}
-    \label{fig:angles-3x3}}
-  \hfill
-  \subfigure[$5\times 5$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/angles-5x5.png}
-    \label{fig:angles-5x5}}
-  \caption[]{Estimation of $1/\sin\phi$ where $\phi$ is the angle between
-    tangent lines to the interface by filters $H$ and $H'$.}
-  \label{fig:angles}
-\end{figure*}
-
 \section{Results}

### 2023-03-29 paper.tex
Fix typos and errors

@@
 \begin{equation*}
-  A' = H*A = F^{-1}[F[H] F[A]]
+  A' = |H*A| = |F^{-1}[F[H] F[A]]|
 \end{equation*}
@@
   \Procedure{surfsurf}{$A$}
-  \State $A' \gets H*A$
+  \State $A' \gets |H*A|$
   \Comment{$A'$ becomes an interface of $A$.}
@@
   \Procedure{surfvoid}{$A$}
-  \State $A' \gets A*H$
+  \State $A' \gets |H*A|$
   \Comment{$A'$ becomes an interface of $A$.}
@@
   \Procedure{surfsurfsurf}{$A$, $\bm{r_1}$, $\bm{r_2}$}
-  \State $A' \gets A*H$
+  \State $A' \gets |H*A|$
   \Comment{$A'$ becomes an interface of $A$.}
@@
     where $|(H*A)\cdot(H*B)|$ has non-zero values. Sum of all values in this
-    area equals to $1 / \sin \phi$.}
+    area approximates $1 / \sin \phi$.}
   \label{fig:experiment-setup}
@@
 Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
-between black and white areas cross each other at the angle $\phi$. We apply a
+between black and white areas cross each other at the angle $\phi$. We apply an
 edge detection filter to each image, multiply results element-wise and sum all

### 2023-03-30 paper.tex
Rename a section 'Problems of verification'

@@
 \cref{sec:algo} we describe the all methodological details for "discrete" method
-for digital images. Next, in \cref{sec:verify} we explain in detail why
+for digital images. Next, in \cref{sec:algo-precise} we explain in detail why
 verification of computational approaches for digital images is currently
@@
 More detailed information on surface correlation functions can be found in
-\cref{sec:verify} and comprehensive Torquato's book \cite{Torquato_book}.
+\cref{sec:algo-precise} and comprehensive Torquato's book \cite{Torquato_book}.
 
-\section{Algorithm for computation of surface functions for digital images}
+\section{Computation of surface functions for digital images}
 \label{sec:algo}
@@
 
-\section{Problem of verification}
-\label{sec:verify}
-In paper \textcolor{red}{our paper} we tested these algorithms against known
-analytic solutions. Although we obtained acceptable results in the cases of
+\section{Computation of surface functions for sets with smooth boundary}
+\label{sec:algo-precise}
+In paper \textcolor{red}{our paper} we tested our algorithms for digital images
+against known analytic solutions. Although we obtained acceptable results in the cases of
 overlapping balls and disks, we were not sure if our algorithm performs good in
-general and searched for more test cases. Here we briefly discuss dual numbers
-and autodifferentiation technique and present another case: two- and
-three-dimensional sets with smooth boundary.
+general and searched for more test cases. Here we present another test case and
+develop an algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
+two- and three-dimensional sets with smooth boundary.
 

### 2023-03-30 scripts&data/filter-comparison.py
Add a script for filter comparison

@@ -1,0 +1,19 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fn(x):
+    return 1/np.sin(x)
+
+data = np.load('filter-comparison.npy')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+plt.plot(data[:,0], fn(data[:,0]))
+plt.plot(data[:,0], data[:,1])
+plt.plot(data[:,0], data[:,2])
+plt.xlabel('$\phi$')
+plt.ylabel('$1/\sin \phi$')
+plt.legend(['Exact value', 'Approximation by $H$', "Approximation by $H'$"])
+plt.savefig('../images/filter-comparison.png')

### 2023-03-30 paper.tex
Merge sections 'Results' and 'Examples...'

@@
 \cref{sec:fss-2d}. The choice of verification cases is presented in
-\textcolor{red}{Fix reference} followed by improvements in methodology of
-Samarin et al. The paper concludes with discussion, outline and summary in
-\cref{sec:summary}.
+\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
+paper concludes with discussion, outline and summary in \cref{sec:summary}.
 
@@
 
-\section{Examples of two-dimensional sets with smooth boundary}
-\label{seq:examples}
+\section{Results}
+\label{sec:results}
 In this section we will provide few examples of sets for which the developed
@@
 
-\section{Results}
+\section{Conclusion}
+% Is this a right label?
+\label{sec:summary}
+In this paper we develop an algorithm for precise calculation of surface-surface
+correlation function for two-dimensional sets with smooth boundary and checked
+our fast algorithm using these new cases. The fast algorithm was improved using
+a wider filter $H'$.
+
 \begin{figure}
@@
 where $x_i$ belong to a set
-$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$ (here we assume image
-dimensions to be $1 \times 1 \times 1$ length units). Taking
-$\epsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
-for filter $H'$.
+$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
+get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter $H'$.
 
@@
 
-\section{Conclusion}
-% Is this a right label?
-\label{sec:summary}
-In this paper we develop an algorithm for precise calculation of surface-surface
-correlation function for two-dimensional sets with smooth boundary and checked
-our fast algorithm using these new cases. The fast algorithm was improved using
-a wider filter $H'$.
-
 \bibliography{paper}

### 2023-03-30 paper.tex
Cite our implementation

@@
 precise algorithm is applicable and compare the surface-surface function
-calculated with the fast algorithm (\cref{sec:algo}) with results of the new
-algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
+calculated with the algorithm for digital images (\cref{sec:algo}) with results
+of the new algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
 detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
@@
 compute precise values of $F_{ss}$ for this blob and compare them with values
-obtained by using the fast algorithm in section \cref{sec:algo}. The result of
-this comparison is on \cref{fig:fss-blob}.
+obtained by using the algorithm in section \cref{sec:algo}. The result of this
+comparison is on \cref{fig:fss-blob}.
 \begin{figure*}[!hpt]
@@
 correlation function for two-dimensional sets with smooth boundary and checked
-our fast algorithm using these new cases. The fast algorithm was improved using
-a wider filter $H'$.
+our algorithm for digital images using these new cases. The algorithm was
+improved using a wider filter $H'$.
 
@@
 
+An implementation of the precise algorithm for sets with smooth boundary is
+available on GitHub\cite{diff-boundary-corrfn}.
+
 \bibliography{paper}

### 2023-04-05 paper.tex
Introduce a conventional unit of measurement

@@
 \cite{jiao2014chawla,EPL1}. These functions are defined for media with
-dimensionality of 2 and higher and have units of measurement $m^{-1}$ for
-$F_{sv}$ and $m^{-2}$ for $F_{ss}$.
+dimensionality of 2 and higher. $F_{sv}$ is a physical quantity inversely
+proportional to length and $F_{ss}$ is inversionaly proportional to surface
+area. SI units of measurement for these functions are $m^{-1}$ for $F_{sv}$
+and $m^{-2}$ for $F_{ss}$. In practice non-standard units of measurement can be
+used instead.
 
@@
 \end{equation}
-This function is defined for media with dimensionality 3 or higher and has unit
-of measurement $m^{-3}$. For three-dimensional media $F_{sss}$ is a function of
-six scalar arguments: $\bm{r_1} = (r_{1x}, r_{1y}, r_{1z})$ and
-$\bm{r_2} = (r_{2x}, r_{2y}, r_{2z})$. However if the medium under consideration
-is isotropic, only three scalar arguments $r_1 = |\bm{r_1}|$, $r_2 = |\bm{r_2}|$
-and $r_3 = |\bm{r_1} - \bm{r_2}|$ are required. The last argument can be
-replaced with an angle $\theta$ between vectors $\bm{r_1}$ and $\bm{r_2}$:
+This function is defined for media with dimensionality 3 or higher and is a
+physical quantity inversely proportional to volume. SI units for $F_{sss}$ are
+$m^{-3}$ but other units can be used in practice. For three-dimensional media
+$F_{sss}$ is a function of six scalar arguments:
+$\bm{r_1} = (r_{1x}, r_{1y}, r_{1z})$ and $\bm{r_2} = (r_{2x}, r_{2y}, r_{2z})$.
+However if the medium under consideration is isotropic, only three scalar
+arguments $r_1 = |\bm{r_1}|$, $r_2 = |\bm{r_2}|$ and $r_3 = |\bm{r_1} - \bm{r_2}|$
+are required. The last argument can be replaced with an angle $\theta$ between
+vectors $\bm{r_1}$ and $\bm{r_2}$:
 \begin{equation*}
@@
 
-From now on when considering $F_{ss}$ and $F_{sv}$ functions we will work with
-square images which have unit area, so we can omit division by $N$ in described
+From now on we introduce a conventional unit of measurement ($cu$) for length.
+When considering $F_{ss}$ and $F_{sv}$ functions we will work with square images
+with side equal to $1\ cu$, so we can omit division by $N$ in described
 algorithms and ensemble average in \cref{eq:fss} and \cref{eq:fsv} becomes a
 double integral over a square $[0, 1]^2$. When considering $F_{sss}$ function we
-will work with cubic images which have unit volume. Then we can also omit
+will work with cubic images with side equal to $1\ cu$. Then we can also omit
 division by $N$ and ensemble average in \cref{eq:fsss} becomes a triple integral
-over a cube $[0, 1]^3$.
+over a cube $[0, 1]^3$. On plots of surface functions we will omit units of
+measurements in captions (e.g. we will write ``$F_{ss}$'' instead of
+``$F_{ss}, cu^{-2}$'').
 

### 2023-04-05 paper.tex
Fix caption

@@
   \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
-    implementation is a right triangle with varying catets $r_1$ and
-    $r_2$. Patterns can lie in planes $XY$ (as on the picture), $XZ$ or
-    $YZ$. Black dots depict elements of $A'$}
+    implementation is a right triangle with fixed catets $r_1$ and $r_2$.
+    Patterns can lie in planes $XY$ (as on the picture), $XZ$ or $YZ$. This
+    pattern is moved over the input which results in all possible distinct
+    configurations. Black dots depict elements of $A'$.}
   \label{fig:Fsss-pattern}
@@
 This case is also handled good by the algorithm described in
-\cref{sec:algo}. \textcolor{red}{Any picture/plot here?}.
+\cref{sec:algo}. Plot of $F_{sss}$ for this case is trivial and not shown here.
 
@@
 
-\section{Conclusion}
-% Is this a right label?
-\label{sec:summary}
-In this paper we develop an algorithm for precise calculation of surface-surface
-correlation function for two-dimensional sets with smooth boundary and checked
-our algorithm for digital images using these new cases. The algorithm was
-improved using a wider filter $H'$.
+\subsection{Influence of filter $H'$ on cases not covered by the new algorithm}
+In this section we show how filter $H'$ affects calculation of surface-functions
+in cases not covered by the algorithm described in \cref{sec:fss-2d} and
+\cref{sec:fsss-3d}.
 
@@
 
+\section{Conclusion}
+% Is this a right label?
+\label{sec:summary}
+In this paper we develop an algorithm for precise calculation of $F_{ss}$
+function for two-dimensional sets and $F_{sss}$ function for three-dimensional
+sets. These sets must have smooth boundary for the algorithm to be
+applicable. With help of this algorithm we introduce some new test cases and
+check our algorithm for digital images more thoroughly. The algorithm is
+improved using a wider filter $H'$.
+
 An implementation of the precise algorithm for sets with smooth boundary is

### 2023-04-05 paper.tex
Plot not shown
Move text from conclusion to results

@@
   \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
-    implementation is a right triangle with fixed catets $r_1$ and $r_2$.
-    Patterns can lie in planes $XY$ (as on the picture), $XZ$ or $YZ$. This
-    pattern is moved over the input which results in all possible distinct
-    configurations. Black dots depict elements of $A'$.}
+    implementation is a right triangle with varying catets $r_1$ and
+    $r_2$. Patterns can lie in planes $XY$ (as on the picture), $XZ$ or
+    $YZ$. Black dots depict elements of $A'$}
   \label{fig:Fsss-pattern}

### 2023-04-05 paper.tex
More plots for the god of plots!

--- 2023-04-05 paper.tex
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{images/ball-3d-ss.png}
-  \caption[]{Surface-surface function calculated for a three-dimensional ball
-    with radius $R = 0.24$ using filters $H$ and $H'$. Theoretical curve is
-    provided for a comparison. Image dimensions are $450 \times 450 \times 450$.}
-  \label{fig:fss-ball}
-\end{figure}
-With the new filter calculation of $F_{ss}$ becomes more precise, even for
+  \subfigure[Surface-surface function calculated for a ball with radius
+    $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
+    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
+    \label{fig:fss-ball}}
+  \hfill
+  \subfigure[Surface-void function calculated for a disk with radius
+    $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
+    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
+    \label{fig:fsv-disk}}
+  \hfill
+  \subfigure[Surface-void function calculated for a ball with radius
+    $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
+    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
+    \label{fig:fsv-ball}}
+  \caption[]{Comparison of filters $H$ and $H'$ for cases in which newly
+    developed algorithms \cref{sec:fss-2d}, \cref{sec:fsss-3d} are not
+    applicable. Theoretical curves are provided for each case.}
+  \label{fig:not-covered}
+\end{figure*}
+With the new filter calculation of $F_{ss}$ becomes more precise also for
 three-dimensional images. This can be seen in comparison with theoretical values
@@
 $(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
-get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter $H'$.
+get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter
+$H'$. Calculation of surface-void function also benefits from the new filter
+(\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
 

### 2023-04-05 scripts&data/fsv-ball.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def sv(x, R):
+    return np.where(x < 2*R, np.pi*R*x + 2*np.pi*R**2, 4*np.pi*R**2)
+
+data3 = np.loadtxt('ball-sv-3.dat')
+data7 = np.loadtxt('ball-sv-7.dat')
+x = np.linspace(0, 0.5, data3.size)
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+plt.plot(x, sv(x, 0.2))
+plt.plot(x, data3)
+plt.plot(x, data7)
+plt.legend(['Theory', 'Filter $H$', "Filter $H'$"])
+plt.xlabel('$r$')
+plt.ylabel('$F_{sv}(r)$')
+plt.savefig('../images/fsv-ball.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/fsv-disk.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def sv(x, R):
+    return np.where(x < 2*R, 2*R*(np.pi - np.arccos(x/(2*R))), 2*R*np.pi)
+
+data3 = np.loadtxt('disk-sv-3.dat')
+data7 = np.loadtxt('disk-sv-7.dat')
+x = np.linspace(0, 0.5, data3.size)
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+plt.plot(x, sv(x, 0.2))
+plt.plot(x, data3)
+plt.plot(x, data7)
+plt.legend(['Theory', 'Filter $H$', "Filter $H'$"])
+plt.xlabel('$r$')
+plt.ylabel('$F_{sv}(r)$')
+plt.savefig('../images/fsv-disk.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/ball.py
Update plots

@@ -28,12 +28,12 @@ plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 18)
 
 x = np.linspace(0, 0.5, 1000)
-plt.plot(np.linspace(0, 0.5, data3.size), data3 * 450**2, 'b', linewidth = 1.2)
-plt.plot(np.linspace(0, 0.5, data5.size), data5 * 450**2, 'g', linewidth = 1.2)
-plt.plot(x, ss(x, R), 'r', linewidth = 1.2)
+plt.plot(x, ss(x, R))
+plt.plot(np.linspace(0, 0.5, data3.size), data3 * 450**2)
+plt.plot(np.linspace(0, 0.5, data5.size), data5 * 450**2)
 plt.ylim([0, 10])
 plt.xlim([0.03, 0.5])
 plt.xlabel('$r$')
 plt.ylabel('$F_{ss}(r)$')
-plt.legend(['Filter 3x3', 'Filter 5x5', 'Therory'])
-plt.savefig('../images/ball-3d-ss.png')
+plt.legend(['Therory', 'Filter $H$', "Filter $H'$"])
+plt.savefig('../images/ball-3d-ss.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/filter-comparison.py

@@ -16,4 +16,4 @@ plt.plot(data[:,0], data[:,2])
 plt.xlabel('$\phi$')
 plt.ylabel('$1/\sin \phi$')
 plt.legend(['Exact value', 'Approximation by $H$', "Approximation by $H'$"])
-plt.savefig('../images/filter-comparison.png')
+plt.savefig('../images/filter-comparison.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/plot-ss.py

@@ -18,8 +18,8 @@ xs = np.linspace(0, 0.5, 1000)
 plt.xlim([0, 0.1])
 plt.ylim([0, 4])
 plt.plot(xs, ss(xs, 0.0334), linewidth = 1.2)
-plt.ticklabel_format(axis = "x", scilimits = (0, 0))
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
 plt.legend(legend + ['Theory'])
-plt.xlabel('Correlation length $r$, m')
-plt.ylabel('$F_{ss}(r)$, $m^{-2}$')
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$F_{ss}(r)$')
 plt.savefig('../images/fss-disk-3x3.png')

### 2023-04-05 scripts&data/plot-sss-error.py

@@ -28,5 +28,5 @@ ax.plot_trisurf(x[indices], y[indices], error[indices])
 ax.set_xlabel('x')
 ax.set_ylabel('y')
 ax.set_zlabel('Relative error')
-ax.ticklabel_format(scilimits = (0, 0))
+ax.ticklabel_format(scilimits = (0, 0), useMathText = True)
 plt.savefig('../images/ball-sss-error.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/plot-sss.py

@@ -18,5 +18,5 @@ ax.plot_trisurf(x[indices], y[indices], julia[indices])
 ax.set_xlabel('x')
 ax.set_ylabel('y')
 ax.set_zlabel("$F_{sss}(x\mathbf{i}, y\mathbf{j})$")
-ax.ticklabel_format(scilimits = (0, 0))
+ax.ticklabel_format(scilimits = (0, 0), useMathText = True)
 plt.savefig('../images/ball-sss.png', bbox_inches = 'tight')

### 2023-04-05 paper.tex
Fix a typo
Update plots
Join two images

@@
         1 & 1 & 1 \\
-        1 & -24 & 1 \\
+        1 & -26 & 1 \\
         1 & 1 & 1
@@
   \hfill
-  \subfigure[$5\times 5$ kernel $H'$]{
+  \subfigure[$7\times 7$ kernel $H'$]{
     \includegraphics[width=0.45\linewidth]{images/fss-disk-5x5.png}
@@
   \caption[]{Plot of surface-surface function for a disk with radius
-    $R = 0.334$. Resolution of the image varies from $100\times 100$ pixels to
+    $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
     $3100\times 3100$.}
@@
 \label{sec:gauss}
-\begin{figure}
+\begin{figure*}[!hpt]
   \centering
-  \includegraphics[width=0.8\linewidth, frame]{images/blob.png}
-  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
+  \subfigure[An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
     which consists of four Gaussian functions. White area is where
-    $f(x,y) \le 3$.}
-  \label{fig:blob}
-\end{figure}
+    $f(x,y) \le 3$.] {
+    \includegraphics[width=0.45\linewidth, frame]{images/blob.png}
+    \label{fig:blob}}
+  \hfill
+  \subfigure[An example of generated ellipses.] {
+    \includegraphics[width=0.45\linewidth, frame]{images/ellipses.png}
+    \label{fig:ellipses}}
+  \caption[]{Examples of sets with smooth boundary.}
+\end{figure*}
 Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
@@
   \hfill
-  \subfigure[$5\times 5$ kernel $H'$]{
+  \subfigure[$7\times 7$ kernel $H'$]{
     \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
@@
 \label{sec:ellipses}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth, frame]{images/ellipses.png}
-  \caption[]{An example of generated ellipses.}
-  \label{fig:ellipses}
-\end{figure}
 Take $N$ random values $a_i$, $b_i$, $c_i$, $x^c_i$ and $y^c_i$ and define
@@
   \hfill
-  \subfigure[$5\times 5$ kernel $H'$]{
+  \subfigure[$7\times 7$ kernel $H'$]{
     \includegraphics[width=0.45\linewidth]{images/fss-ellipses-5x5.png}

### 2023-04-05 scripts&data/calc-disk.jl
Upldate plots with disks

@@ -1,8 +1,17 @@
 module Torquatsky
 using DelimitedFiles
+using Images
 import CorrelationFunctions.Map as M
 import CorrelationFunctions.Utilities as U
 export do_it!
+
+struct FuckKernel <: U.AbstractKernel
+end
+
+const foo = [1 1 1; 1 -8 1; 1 1 1]
+
+U.extract_edges(array :: AbstractArray, filter :: FuckKernel, topology :: U.AbstractTopology) =
+    abs.(imfilter(array, centered(foo / 6), U.edge2pad(topology)))
 
 function draw_ball(s, r)
     array = falses(s)
@@ -20,13 +29,12 @@ end
 
 function do_it!()
     R = 0.0334
-    flt = U.EdgeFilter(U.BCPeriodic(), U.Kernel3x3())
     for side in 100:100:3100
         disk = draw_ball((side, side), R*side)
         println(side)
         println(U.lowfreq_energy_ratio(disk))
 
-        ss = M.surfsurf(disk, false; periodic = true, filter = flt) |> M.average_directions
+        ss = M.surf2(disk, false; periodic = true, filter = U.ConvKernel(7)) |> M.average_directions
 
         open("disks-$(side)-we-ss.dat", "w") do out
             writedlm(out, ss)

### 2023-04-05 scripts&data/plot-ss.py

@@ -22,4 +22,4 @@ plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
 plt.legend(legend + ['Theory'])
 plt.xlabel('Correlation length $r$')
 plt.ylabel('$F_{ss}(r)$')
-plt.savefig('../images/fss-disk-3x3.png')
+plt.savefig('../images/fss-disk-7x7.png', bbox_inches = 'tight')

### 2023-04-05 scripts&data/calc-blob.jl
Update more plots

@@ -5,9 +5,16 @@ using FFTW
 import CorrelationFunctions.Map as M
 import CorrelationFunctions.Utilities as U
 
-flt = U.EdgeFilter(U.BCPeriodic(), U.Kernel3x3())
+struct FuckKernel <: U.AbstractKernel
+end
+
+const foo = [1 1 1; 1 -8 1; 1 1 1]
+
+U.extract_edges(array :: AbstractArray, filter :: FuckKernel, topology :: U.AbstractTopology) =
+    abs.(imfilter(array, centered(foo / 6), U.edge2pad(topology)))
+
 for side in 500:500:3000
     data = load("field-$(side).pbm") .|> Gray |> BitArray;
     npzwrite("field-ss-$(side).npy",
-             fftshift(M.surfsurf(data, false; periodic = true, filter = flt)) * side^2)
+             fftshift(M.surf2(data, false; periodic = true, filter = U.ConvKernel(7))) * side^2)
 end

### 2023-04-05 scripts&data/compare-blob.py

@@ -26,6 +26,6 @@ for side in range(500, 3500, 500):
 plt.plot(phi, data_def[:, 0], linewidth = 1.2)
 plt.xlabel('$\phi$')
 plt.ylabel('$F_{ss}(R, \phi)$')
-plt.ylim([1,13])
+plt.ylim([0, 45])
 plt.legend(legend + ['Precise'])
-plt.savefig('../images/fss-blob-3x3.png')
+plt.savefig('../images/fss-blob-7x7.png', bbox_inches = 'tight')

### 2023-05-10 paper.tex
Upldate plots with disks
Update more plots
edit's to Vasya's text

@@
 \author{Marina V. Karsanina\textsuperscript{1}}
-\author{Aleksey Khlyupin\textsuperscript{1}}
+\author{Aleksey Khlyupin\textsuperscript{1,2}}
 \author{Kirill M. Gerke\textsuperscript{1}}
@@
   Russian Academy of Sciences, Moscow, 107031, Russia}
-%\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
-%  Lomonosov Moscow State University, Moscow, 119991, Russia}
+\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
+  Dolgoprudny, 141701, Russia}
 %\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
@@
 dimensionality of 2 and higher. $F_{sv}$ is a physical quantity inversely
-proportional to length and $F_{ss}$ is inversionaly proportional to surface
+proportional to length and $F_{ss}$ is inversely proportional to surface
 area. SI units of measurement for these functions are $m^{-1}$ for $F_{sv}$
@@
 physical quantity inversely proportional to volume. SI units for $F_{sss}$ are
-$m^{-3}$ but other units can be used in practice. For three-dimensional media
+$m^{-3}$, but relative units can be used in practice. For three-dimensional media
 $F_{sss}$ is a function of six scalar arguments:
@@
 \label{sec:algo}
-Here we briefly describe an algorithm for computation of surface-surface,
+Here we briefly describe the algorithm for computation of surface-surface,
 surface-void and surface-surface-surface correlation functions for digital
-images of porous media. A more detailed description can be found in a paper of
+images of porous media. A more detailed description can be found in the recent paper of
 Samarin et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
 correlation functions for all possible directions and correlation lengths. It
-consists of two stages: edge detection stage and computation of autocorrelation.
+consists of two steps: edge detection and computation of autocorrelation.
 
-We give an image of porous medium in the form of two- or three-dimensional bit
+We consider an image of porous medium in the form of two- or three-dimensional bit
 array $A$ as the input to our algorithm. In the first stage, we convolve the
-input with high-pass filter to extract edges from the image. We use the
+input with high-pass filter to extract edges from the image. In our previous paper \cite{Samarin} we used the
 following filter kernel $H$:
@@
 
-In the second stage we calculate autocorrelation for $A'$ and divide it by a
+Next, we calculate autocorrelation for $A'$ and divide it by a
 total number of elements in $A$:
@@
 
-All in all we get the following algorithm for calculation of $F_{ss}$ function:
+Putting everything together, we obtain the following algorithm for calculation of $F_{ss}$ function:
 \begin{algorithmic}[1]
@@
 
-Algorithm for surface-void function $F_{sv}$ is similar:
+Algorithm for surface-void function $F_{sv}$ computation is similar:
 \begin{algorithmic}[1]
@@
 
-A result $R_{ij}$ (resp. $R_{ijk}$) of either of two algorithms is an array of
+The results of either of two algorithms is an array of
 the same shape as $A$ which contains values of correlation function for the
@@
 
-For surface-surface-surface function $F_{sss}$ the former approach can also be
-used, but it would be highly inefficient memory-wise because for three
-dimensional case $F_{sss}$ is a function of six scalar coordinates which leads
-to a very large output array. Instead of this approach we use a slower approach
-which computes $F_{sss}$ at a specified point calculating a convolution using
+For surface-surface-surface function $F_{sss}$ the previously described approach can also be
+used, but it results in inefficient memory usage because for three-dimensional case $F_{sss}$ is a function of six scalar coordinates, which leads
+to a very large output array. Therefore, instead we use a somewhat slower, but more memory efficient, approach
+that computes $F_{sss}$ at a specified point calculating a convolution using
 its definition:
@@
 
-In addition to filter $H$ we propose an improved filter $H'$. The rationale
-behind this improvement is that
+In this work, in addition to filter $H$, we propose an improved filter $H'$. The rationale
+behind this improvement is that:
 \begin{enumerate*}[label=\alph*)]
-\item A filter of width 3 is too narrow to give a good approximation for surface
-  functions.
-\item Filter $H$ is not invariant under rotations, i.e.
-  $H*\phi(A) \ne \phi(H*A)$ where $\phi$ is a rotation operator.
+\item a filter of width 3 is too narrow to give a good approximation for surface
+  functions;
+\item filter $H$ is not invariant under rotations, i.e.
+  $H*R(A) \ne R(H*A)$, where $R$ is a rotation operator.
 \end{enumerate*}
-Filter $H'$ has a length $7$ and all coefficients with exception of the central
+Filter $H'$ has a length $7$ and all coefficients with exception to the central
 coefficient are inversely proportional to the distance from the center:
@@
 $1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
-better than $H$. Why it's so important will be explained in the next section.
+better than $H$. Why this is important will be explained in the next section.
 \begin{figure}
@@
   \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
-  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ in the
-    experiment on \cref{fig:experiment-setup}.}
+  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary images on \cref{fig:experiment-setup}.}
   \label{fig:filter-comparison}
@@
 In paper \textcolor{red}{our paper} we tested our algorithms for digital images
-against known analytic solutions. Although we obtained acceptable results in the cases of
-overlapping balls and disks, we were not sure if our algorithm performs good in
-general and searched for more test cases. Here we present another test case and
+against known analytic solutions. Although we obtained good results in the cases of
+overlapping balls and disks, weather our algorithm performs with the same high accuracy in
+general was still a question. In this section we present additional test case and
 develop an algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
@@
 
-It's useful to introduce an imaginary unit $\varepsilon$ and write a dual number
-$(a, b)$ as $a + b\varepsilon$. As you can see from multiplication law,
+It is also useful to introduce an imaginary unit $\varepsilon$ and write a dual number
+$(a, b)$ as $a + b\varepsilon$. As follows from the multiplication law,
 $1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
@@
 
-Here are some basic rules for working with dual numbers (some of which we have
-already described):
+Most useful basic rules for working with dual numbers can be summarized as follows:
 \begin{itemize}
@@
 
-As you can see, dual numbers are connected with differentiation. Using a dual
+As is evident from these rules, dual numbers are connected with differentiation. Using a dual
 argument $a + \varepsilon$ we can compute a value of a function at point $x = a$
@@
 \end{equation}
-The last equation will be useful for computation of normals to the interface in
+This last equation will be useful for computation of normals to the interface in
 next sections.
@@
 be replaced with a tangent line at the point of intersection
-(\cref{fig:fss-zoomed}). We get an expression for a surface of
+(\cref{fig:fss-zoomed}). Thus, we get an expression for a surface of
 intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
-acute angle between tangent lines. Hence, we get the following equation:
+acute angle between tangent lines. Hence, we obtain the following equation:
 \begin{equation}
@@
 $\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_A(\bm{x})|$
-and therefore \cref{eq:fss-2d-sin} and \cref{eq:fss} define the same
+and, therefore, \cref{eq:fss-2d-sin} and \cref{eq:fss} define the same
 function. This equation for $F_{ss}$ also explains why edge detection filters
@@
 where $\bm{a} = (a_x, a_y)$, $\bm{b} = (b_x, b_y)$. Jacobian determinant for
-this transformation is
+this transformation is:
 \begin{equation*}
@@
 
-We can rewritte \cref{eq:fss-2d-sin} using $J$ as follows:
+We can rewrite \cref{eq:fss-2d-sin} using $J$ as follows:
 \begin{equation}
@@
 $\bm{r} = (r_x, r_y)$. We find all intersections between a boundary $\Gamma$ and
-its translated version by solving a system of equations
+its translated version by solving a system of equations:
 \begin{equation*}
@@
 \end{equation*}
-which can be replaced by one equation
+which can now be replaced by a single equation:
 \begin{equation}
@@
 and $|f(x_i - r_x, y_i - r_y) - T| < \epsilon$ for some positive $\epsilon$ 
+(small value does not affect computation results, $\epsilon=0.04$ was used in all cases in this work)
 and then using these points as starting points for some algorithm based on
-gradient descent like ADAM to solve \cref{eq:inter}.
+gradient descent (ADAM \cite{adam} was used in this work) to solve \cref{eq:inter}.
 
@@
 \end{align*}
-$V_k$ is a volume of parallelepiped where all three multiplicands under integral
+where $V_k$ is a volume of parallelepiped where all three multiplicands under integral
 are non-zero. $N$ is a number of these parallelepipeds, i.e. number of points
@@
 \end{align*}
-Jacobian determinant for this transformation is
+The Jacobian determinant for this transformation is:
 \begin{equation*}
@@
 \end{equation*}
-and the expression for $F_{sss}$ becomes
+and the expression for $F_{sss}$ becomes:
 \begin{equation}
@@
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-disk-5x5.png}
+    \includegraphics[width=0.45\linewidth]{images/fss-disk-7x7.png}
     \label{fig:fss-disk-5x5}}
@@
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
+    \includegraphics[width=0.45\linewidth]{images/fss-blob-7x7.png}
     \label{fig:fss-blob-5x5}}
@@
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-5x5.png}
+    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-7x7.png}
     \label{fig:fss-ellipses-5x5}}

### 2023-05-11 paper.tex
Formatting fixes
More about acceptance criterion

@@
 phase $S$ and a set of void phase $V$. Surface-surface correlation function
-$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
+$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as
+follows:
 \begin{align}
@@
 surface-void and surface-surface-surface correlation functions for digital
-images of porous media. A more detailed description can be found in the recent paper of
-Samarin et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
-correlation functions for all possible directions and correlation lengths. It
-consists of two steps: edge detection and computation of autocorrelation.
+images of porous media. A more detailed description can be found in the recent
+paper of Samarin et~al. \textcolor{red}{cite paper} This algorithm can calculate
+surface correlation functions for all possible directions and correlation
+lengths. It consists of two steps: edge detection and computation of
+autocorrelation.
 
@@
 array $A$ as the input to our algorithm. In the first stage, we convolve the
-input with high-pass filter to extract edges from the image. In our previous paper \cite{Samarin} we used the
-following filter kernel $H$:
+input with high-pass filter to extract edges from the image. In our previous
+paper \cite{Samarin} we used the following filter kernel $H$:
 \begin{equation}
@@
 
-Putting everything together, we obtain the following algorithm for calculation of $F_{ss}$ function:
+Putting everything together, we obtain the following algorithm for calculation
+of $F_{ss}$ function:
 \begin{algorithmic}[1]
@@
 
-For surface-surface-surface function $F_{sss}$ the previously described approach can also be
-used, but it results in inefficient memory usage because for three-dimensional case $F_{sss}$ is a function of six scalar coordinates, which leads
-to a very large output array. Therefore, instead we use a somewhat slower, but more memory efficient, approach
-that computes $F_{sss}$ at a specified point calculating a convolution using
-its definition:
+For surface-surface-surface function $F_{sss}$ the previously described approach
+can also be used, but it results in inefficient memory usage because for
+three-dimensional case $F_{sss}$ is a function of six scalar coordinates, which
+leads to a very large output array. Therefore, instead we use a somewhat slower,
+but more memory efficient, approach that computes $F_{sss}$ at a specified point
+calculating a convolution using its definition:
 \begin{algorithmic}[1]
@@
 
-In this work, in addition to filter $H$, we propose an improved filter $H'$. The rationale
-behind this improvement is that:
+In this work, in addition to filter $H$, we propose an improved filter $H'$. The
+rationale behind this improvement is that:
 \begin{enumerate*}[label=\alph*)]
@@
   \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
-  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary images on \cref{fig:experiment-setup}.}
+  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary
+    images on \cref{fig:experiment-setup}.}
   \label{fig:filter-comparison}
@@
 against known analytic solutions. Although we obtained good results in the cases of
-overlapping balls and disks, weather our algorithm performs with the same high accuracy in
-general was still a question. In this section we present additional test case and
-develop an algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
-two- and three-dimensional sets with smooth boundary.
+overlapping balls and disks, weather our algorithm performs with the same high
+accuracy in general was still a question. In this section we present additional
+test case and develop an algorithm for calculation of $F_{ss}$ and $F_{sss}$
+functions for two- and three-dimensional sets with smooth boundary.
 
@@
 
-It is also useful to introduce an imaginary unit $\varepsilon$ and write a dual number
-$(a, b)$ as $a + b\varepsilon$. As follows from the multiplication law,
+It is also useful to introduce an imaginary unit $\varepsilon$ and write a dual
+number $(a, b)$ as $a + b\varepsilon$. As follows from the multiplication law,
 $1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
@@
 
-As is evident from these rules, dual numbers are connected with differentiation. Using a dual
-argument $a + \varepsilon$ we can compute a value of a function at point $x = a$
-and its derivative at that point:
+As is evident from these rules, dual numbers are connected with
+differentiation. Using a dual argument $a + \varepsilon$ we can compute a value
+of a function at point $x = a$ and its derivative at that point:
 $f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also we can compute a partial
@@
 and $|f(x_i - r_x, y_i - r_y) - T| < \epsilon$ for some positive $\epsilon$ 
-(small value does not affect computation results, $\epsilon=0.04$ was used in all cases in this work)
-and then using these points as starting points for some algorithm based on
-gradient descent (ADAM \cite{adam} was used in this work) to solve \cref{eq:inter}.
+(small value does not affect computation results, $\epsilon=0.04$ was used in
+all cases in this work) and then using these points as starting points for some
+algorithm based on gradient descent (ADAM \cite{adam} was used in this work) to
+solve \cref{eq:inter}.
 
@@
 \end{align*}
-where $V_k$ is a volume of parallelepiped where all three multiplicands under integral
-are non-zero. $N$ is a number of these parallelepipeds, i.e. number of points
-where all three boundaries (one ``original'' boundary and two translated
+where $V_k$ is a volume of parallelepiped where all three multiplicands under
+integral are non-zero. $N$ is a number of these parallelepipeds, i.e. number of
+points where all three boundaries (one ``original'' boundary and two translated
 versions) have an intersection. With $\Delta$ going to zero we get a convergence
@@
 calculating
-\begin{equation*}
+\begin{equation}
   error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
       F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
-\end{equation*}
-where $x_i$ belong to a set
-$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
-get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter
-$H'$. Calculation of surface-void function also benefits from the new filter
-(\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
+  \label{eq:error}
+\end{equation}
+where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
+$\epsilon = 0.01$ we get $error = 0.05$ for filter $H$ and $error = 0.03$ for
+filter $H'$. Calculation of surface-void function also benefits from the new
+filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
 
@@
 $H$ has faster convergence with increase of image resolution. Our
-acceptance criterion developed in \textcolor{red}{cite our paper again} works
-also for $H'$, but sometimes it's possible to calculate a poor estimate of
-$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
+acceptance criterion $C_{0.5} > 0.97$ developed in \textcolor{red}{cite our
+  paper again} works also for $H'$, but sometimes when the criterion is not
+satisfied, it's possible to calculate a poor estimate of $F_{ss}$ using $H$ but
+not $H'$. For example, consider images of a disk used for calculation of
+$F_{ss}$ on \cref{fig:fss-disk}. In \cref{table:crit} we provide values of
+$C_{0.5}$ criterion and errors \cref{eq:error} for filters $H$ and $H'$.
+
+Secondly, $H'$ behaves worse that $H$ in points
 of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
+
+\begin{table}[h!]
+  \centering
+  \begin{tabular}{|c | c | c | c|}
+    \hline
+    Dimensions & $C_{0.5}$ & Error ($H$) & Error ($H'$) \\
+    \hline
+    $100 \times 100$ & 0.822 & 0.178 & 0.408 \\
+    \hline
+    $400 \times 400$ & 0.921 & 0.072 & 0.098 \\
+    \hline
+    $3100 \times 3100$ & 0.972 & 0.049 & 0.009 \\
+    \hline
+  \end{tabular}
+  \caption{$C_{0.5}$ criterion and relative errors in computation of $F_{ss}$
+    for filters $H$ and $H'$. The case with a disk. Plots of $F_{ss}$ functions
+    can be seen on \cref{fig:fss-disk}.}
+  \label{table:crit}
+\end{table}
 

### 2023-05-11 paper.tex
More words about C0.5 parameter

--- 2023-05-10 paper.tex
@@
 calculating
-\begin{equation*}
+\begin{equation}
   error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
       F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
-\end{equation*}
-where $x_i$ belong to a set
-$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
-get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter
-$H'$. Calculation of surface-void function also benefits from the new filter
-(\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
+  \label{eq:error}
+\end{equation}
+where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
+$\epsilon = 0.01$ we get $error = 0.05$ for filter $H$ and $error = 0.03$ for
+filter $H'$. Calculation of surface-void function also benefits from the new
+filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
 
 Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
-$H$ has faster convergence with increase of image resolution. Our
-acceptance criterion developed in \textcolor{red}{cite our paper again} works
-also for $H'$, but sometimes it's possible to calculate a poor estimate of
-$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
+$H$ has faster convergence with increase of image resolution. We developed an
+acceptance parameter $C_{0.5}$ to determine if an image is suitable for
+processing with our algorithm or not. This parameter is defined as
+\begin{equation*}
+  C_{0.5} = \frac{\text{Power of the lower half of the image's
+      spectrum}}{\text{Power of the image}}
+\end{equation*}
+In this expression the words ``Power of the image'' are understood as $L^2$ norm
+of the image and ``the lower half of the \dots spectrum'' is the part of the
+spectrum (Fourier image) with frequencies $[-\omega_N/2, \omega_N/2]$ where
+$\omega_N$ is a Nyquist frequency for the image. It's important to firstly
+subtract the zeroth frequency (mean value) from the image before calculation of
+$C_{0.5}$. The image is suitable for processing if the acceptance criterion
+$C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and $H'$, but
+$H$ results in smaller error when $C_{0.5}$ is slightly less than 0.97. For
+example, consider images of a disk used for calculation of $F_{ss}$ for
+\cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for
+those images and relative errors in $F_{ss}$ \cref{eq:error} for both filters.
+
+Secondly, $H'$ behaves worse that $H$ in points
 of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
+
+\begin{figure*}[!hpt]
+  \centering
+  \subfigure[$C_{0.5}$ criterion]{
+    \includegraphics[width=0.45\linewidth]{images/c05.png}
+    \label{fig:c05}}
+  \hfill
+  \subfigure[Relative errors in computation of $F_{ss}$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-disk-errors.png}
+    \label{fig:relerr}}
+  \caption[]{Relative errors in function $F_{ss}$ for the case of a disk
+    (\cref{fig:fss-disk}) for filters $H$ and $H'$ and the acceptance parameter
+    $C_{0.5}$.}
+  \label{fig:error}
+\end{figure*}
 

### 2023-05-11 paper.tex
my aadons to check

--- 2023-05-10 paper.tex
@@
 
-\title{Surface correlation functions calculations: improving methodology for
-  discrete images with novel exact continuous approach}
+\title{The 2- and 3-point surface correlation functions calculations: from novel exact continuous 
+    approach to improving methodology for discrete images}
 
@@
 surface-void and surface-surface-surface correlation functions for digital
-images of porous media. A more detailed description can be found in the recent paper of
-Samarin et~al. \textcolor{red}{cite paper} This algorithm can calculate surface
+images of porous media \cite{Samarin}. This discrete algorithm can calculate surface
 correlation functions for all possible directions and correlation lengths. It
-consists of two steps: edge detection and computation of autocorrelation.
+consists of two steps: edge detection and computation of autocorrelation. Next,
+we present some improvements in this approach that later will be verified withthe help of
+exact continuous method.
 
+\subsection{Discrete method details}
 We consider an image of porous medium in the form of two- or three-dimensional bit
@@
 
+\subsection{Betterment of the discrete approach with improved edge filter}
 In this work, in addition to filter $H$, we propose an improved filter $H'$. The rationale
@@
 \begin{enumerate*}[label=\alph*)]
-\item a filter of width 3 is too narrow to give a good approximation for surface
-  functions;
+\item a filter of width 3 may turn to be too narrow to give a good approximation for 
+    particular structures;
 \item filter $H$ is not invariant under rotations, i.e.
@@
   \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
-  \caption[]{Left, center: images $A$ and $B$ used in the experiment for
-    approximation of $1 / \sin \phi$. Right: Interfaces between phases are
+  \caption[]{Left, center: images $Q1$ and $Q2$ used in the demostration of
+    approximation for $1 / \sin \phi$. Right: Interfaces between phases are
     line segments which intersect each other at angle $\phi$. Shaded area is
-    where $|(H*A)\cdot(H*B)|$ has non-zero values. Sum of all values in this
+    where $|(H*Q1\cdot(H*Q2)|$ has non-zero values. Sum of all values in this
     area approximates $1 / \sin \phi$.}
@@
 \end{figure}
-Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
+Consider two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
 between black and white areas cross each other at the angle $\phi$. We apply an
 edge detection filter to each image, multiply results element-wise and sum all
-elements of the product. We want an obtained value to approximate
+elements of the product. We want the resulting value to approximate
 $1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
@@
 
+\subsection{Units for computed surface correlation funtions}
 From now on we introduce a conventional unit of measurement ($cu$) for length.
@@
 \label{sec:algo-precise}
-In paper \textcolor{red}{our paper} we tested our algorithms for digital images
+Previously \cite{Samarin} we tested algorithms for digital images
 against known analytic solutions. Although we obtained good results in the cases of
 overlapping balls and disks, weather our algorithm performs with the same high accuracy in
-general was still a question. In this section we present additional test case and
-develop an algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
+general is still an open question. In this section we develop a universal test case and
+novel exact algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
 two- and three-dimensional sets with smooth boundary.
@@
 
-\section{Results}
+\section{Verification and computation results}
 \label{sec:results}
-In this section we will provide few examples of sets for which the developed
-precise algorithm is applicable and compare the surface-surface function
+In this section we consider a variety of examples of sets for which the developed
+precise algorithm is applicable. We intercompare surface-surface functions
 calculated with the algorithm for digital images (\cref{sec:algo}) with results
-of the new algorithm. We will use the filter $H$ (\ref{eq:filter-3x3}) for edge
+of the novel continuous algorithm. We also demostrate the work of both filter $H$ (\ref{eq:filter-3x3}) for edge
 detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
-paper.
+paper. We verify both digital and continuous methods against available analytical solutions.
 
@@
 \end{equation*}
-This case is also handled good by the algorithm described in
-\cref{sec:algo}. Plot of $F_{sss}$ for this case is trivial and not shown here.
+This case is also handled perfectly by the algorithm described in
+\cref{sec:algo}. Plot of $F_{sss}$ for the cube is trivially similar to \cref{fig:fss-square}
+and, thus, not shown here. We conclude that all approaches perform equaly accurately
+for this simple test.
 
@@
 \end{equation*}
-A comparison of the algorithm described in \cref{sec:algo} applied to images
-with different resolution with a theory is shown on \cref{fig:fss-disk}.
+The comparison of the algorithm described in \cref{sec:algo} applied to images
+with different resolution against theory is shown on \cref{fig:fss-disk}.
+Continuous approach results for the disk coincide with analytical $F_{ss}$ function.
 \begin{figure*}[!hpt]
@@
 algorithm in \cref{sec:algo} with the precise algorithm in
-\cref{sec:fsss-3d}. There is no known analytic solution for this case.
+\cref{sec:fsss-3d}. There is no known analytical solution for 3D ball (one could
+derive a solution in analogy with 2D case \cite{Torquato_book}, but this is a
+non-trivial task well beyond the scope of the current work).
 \begin{figure*}[!hpt]
@@
 \end{figure*}
+
+We conclude that continuous approach has zero error against analitical solution around
+can be used to assess the quality of digital approach for discretized sets. As expected,
+digital approach performance depends on the image resolution with new edge filter
+outperforming $H$.
 
@@
 \end{figure*}
-Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
+Let us now consider more complex surfaces, including concave shapes. Take $N$ random values
+of each of $a_i$, $b_i$ and $\sigma_i$. Let $f$ be:
 \begin{equation*}
@@
 obtained by using the algorithm in section \cref{sec:algo}. The result of this
-comparison is on \cref{fig:fss-blob}.
+comparison is presented on \cref{fig:fss-blob}.
 \begin{figure*}[!hpt]
@@
 
-\subsection{Influence of filter $H'$ on cases not covered by the new algorithm}
-In this section we show how filter $H'$ affects calculation of surface-functions
-in cases not covered by the algorithm described in \cref{sec:fss-2d} and
-\cref{sec:fsss-3d}.
+Again, we observe the convergence of continuous and discrete approaches to compute
+surface functions \cite{Samarin} that confirms the accuracy of results thus obtained.
+
+\subsection{Influence of filter $H'$ on computation accuracy}
 
@@
 \end{figure*}
-With the new filter calculation of $F_{ss}$ becomes more precise also for
+With the new filter the calculation of $F_{ss}$ becomes more precise also for
 three-dimensional images. This can be seen in comparison with theoretical values
@@
 
-\section{Conclusion}
-% Is this a right label?
+\section{Discussion, outlook and summary}
 \label{sec:summary}
-In this paper we develop an algorithm for precise calculation of $F_{ss}$
+The exact continuos method presented in this paper is developed only for surface-surface 
+function (and its 3-point counterpart). The surface-void function computations in digital manner 
+are much more robust and exhibit no noise \cite{ma2018SS,Samarin}. The filter $H'$ verified for 
+$F_{ss}$ also improves calculations for $F_{sv}$ (as evident from \cref{fig:not-covered}).
+
+In addition to obvious applications of surface correlations, as described in \cref{sec:intro}, 
+the development of robust computation techniques opens interesting research directions:
+\begin{enumerate}
+    \item Possibility to evaluate surface functions from small-angle scattering experiments \cite{theor_paper};
+    \item Finding overall trends in porous media structural evolution, e.g., based on experimental 
+        datasets \cite{Jose,Fomin,nano_structure};
+    \item Description of interfaces during multi-phase flow beyond conventional metrics (e.g.,
+        surface area or Minkowski functionals which are all subset of classical correlation functions)
+        \cite{Hassanizadeh,Armstrong}.
+\end{enumerate}
+This list immediately pops up from the authors' research activities and potentially is much wider.
+
+In summary, here we developed novel algorithm for precise calculation of $F_{ss}$
 function for two-dimensional sets and $F_{sss}$ function for three-dimensional
 sets. These sets must have smooth boundary for the algorithm to be
-applicable. With help of this algorithm we introduce some new test cases and
-check our algorithm for digital images more thoroughly. The algorithm is
-improved using a wider filter $H'$.
+applicable. With help of this new algorithm we introduced some additional testing
+techniques for digital computational methodology, including concave surface shapes. 
+In particular, we were able to demostrate the inmprovement in calculations of surface-surface
+and surface-viod correlation functions for digital binary images with the help of
+proposed $H'$ filter.
 
-An implementation of the precise algorithm for sets with smooth boundary is
-available on GitHub\cite{diff-boundary-corrfn}.
+An implementation of the precise continuous algorithm in Common Lisp for sets with smooth boundary is
+available on GitHub\cite{diff-boundary-corrfn}. Improved digital approach for both $F_{ss}$ and 
+$F_{sss}$ is now part of open source package CorrelationFunctions.jl written in Julia \cite{CFs.jl}.
 

### 2023-05-11 paper.tex
New paper.tex from Kirill

@@
 
-\title{The 2- and 3-point surface correlation functions calculations: from novel exact continuous 
-    approach to improving methodology for discrete images}
+\title{The 2- and 3-point surface correlation functions calculations: from novel
+  exact continuous approach to improving methodology for discrete images}
 
@@
 \subsection{Betterment of the discrete approach with improved edge filter}
-In this work, in addition to filter $H$, we propose an improved filter $H'$. The rationale
-behind this improvement is that:
+In this work, in addition to filter $H$, we propose an improved filter $H'$. The
+rationale behind this improvement is that:
 \begin{enumerate*}[label=\alph*)]
-\item a filter of width 3 may turn to be too narrow to give a good approximation for 
-    particular structures;
+\item a filter of width 3 may turn to be too narrow to give a good approximation
+  for particular structures;
 \item filter $H$ is not invariant under rotations, i.e.
@@
   \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
-  \caption[]{Left, center: images $Q1$ and $Q2$ used in the demostration of
+  \caption[]{Left, center: images $Q_1$ and $Q_2$ used in the demostration of
     approximation for $1 / \sin \phi$. Right: Interfaces between phases are
     line segments which intersect each other at angle $\phi$. Shaded area is
-    where $|(H*Q1\cdot(H*Q2)|$ has non-zero values. Sum of all values in this
+    where $|(H*Q_1\cdot(H*Q_2)|$ has non-zero values. Sum of all values in this
     area approximates $1 / \sin \phi$.}
@@
 \label{sec:algo-precise}
-Previously \cite{Samarin} we tested algorithms for digital images
-against known analytic solutions. Although we obtained good results in the cases of
-overlapping balls and disks, weather our algorithm performs with the same high accuracy in
-general is still an open question. In this section we develop a universal test case and
-novel exact algorithm for calculation of $F_{ss}$ and $F_{sss}$ functions for
-two- and three-dimensional sets with smooth boundary.
+Previously \cite{Samarin} we tested algorithms for digital images against known
+analytic solutions. Although we obtained good results in the cases of
+overlapping balls and disks, weather our algorithm performs with the same high
+accuracy in general is still an open question. In this section we develop a
+universal test case and novel exact algorithm for calculation of $F_{ss}$ and
+$F_{sss}$ functions for two- and three-dimensional sets with smooth boundary.
 
@@
 calculated with the algorithm for digital images (\cref{sec:algo}) with results
-of the novel continuous algorithm. We also demostrate the work of both filter $H$ (\ref{eq:filter-3x3}) for edge
-detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
-paper. We verify both digital and continuous methods against available analytical solutions.
+of the novel continuous algorithm. We also demonstrate the work of both filter
+$H$ (\ref{eq:filter-3x3}) for edge detection along with a new filter $H'$
+(\ref{eq:filter-7x7}) proposed in this paper. We verify both digital and
+continuous methods against available analytical solutions.
 
@@
 This case is also handled perfectly by the algorithm described in
-\cref{sec:algo}. Plot of $F_{sss}$ for the cube is trivially similar to \cref{fig:fss-square}
-and, thus, not shown here. We conclude that all approaches perform equaly accurately
-for this simple test.
+\cref{sec:algo}. Plot of $F_{sss}$ for the cube is trivially similar to
+\cref{fig:fss-square} and, thus, not shown here. We conclude that all approaches
+perform equaly accurately for this simple test.
 
@@
 
-We conclude that continuous approach has zero error against analitical solution around
-can be used to assess the quality of digital approach for discretized sets. As expected,
-digital approach performance depends on the image resolution with new edge filter
-outperforming $H$.
+We conclude that continuous approach has zero error against analitical solution
+around can be used to assess the quality of digital approach for discretized
+sets. As expected, digital approach performance depends on the image resolution
+with new edge filter outperforming $H$.
 
@@
 \end{figure*}
-Let us now consider more complex surfaces, including concave shapes. Take $N$ random values
-of each of $a_i$, $b_i$ and $\sigma_i$. Let $f$ be:
+Let us now consider more complex surfaces, including concave shapes. Take $N$
+random values of each of $a_i$, $b_i$ and $\sigma_i$. Let $f$ be:
 \begin{equation*}
@@
 
-Again, we observe the convergence of continuous and discrete approaches to compute
-surface functions \cite{Samarin} that confirms the accuracy of results thus obtained.
+Again, we observe the convergence of continuous and discrete approaches to
+compute surface functions \cite{Samarin} that confirms the accuracy of results
+thus obtained.
 
@@
 \label{sec:summary}
-The exact continuos method presented in this paper is developed only for surface-surface 
-function (and its 3-point counterpart). The surface-void function computations in digital manner 
-are much more robust and exhibit no noise \cite{ma2018SS,Samarin}. The filter $H'$ verified for 
-$F_{ss}$ also improves calculations for $F_{sv}$ (as evident from \cref{fig:not-covered}).
+The exact continuos method presented in this paper is developed only for
+surface-surface function (and its 3-point counterpart). The surface-void
+function computations in digital manner are much more robust and exhibit no
+noise \cite{ma2018SS,Samarin}. The filter $H'$ verified for $F_{ss}$ also
+improves calculations for $F_{sv}$ (as evident from \cref{fig:not-covered}).
 
-In addition to obvious applications of surface correlations, as described in \cref{sec:intro}, 
-the development of robust computation techniques opens interesting research directions:
+In addition to obvious applications of surface correlations, as described in
+\cref{sec:intro}, the development of robust computation techniques opens
+interesting research directions:
 \begin{enumerate}
-    \item Possibility to evaluate surface functions from small-angle scattering experiments \cite{theor_paper};
-    \item Finding overall trends in porous media structural evolution, e.g., based on experimental 
-        datasets \cite{Jose,Fomin,nano_structure};
-    \item Description of interfaces during multi-phase flow beyond conventional metrics (e.g.,
-        surface area or Minkowski functionals which are all subset of classical correlation functions)
-        \cite{Hassanizadeh,Armstrong}.
+    \item Possibility to evaluate surface functions from small-angle scattering
+      experiments \cite{theor_paper};
+    \item Finding overall trends in porous media structural evolution, e.g.,
+      based on experimental datasets \cite{Jose,Fomin,nano_structure};
+    \item Description of interfaces during multi-phase flow beyond conventional
+      metrics (e.g., surface area or Minkowski functionals which are all subset
+      of classical correlation functions) \cite{Hassanizadeh,Armstrong}.
 \end{enumerate}
-This list immediately pops up from the authors' research activities and potentially is much wider.
+This list immediately pops up from the authors' research activities and
+potentially is much wider.
 
-In summary, here we developed novel algorithm for precise calculation of $F_{ss}$
-function for two-dimensional sets and $F_{sss}$ function for three-dimensional
-sets. These sets must have smooth boundary for the algorithm to be
-applicable. With help of this new algorithm we introduced some additional testing
-techniques for digital computational methodology, including concave surface shapes. 
-In particular, we were able to demostrate the inmprovement in calculations of surface-surface
-and surface-viod correlation functions for digital binary images with the help of
-proposed $H'$ filter.
+In summary, here we developed novel algorithm for precise calculation of
+$F_{ss}$ function for two-dimensional sets and $F_{sss}$ function for
+three-dimensional sets. These sets must have smooth boundary for the algorithm
+to be applicable. With help of this new algorithm we introduced some additional
+testing techniques for digital computational methodology, including concave
+surface shapes.  In particular, we were able to demostrate the inmprovement in
+calculations of surface-surface and surface-viod correlation functions for
+digital binary images with the help of proposed $H'$ filter.
 
-An implementation of the precise continuous algorithm in Common Lisp for sets with smooth boundary is
-available on GitHub\cite{diff-boundary-corrfn}. Improved digital approach for both $F_{ss}$ and 
-$F_{sss}$ is now part of open source package CorrelationFunctions.jl written in Julia \cite{CFs.jl}.
+An implementation of the precise continuous algorithm in Common Lisp for sets
+with smooth boundary is available on GitHub\cite{diff-boundary-corrfn}. Improved
+digital approach for both $F_{ss}$ and $F_{sss}$ is now part of open source
+package CorrelationFunctions.jl written in Julia \cite{CFs.jl}.
 

### 2023-05-11 paper.tex

@@
 surface-void and surface-surface-surface correlation functions for digital
-images of porous media \cite{Samarin}. This discrete algorithm can calculate surface
-correlation functions for all possible directions and correlation lengths. It
-consists of two steps: edge detection and computation of autocorrelation. Next,
-we present some improvements in this approach that later will be verified withthe help of
-exact continuous method.
+images of porous media \cite{Samarin}. This discrete algorithm can calculate
+surface correlation functions for all possible directions and correlation
+lengths. It consists of two steps: edge detection and computation of
+autocorrelation. Next, we present some improvements in this approach that later
+will be verified with the help of exact continuous method.
 
@@
 calculating
-\begin{equation*}
+\begin{equation}
   error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
       F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
+  \label{eq:error}
+\end{equation}
+where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
+$\epsilon = 0.01$ we get $error = 0.05$ for filter $H$ and $error = 0.03$ for
+filter $H'$. Calculation of surface-void function also benefits from the new
+filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
+
+Unfortunately the filter $H'$ has some drawbacks in comparison with
+$H$. Firstly, $H$ has faster convergence with increase of image resolution. To
+demonstrate this we can use an acceptance parameter $C_{0.5}$ developed to
+determine if an image is suitable for processing with our algorithm or not. This
+parameter is defined as
+\begin{equation*}
+  C_{0.5} = \frac{\text{Power of the lower half of the image's
+      spectrum}}{\text{Power of the image}}
 \end{equation*}
-where $x_i$ belong to a set
-$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
-get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter
-$H'$. Calculation of surface-void function also benefits from the new filter
-(\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
+In this expression the words ``Power of the image'' are understood as $L^2$ norm
+of the image and ``the lower half of the \dots spectrum'' is the part of the
+spectrum (Fourier image) with frequencies $[-\omega_N/2, \omega_N/2]$ where
+$\omega_N$ is a Nyquist frequency for the image. It's important to firstly
+subtract the zeroth frequency (mean value) from the image before calculation of
+$C_{0.5}$. The image is suitable for processing if the acceptance criterion
+$C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and $H'$, but
+$H$ results in smaller error when $C_{0.5}$ is slightly less than 0.97. For
+example, consider images of a disk used for calculation of $F_{ss}$ on
+\cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for
+those images and relative errors in $F_{ss}$ (\cref{eq:error}) for both
+filters. It can be seen that $H$ gives twice the lower error than $H'$ when used
+for an image with $C_{0.5} \approx 0.82$.
 
-Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
-$H$ has faster convergence with increase of image resolution. Our
-acceptance criterion developed in \textcolor{red}{cite our paper again} works
-also for $H'$, but sometimes it's possible to calculate a poor estimate of
-$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
+Secondly, $H'$ behaves worse that $H$ in points
 of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
+
+\begin{figure*}[!hpt]
+  \centering
+  \subfigure[$C_{0.5}$ criterion]{
+    \includegraphics[width=0.45\linewidth]{images/c05.png}
+    \label{fig:c05}}
+  \hfill
+  \subfigure[Relative errors in computation of $F_{ss}$]{
+    \includegraphics[width=0.45\linewidth]{images/fss-disk-errors.png}
+    \label{fig:relerr}}
+  \caption[]{Relative errors in function $F_{ss}$ for the case of a disk
+    (\cref{fig:fss-disk}) for filters $H$ and $H'$ and the acceptance parameter
+    $C_{0.5}$.}
+  \label{fig:error}
+\end{figure*}
 

### 2023-05-12 paper.tex
final text changes from kg

@@
 \begin{abstract}
-  Here we are again.
+  Surface correlation functions are extremely useful descriptors of interfaces and in this role 
+  can be used in material science, rock and soil physics, food engineering and other numerous
+  areas. However, their widespread usage was hampered by insufficiently robust computation methodologies. 
+  In this contribution we elaborate on recent works in surface function evaluation and present a 
+  novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions for smooth boundary sets without 
+  discretization. This allows us to test digital computational approach on geometries beyond those with 
+  analytical solutions. Moreover, we propose a better edge detection filter that allowed to improve the 
+  quality of surface correlation functions (both surface-surface and surface-void) assessment based on 
+  digital images. The code for continuous and discrete computational frameworks is freely available and 
+  is now the part of the more general CorrelationFunctions.jl package.
 \end{abstract}
@@
     further squeezed into parameters for a number of basis functions
-    \cite{jiao_basis,KarsaninaEJSS},
+    \cite{jiao2007,KarsaninaEJSS},
   \item describing structural dynamics and evolution
@@
   \item evaluation of image replica quality, e.g., stochastic reconstructions
-    \cite{deeep_papers_or_somethingelse},
-  \item assessing stationarity of the structure at hand \cite{REVpaper}.
+    \cite{capek2009},
+  \item assessing stationarity of the structure at hand \cite{REVpaper,EfimEPL}.
 \end{enumerate}
@@
 $F_{ss}$ and $F_{sv}$ - were underrepresented due to our inability to compute
-them in a robust way. While known for a long time \cite{theory_in_MT}, only
-somewhat crude approximate approaches \cite{crude_approx_inMT} were developed
+them in a robust way. While known for a long time \cite{dietrich1995scattering}, only
+somewhat crude approximate approaches \cite{seaton1986spatial} were developed
 until Ma and Torquato laid foundation for such a robust computational
 methodology \cite{ma2018SS}. They proposed an elegant solution for infinite
-resolution Gaussian random fields, or "continouos" approach. They also assumed
+resolution Gaussian random fields, or "continuous" approach. They also assumed
 that the same approach can be readily applied to discrete experimental images if
-grey-scale values are thresholded in a similar way to continuious Gaussian
-field. Samarin et al. \cite{our_SS_paper} argued that experimental images needs
+grey-scale values are thresholded similarly to continuous Gaussian
+field. Samarin et al. \cite{Samarin} argued that experimental images needs
 to be segmented first using current cutting edge techniques \cite{NNseg} and
-proposed "discrete" approach. The latter allowed to obtain surface functions
-closer to analytical solutions for overlapping disks/spheres and to supress
+proposed "discrete" approach. The latter allowed obtaining surface functions
+closer to analytical solutions for overlapping disks/spheres and to suppress
 noise, in particular for $F_{ss}$. The noise in Ma and Torquato method resulted
@@
 leaves a room for improvements. While Samarin et al. obtained better convergence
-with analytical solution, this was demostrated only for overlapping disks image
+with analytical solution, this was demonstrated only for overlapping disks image
 of limited size (that can potentially introduce some differences between
@@
   \item describing real surfaces resulting from different mechanical processes,
-    e.g., cracking \cite{some_examples},
+    e.g., cracking \cite{hansen1991roughness,akhavan2012quantifying},
   \item delineating surface evolution \cite{chen2022} during such mechanical
@@
 In this contribution we continue to build upon foundational work of Ma and
-Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{our_SS} to
+Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{Samarin} to
 develop a robust and efficient approach to compute surface correlation functions
-from digital 2D and 3D images. In partiuclar, here our aim is to establish a
+from digital 2D and 3D images. In particular, here our aim is to establish a
 direct verification of "discrete" methodology (that is easily parallelizable on
@@
 $\bm{r_1} = (r_{1x}, r_{1y}, r_{1z})$ and $\bm{r_2} = (r_{2x}, r_{2y}, r_{2z})$.
-However if the medium under consideration is isotropic, only three scalar
+However, if the medium under consideration is isotropic, only three scalar
 arguments $r_1 = |\bm{r_1}|$, $r_2 = |\bm{r_2}|$ and $r_3 = |\bm{r_1} - \bm{r_2}|$
@@
   \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
-  \caption[]{Left, center: images $Q_1$ and $Q_2$ used in the demostration of
+  \caption[]{Left, center: images $Q_1$ and $Q_2$ used in the demonstration of
     approximation for $1 / \sin \phi$. Right: Interfaces between phases are
@@
 
-\subsection{Units for computed surface correlation funtions}
+\subsection{Units for computed surface correlation functions}
 From now on we introduce a conventional unit of measurement ($cu$) for length.
@@
 of a function at point $x = a$ and its derivative at that point:
-$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also we can compute a partial
+$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also, we can compute a partial
 derivative of a multivariate function. For example:
@@
 \end{equation}
-Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
+Here $\rho(\bm{x}, \Gamma)$ means the closest distance from point $\bm{x}$ to the
 boundary $\Gamma$.
@@
 \begin{enumerate}
-\item Find $X$ which is a set of soulutions of \cref{eq:inter}.
+\item Find $X$ which is a set of solutions of \cref{eq:inter}.
 \item For all points in $X$ find normals to the boundaries using
@@
 $H$ (\ref{eq:filter-3x3}) for edge detection along with a new filter $H'$
-(\ref{eq:filter-7x7}) proposed in this paper. We verify both digital and
-continuous methods against available analytical solutions.
+(\ref{eq:filter-7x7}) proposed in this paper. Both digital and
+continuous methods are verified against available analytical solutions.
 
@@
 where $\bm{x} \in \mathbb{R}^2$ is a square with side $2T$. The function $f$ is
-differentiable at all points where $f(\bm{x}) = T$ with exception of points
+differentiable at all points where $f(\bm{x}) = T$ with exception to points
 $(-T, -T)$, $(-T, T)$, $(T, -T)$ and $(T, T)$. The surface-surface correlation
@@
 \cref{fig:fss-square} and, thus, not shown here. We conclude that all approaches
-perform equaly accurately for this simple test.
+perform equally accurately for this simple test.
 
@@
     $\bm{r_2}$ is parallel to a vector $\bm{j} = (0, 1, 0)$. Vectors $\bm{i}$
-    and $\bm{j}$ constitute a two dimensional parameter space for $F_{sss}$. On
+    and $\bm{j}$ constitute a two-dimensional parameter space for $F_{sss}$. On
     the right: Relative error of computation. True values for $F_{sss}$ are
@@
 
-We conclude that continuous approach has zero error against analitical solution
+We conclude that continuous approach has zero error against analytical solution
 around can be used to assess the quality of digital approach for discretized
@@
 three-dimensional images. This can be seen in comparison with theoretical values
-for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
+for known cases, e.g., a ball. On \cref{fig:fss-ball} plots
 of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
-theoretical curve. It can be verified that filter $H'$ is better indeed by
-calculating
+theoretical curve are presented. It can be verified that filter $H'$ is indeed results 
+in higher accuracies with the help of error metric:
 \begin{equation}
@@
 where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
-$\epsilon = 0.01$ we get $error = 0.05$ for filter $H$ and $error = 0.03$ for
-filter $H'$. Calculation of surface-void function also benefits from the new
+$\epsilon = 0.01$ we obtain the +$error = 0.05$ for filter $H$ and $error = 0.03$ for
+filter $H'$, respectively. Calculation of surface-void function also benefits from the new
 filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
 
-Unfortunately the filter $H'$ has some drawbacks in comparison with
-$H$. Firstly, $H$ has faster convergence with increase of image resolution. To
-demonstrate this we can use an acceptance parameter $C_{0.5}$ developed to
-determine if an image is suitable for processing with our algorithm or not. This
-parameter is defined as
+However, the $H'$ filter has some drawbacks as compared to
+$H$. Firstly, $H$ has faster convergence with increase of image resolution. 
+Secondly, $H'$ behaves worse that $H$ in points
+of discontinuity of $F_{ss}$ for low resolutions as can be seen on \cref{fig:fss-disk}.
+To explore such effects we appeal to the criterion $C_{0.5}$ \cite{Samarin} developed to
+determine if an image is suitable for robust surface correlation functions assessment. This
+parameter is defined as:
 \begin{equation*}
@@
 \end{equation*}
-In this expression the words ``Power of the image'' are understood as $L^2$ norm
+In this expression the part of ``Power of the image'' refers to $L^2$ norm
 of the image and ``the lower half of the \dots spectrum'' is the part of the
 spectrum (Fourier image) with frequencies $[-\omega_N/2, \omega_N/2]$ where
-$\omega_N$ is a Nyquist frequency for the image. It's important to firstly
-subtract the zeroth frequency (mean value) from the image before calculation of
-$C_{0.5}$. The image is suitable for processing if the acceptance criterion
+$\omega_N$ is a Nyquist frequency of the image. It's important to firstly
+subtract the zeroth frequency (mean value) from the image before the calculation of
+$C_{0.5}$ is executed. The image is suitable for processing if the acceptance criterion
 $C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and $H'$, but
@@
 \cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for
-those images and relative errors in $F_{ss}$ (\cref{eq:error}) for both
-filters. It can be seen that $H$ gives twice the lower error than $H'$ when used
+this image (for variety of resolutions) and relative errors in $F_{ss}$ (\cref{eq:error}) 
+for both filters. It can be seen that $H$ gives twice the lower error than $H'$ when used
 for an image with $C_{0.5} \approx 0.82$.
 
-Secondly, $H'$ behaves worse that $H$ in points
-of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
+In short, for images of acceptable quality the $H'$ filter is superior. Images with insufficient
+resolution benefit from downscaling prior to correlation functions evalution \cite{Samarin} (and 
+then again new filter will provide better results).
 
@@
 \label{sec:summary}
-The exact continuos method presented in this paper is developed only for
+The exact continuous method presented in this paper is developed only for
 surface-surface function (and its 3-point counterpart). The surface-void
@@
     \item Possibility to evaluate surface functions from small-angle scattering
-      experiments \cite{theor_paper};
+      experiments \cite{dietrich1995scattering};
     \item Finding overall trends in porous media structural evolution, e.g.,
-      based on experimental datasets \cite{Jose,Fomin,nano_structure};
-    \item Description of interfaces during multi-phase flow beyond conventional
-      metrics (e.g., surface area or Minkowski functionals which are all subset
-      of classical correlation functions) \cite{Hassanizadeh,Armstrong}.
+      based on experimental datasets \cite{noiriel2021pore,fomin2023};
+    \item Qualitative exploration of molecular scale roughness effects on electric 
+      double layer structure in asymmetric ionic liquids \cite{aslyamov2021,khlyupin2023}.
 \end{enumerate}
-This list immediately pops up from the authors' research activities and
-potentially is much wider.
+This list immediately pops up from the authors' research activities and is,
+potentially, much wider.
 
@@
 testing techniques for digital computational methodology, including concave
-surface shapes.  In particular, we were able to demostrate the inmprovement in
-calculations of surface-surface and surface-viod correlation functions for
+surface shapes.  In particular, we were able to demonstrate the improvement in
+calculations of surface-surface and surface-void correlation functions for
 digital binary images with the help of proposed $H'$ filter.

### 2023-05-12 paper.tex
Change document class

@@
-\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}
+\documentclass[preprint]{elsarticle}
+
+%\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}
+
 \usepackage[english]{babel}
@@
 \usepackage[T1]{fontenc}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{bm}
@@
 \usepackage{hyperref}
-\usepackage{cleveref}
 \usepackage[inline]{enumitem}
 \usepackage{resizegather}
+\usepackage{cleveref}
 
@@
 
+\bibliographystyle{elsarticle-num}
+
 \begin{document}
-\preprint{APS/123-QED}
-
-\author{Vasily Postnicov\textsuperscript{1}}
-\author{Marina V. Karsanina\textsuperscript{1}}
-\author{Aleksey Khlyupin\textsuperscript{1,2}}
-\author{Kirill M. Gerke\textsuperscript{1}}
-\email{kg@ifz.ru}
-
-\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
-  Russian Academy of Sciences, Moscow, 107031, Russia}
-\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
+
+\author[Smith]{Vasily~Postnicov}
+\author[Smith]{Marina~V.~Karsanina}
+\author[Smith,MIT]{Aleksey~Khlyupin}
+\author[Smith]{Kirill~M.~Gerke\corref{maincorr}}
+\cortext[maincorr]{Corresponding author}
+\ead{kg@ifz.ru}
+
+\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 107031, Russia}
+\address[MIT]{Moscow Institute of Physics and Technology,
   Dolgoprudny, 141701, Russia}
@@
 \begin{abstract}
-  Surface correlation functions are extremely useful descriptors of interfaces and in this role 
-  can be used in material science, rock and soil physics, food engineering and other numerous
-  areas. However, their widespread usage was hampered by insufficiently robust computation methodologies. 
-  In this contribution we elaborate on recent works in surface function evaluation and present a 
-  novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions for smooth boundary sets without 
-  discretization. This allows us to test digital computational approach on geometries beyond those with 
-  analytical solutions. Moreover, we propose a better edge detection filter that allowed to improve the 
-  quality of surface correlation functions (both surface-surface and surface-void) assessment based on 
-  digital images. The code for continuous and discrete computational frameworks is freely available and 
-  is now the part of the more general CorrelationFunctions.jl package.
+  Surface correlation functions are extremely useful descriptors of interfaces
+  and in this role can be used in material science, rock and soil physics, food
+  engineering and other numerous areas. However, their widespread usage was
+  hampered by insufficiently robust computation methodologies.  In this
+  contribution we elaborate on recent works in surface function evaluation and
+  present a novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions
+  for smooth boundary sets without discretization. This allows us to test
+  digital computational approach on geometries beyond those with analytical
+  solutions. Moreover, we propose a better edge detection filter that allowed to
+  improve the quality of surface correlation functions (both surface-surface and
+  surface-void) assessment based on digital images. The code for continuous and
+  discrete computational frameworks is freely available and is now the part of
+  the more general CorrelationFunctions.jl package.
 \end{abstract}
-\keywords {3D images; correlation functions; surface-surface function;
-  surface-void function; image analysis; image scaling}
+
+\begin{keyword}
+  3D images, correlation functions, surface-surface function,
+  surface-void function, image analysis, image scaling
+\end{keyword}
 

### 2023-05-17 paper.tex
final (hopefully) text changes from kg
Explain what F_{sv} means in the abstract

@@
 \bibliographystyle{elsarticle-num}
+\journal{Physica A: Statistical Mechanics and its Applications}
 
@@
   contribution we elaborate on recent works in surface function evaluation and
-  present a novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions
-  for smooth boundary sets without discretization. This allows us to test
-  digital computational approach on geometries beyond those with analytical
-  solutions. Moreover, we propose a better edge detection filter that allowed to
-  improve the quality of surface correlation functions (both surface-surface and
-  surface-void) assessment based on digital images. The code for continuous and
+  present a novel exact algorithm to compute surface-surface ($F_{ss}$) and
+  surface-surface-surface ($F_{sss}$) functions for smooth boundary sets without
+  discretization. This allows us to test digital computational approach on
+  geometries beyond those available as analytical solutions. Moreover, we
+  propose a better edge detection filter that allowed to improve the quality of
+  assessment of surface correlation functions, both surface-surface and
+  surface-void ($F_{sv}$), for digital images. The code for continuous and
   discrete computational frameworks is freely available and is now the part of
@@
 \begin{keyword}
-  3D images, correlation functions, surface-surface function,
-  surface-void function, image analysis, image scaling
+  3D images, correlation functions, surface-surface function, surface-void
+  function, image analysis, image scaling
 \end{keyword}

### 2023-05-17 paper.tex
Replace noise -> perturbation

@@
 closer to analytical solutions for overlapping disks/spheres and to suppress
-noise, in particular for $F_{ss}$. The noise in Ma and Torquato method resulted
-from $1/cos(\theta)$ computations during random line segment placement - this
-leaves a room for improvements. While Samarin et al. obtained better convergence
-with analytical solution, this was demonstrated only for overlapping disks image
-of limited size (that can potentially introduce some differences between
-computations and analytical solution for infinite size structure). Moreover,
-good agreement was achieved by manually fitting the values of edge-detecting
-filter that could lack accuracy for arbitrary structure different from
-overlapping disks. In other words, we still lack robustness in surface CFs
-evaluation due to inability to directly compare "discrete" versus "continuous"
-methodology, and verify both approaches for arbitrary geometries.
+perturbation, in particular for $F_{ss}$. The perturbation in Ma and Torquato
+method resulted from $1/cos(\theta)$ computations during random line segment
+placement -- this leaves a room for improvements. While Samarin et al. obtained
+better convergence with analytical solution, this was demonstrated only for
+overlapping disks image of limited size (that can potentially introduce some
+differences between computations and analytical solution for infinite size
+structure). Moreover, good agreement was achieved by manually fitting the values
+of edge-detecting filter that could lack accuracy for arbitrary structure
+different from overlapping disks. In other words, we still lack robustness in
+surface CFs evaluation due to inability to directly compare "discrete" versus
+"continuous" methodology, and verify both approaches for arbitrary geometries.
 
@@
 direct verification of "discrete" methodology (that is easily parallelizable on
-CPU and GPU architectures) using exact noiseless "continuous" approach for
-arbitrary structures (still described by some continuous function). The rest of
-the manuscript is organized as follows: in \cref{sec:def} we introduce some
-major definitions of CFs necessary for establishing algorithms, in
-\cref{sec:algo} we describe the all methodological details for "discrete" method
-for digital images. Next, in \cref{sec:algo-precise} we explain in detail why
-verification of computational approaches for digital images is currently
-hampered, and then introduce novel exact "continuous" methodology in
-\cref{sec:fss-2d}. The choice of verification cases is presented in
-\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
-paper concludes with discussion, outline and summary in \cref{sec:summary}.
+CPU and GPU architectures) using exact "continuous" approach for arbitrary
+structures (still described by some continuous function). The rest of the
+manuscript is organized as follows: in \cref{sec:def} we introduce some major
+definitions of CFs necessary for establishing algorithms, in \cref{sec:algo} we
+describe the all methodological details for "discrete" method for digital
+images. Next, in \cref{sec:algo-precise} we explain in detail why verification
+of computational approaches for digital images is currently hampered, and then
+introduce novel exact "continuous" methodology in \cref{sec:fss-2d}. The choice
+of verification cases is presented in \cref{sec:results} followed by
+improvements in methodology of Samarin et~al. The paper concludes with
+discussion, outline and summary in \cref{sec:summary}.
 
@@
 surface-surface function (and its 3-point counterpart). The surface-void
-function computations in digital manner are much more robust and exhibit no
-noise \cite{ma2018SS,Samarin}. The filter $H'$ verified for $F_{ss}$ also
+function computations in digital manner are much more robust and exhibit less
+perturbation \cite{ma2018SS,Samarin}. The filter $H'$ verified for $F_{ss}$ also
 improves calculations for $F_{sv}$ (as evident from \cref{fig:not-covered}).

### 2023-05-17 paper.tex
Start a new paragraph

@@
 CPU and GPU architectures) using exact "continuous" approach for arbitrary
-structures (still described by some continuous function). The rest of the
-manuscript is organized as follows: in \cref{sec:def} we introduce some major
-definitions of CFs necessary for establishing algorithms, in \cref{sec:algo} we
-describe the all methodological details for "discrete" method for digital
-images. Next, in \cref{sec:algo-precise} we explain in detail why verification
-of computational approaches for digital images is currently hampered, and then
-introduce novel exact "continuous" methodology in \cref{sec:fss-2d}. The choice
-of verification cases is presented in \cref{sec:results} followed by
-improvements in methodology of Samarin et~al. The paper concludes with
-discussion, outline and summary in \cref{sec:summary}.
+structures (still described by some continuous function).
+
+The rest of the manuscript is organized as follows: in \cref{sec:def} we
+introduce some major definitions of CFs necessary for establishing algorithms,
+in \cref{sec:algo} we describe the all methodological details for "discrete"
+method for digital images. Next, in \cref{sec:algo-precise} we explain in detail
+why verification of computational approaches for digital images is currently
+hampered, and then introduce novel exact "continuous" methodology in
+\cref{sec:fss-2d}. The choice of verification cases is presented in
+\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
+paper concludes with discussion, outline and summary in \cref{sec:summary}.
 

### 2023-05-17 paper.tex
Add a citation
All equations are numbered

@@
 defined as follows:
-\begin{equation*}
+\begin{equation}
   \chi_A(\bm{x}) = \left\{
@@
   \right.
-\end{equation*}
+\end{equation}
 
@@
 $F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as
-follows:
+follows: \cite{Torquato_book}
 \begin{align}
@@
 $F_{sv}$ can be replaced with a scalar $r = |\bm{r}|$:
-\begin{align*}
+\begin{align}
   F_{ss}(r) &= F_{ss}(\bm{r}) \\
   F_{sv}(r) &= F_{sv}(\bm{r})
-\end{align*}
+\end{align}
 In case correlation functions are computed in predefined directions, scalar
@@
 vectors $\bm{r_1}$ and $\bm{r_2}$:
-\begin{equation*}
+\begin{equation}
   F_{sss}(r_1, r_2, r_3) = F_{sss}(r_1, r_2, \theta) = F_{sss}(\bm{r_1}, \bm{r_2})
-\end{equation*}
+\end{equation}
 
@@
 is performed as follows:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     A'_{lm}  &= \left| \sum_i\sum_j A_{l-i, m-j}H_{ij} \right| \quad \text{for 2D} \\
-  A'_{lmn} &= \left| \sum_i\sum_j\sum_k A_{l-i, m-j, n-k}H_{ijk} \right| \quad
-  \text{for 3D}
-\end{align*}
+    A'_{lmn} &= \left| \sum_i\sum_j\sum_k A_{l-i, m-j, n-k}H_{ijk} \right| \quad \text{for 3D}
+  \end{aligned}
+\end{equation}
 Therefore $A'$ has non-zero elements only in a small area around interface
@@
 image $A$ and can be performed using Fourier transform:
-\begin{equation*}
+\begin{equation}
   A' = |H*A| = |F^{-1}[F[H] F[A]]|
-\end{equation*}
+\end{equation}
 Here $F$ is a forward Fourier transform and $F^{-1}$ is its inverse.
@@
 total number of elements in $A$:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     F_{{ss}_{lm}} &= \frac{1}{N} \sum_i \sum_j A'_{ij}A'_{i+l, j+m} \quad
     \text{for 2D} \\
-  F_{{ss}_{lmn}} &= \frac{1}{N} \sum_i \sum_j \sum_k A'_{ijk}A'_{i+l, j+m, k+n}
-  \quad \text{for 3D}
-\end{align*}
+    F_{{ss}_{lmn}} &= \frac{1}{N} \sum_i \sum_j \sum_k A'_{ijk}A'_{i+l, j+m,
+      k+n} \quad \text{for 3D}
+  \end{aligned}
+\end{equation}
 Calculation of sums in the latter equations can be performed using the following
 properties of Fourier transform (here $\hat{f}(z) = F[f(x)]$):
-\begin{equation*}
+\begin{equation}
   F[f(x) \star f(x)] = F[f(x) * f(-x)] = \hat{f}(z)\overline{\hat{f}(z)} = |\hat{f}(z)|^2
-\end{equation*}
+\end{equation}
 
@@
 multiplication works according to the following law:
-\begin{equation*}
+\begin{equation}
   (a, b)\cdot(c, d) = (ac, ad + bc)
-\end{equation*}
+\end{equation}
 It's easy to see that $D$ is commutative.
@@
 integral domain and division is defined only if divisor has non-zero real part:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     \frac{a+b\varepsilon}{c+d\varepsilon} &=
@@
     &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
-\end{align*}
+  \end{aligned}
+\end{equation}
 
@@
 formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
-\begin{equation*}
+\begin{equation}
   (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
   x^n + n x^{n-1} y \varepsilon
-\end{equation*}
+\end{equation}
 This formula can be extended to $n \in \mathbb{Q}$ as well.
@@
 $a$ is some point at which $f$ is differentiable):
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
@@
     &= f(x) + yf'(x)\varepsilon
-\end{align*}
+  \end{aligned}
+\end{equation}
 
@@
 Now define a functional sequence $F_{ss}(\bm{r}; \Delta)$:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
@@
     &= \sum_{k=1}^N S_k/\Delta^2
-\end{align*}
+  \end{aligned}
+\end{equation}
 Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
@@
 $(1,0), (0,1)$:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     x' &= f(x, y) = a_x x + a_y y \\
     y' &= g(x, y) = b_x x + b_y y
-\end{align*}
+  \end{aligned}
+\end{equation}
 where $\bm{a} = (a_x, a_y)$, $\bm{b} = (b_x, b_y)$. Jacobian determinant for
 this transformation is:
-\begin{equation*}
+\begin{equation}
   J = \left|
@@
   \right| = a_x b_y - a_y b_x
-\end{equation*}
+\end{equation}
 
@@
 its translated version by solving a system of equations:
-\begin{equation*}
+\begin{equation}
   \left\{
@@
   \right.
-\end{equation*}
+\end{equation}
 which can now be replaced by a single equation:
@@
 $F_{sss}(\bm{r_1}, \bm{r_2}; \Delta)$:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     F_{sss}(\bm{r_1}, \bm{r_2}; \Delta) &= \int\int\int dx dy dz \times \\
@@
     &= \sum_{k=1}^N V_k/\Delta^3
-\end{align*}
+  \end{aligned}
+\end{equation}
 where $V_k$ is a volume of parallelepiped where all three multiplicands under
@@
 to $F_{sss}$:
-\begin{equation*}
+\begin{equation}
   \lim_{\Delta \to 0} F_{sss}(\bm{r_1}, \bm{r_2}; \Delta) = F_{sss}(\bm{r_1},
   \bm{r_2})
-\end{equation*}
+\end{equation}
 
@@
 transformation from the basis $(1,0,0), (0,1,0), (0, 0, 1)$:
-\begin{align*}
+\begin{equation}
+  \begin{aligned}
     x' &= f(x, y) = a_x x + a_y y + a_z z \\
     y' &= g(x, y) = b_x x + b_y y + b_z z \\
-  z' &= h(x, y) = c_x x + c_y y + c_z z \\
-\end{align*}
+    z' &= h(x, y) = c_x x + c_y y + c_z z
+  \end{aligned}
+\end{equation}
 The Jacobian determinant for this transformation is:
-\begin{equation*}
+\begin{equation}
   J = \left|
@@
     b_x & b_y & b_z \\
-    c_x & c_y & c_z \\
+    c_x & c_y & c_z
   \end{array}
   \right|
-\end{equation*}
+\end{equation}
 and the expression for $F_{sss}$ becomes:
@@
 function for a square is equal to:
-\begin{equation*}
+\begin{equation}
   F_{ss}(\bm{r}) = \left\{
@@
   \right.
-\end{equation*}
+\end{equation}
 A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
@@
 The surface-surface-surface correlation function for this cube is equal to:
-\begin{equation*}
+\begin{equation}
   F_{sss}(\bm{r}) = \left\{
@@
   \right.
-\end{equation*}
+\end{equation}
 This case is also handled perfectly by the algorithm described in
@@
 the origin. In this case $F_{ss}$ depends only on distance $r$ from the origin:
-\begin{equation*}
+\begin{equation}
   F_{ss}(r) = \left\{
@@
   \right.
-\end{equation*}
+\end{equation}
 The comparison of the algorithm described in \cref{sec:algo} applied to images
@@
 random values of each of $a_i$, $b_i$ and $\sigma_i$. Let $f$ be:
-\begin{equation*}
+\begin{equation}
   f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
-\end{equation*}
+\end{equation}
 Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
@@
 Take $N$ random values $a_i$, $b_i$, $c_i$, $x^c_i$ and $y^c_i$ and define
-\begin{equation*}
+\begin{equation}
   f_i(x, y) = a_i(x-x^c_i)^2 + b(x-x^c_i)(y-y^c_i) + c_i(y-y^c_i)^2
-\end{equation*}
+\end{equation}
 with $a_ic_i - b_i^2 > 0$. Inequation
-\begin{equation*}
+\begin{equation}
   \min_i f_i(x, y) < A^2
-\end{equation*}
+\end{equation}
 defines $N$ ellipses like those which can be seen on \cref{fig:ellipses}. A
@@
 parameter is defined as:
-\begin{equation*}
+\begin{equation}
   C_{0.5} = \frac{\text{Power of the lower half of the image's
       spectrum}}{\text{Power of the image}}
-\end{equation*}
+\end{equation}
 In this expression the part of ``Power of the image'' refers to $L^2$ norm

### 2023-05-17 paper.tex
Introduce the function M
Dual numbers are banished to the appendix!

@@
 \end{equation}
+An absolute value of its gradient (in the sense of distributions) is denoted
+as $M$:
+\begin{equation}
+  M_A(\bm{x}) = |\nabla \chi_A(\bm{x})|
+\end{equation}
 
@@
 \begin{align}
-  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
-  \bm{r})| \rangle \label{eq:fss} \\
-  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
-  \bm{r}) \rangle \label{eq:fsv}
+  F_{ss}(\bm{r}) &= \langle M_S(\bm{x}) M_S(\bm{x} + \bm{r}) \rangle \label{eq:fss} \\
+  F_{sv}(\bm{r}) &= \langle M_S(\bm{x}) \chi_V(\bm{x} + \bm{r}) \rangle
+  \label{eq:fsv}
 \end{align}
@@
 \begin{equation}
-  F_{sss}(\bm{r_1}, \bm{r_2}) = \langle |\nabla \chi_S(\bm{x})|
-  |\nabla \chi_S(\bm{x} + \bm{r_1})|
-  |\nabla \chi_S(\bm{x} + \bm{r_2})|
-  \rangle \label{eq:fsss}
+  F_{sss}(\bm{r_1}, \bm{r_2}) = \langle M_S(\bm{x}) M_S(\bm{x} + \bm{r_1})
+  M_S(\bm{x} + \bm{r_2}) \rangle
+  \label{eq:fsss}
 \end{equation}
@@
 
-\subsection{Dual numbers and automatic differentiation}
-\label{sec:dual}
-A ring of dual numbers $D$ is a set of pairs of real numbers $(a, b)$ with two
-binary operations: $+$ (addition) and $\cdot$ (multiplication) where
-multiplication works according to the following law:
-\begin{equation}
-  (a, b)\cdot(c, d) = (ac, ad + bc)
-\end{equation}
-It's easy to see that $D$ is commutative.
-
-It is also useful to introduce an imaginary unit $\varepsilon$ and write a dual
-number $(a, b)$ as $a + b\varepsilon$. As follows from the multiplication law,
-$1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
-integral domain and division is defined only if divisor has non-zero real part:
-\begin{equation}
-  \begin{aligned}
-    \frac{a+b\varepsilon}{c+d\varepsilon} &=
-    \frac{(a+b\varepsilon)(c-d\varepsilon)}{(c+d\varepsilon)(c-d\varepsilon)} \\
-    &= \frac{ac-ad\varepsilon+bc\varepsilon}{c^2} \\
-    &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
-  \end{aligned}
-\end{equation}
-
-Now we consider functions of dual variable $x + y\varepsilon$. Power function
-$(x + y\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined using binomial
-formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
-\begin{equation}
-  (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
-  x^n + n x^{n-1} y \varepsilon
-\end{equation}
-This formula can be extended to $n \in \mathbb{Q}$ as well.
-
-Elementary functions can be extended to dual numbers using Taylor series (here
-$a$ is some point at which $f$ is differentiable):
-\begin{equation}
-  \begin{aligned}
-    f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
-    & \qquad + \frac{f'''(a)}{3!}(x + y\varepsilon)^3 + \dots \\
-    &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x^2 + 2xy\varepsilon) \\
-    & \qquad + \frac{f'''(a)}{3!}(x^3 + 3x^2y\varepsilon) + \dots \\
-    &= f(a) + f'(a)x + \frac{f''(a)}{2!}x^2 + \frac{f'''(a)}{3!}x^3 + \dots \\
-    & \quad y\varepsilon(f'(a) + f''(a)x + \frac{f'''(a)}{2!}x^2 + \dots) \\
-    &= f(x) + yf'(x)\varepsilon
-  \end{aligned}
-\end{equation}
-
-Most useful basic rules for working with dual numbers can be summarized as follows:
-\begin{itemize}
-\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
-\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
-\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
-\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
-\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
-\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
-\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
-\end{itemize}
-
-As is evident from these rules, dual numbers are connected with
-differentiation. Using a dual argument $a + \varepsilon$ we can compute a value
-of a function at point $x = a$ and its derivative at that point:
-$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also, we can compute a partial
-derivative of a multivariate function. For example:
-\begin{equation}
-  \begin{aligned}
-    \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
-    b) \\
-    \frac{\partial}{\partial y} f(x, y) \vert_{x = a, y = b} &= f(a, b +
-    \varepsilon)
-  \end{aligned}
-  \label{eq:autonormals}
-\end{equation}
-This last equation will be useful for computation of normals to the interface in
-next sections.
-
 \subsection{Surface-surface function for two-dimensional sets with smooth boundary}
@@
 
+\appendix
+\section{Dual numbers and automatic differentiation}
+\label{sec:dual}
+A ring of dual numbers $D$ is a set of pairs of real numbers $(a, b)$ with two
+binary operations: $+$ (addition) and $\cdot$ (multiplication) where
+multiplication works according to the following law:
+\begin{equation}
+  (a, b)\cdot(c, d) = (ac, ad + bc)
+\end{equation}
+It's easy to see that $D$ is commutative.
+
+It is also useful to introduce an imaginary unit $\varepsilon$ and write a dual
+number $(a, b)$ as $a + b\varepsilon$. As follows from the multiplication law,
+$1\cdot \varepsilon = \varepsilon$ and $\varepsilon^2 = 0$, hence $D$ is not an
+integral domain and division is defined only if divisor has non-zero real part:
+\begin{equation}
+  \begin{aligned}
+    \frac{a+b\varepsilon}{c+d\varepsilon} &=
+    \frac{(a+b\varepsilon)(c-d\varepsilon)}{(c+d\varepsilon)(c-d\varepsilon)} \\
+    &= \frac{ac-ad\varepsilon+bc\varepsilon}{c^2} \\
+    &= \frac{a}{c} + \frac{bc-ad}{c^2}\varepsilon
+  \end{aligned}
+\end{equation}
+
+Now we consider functions of dual variable $x + y\varepsilon$. Power function
+$(x + y\varepsilon)^n$ where $n \in \mathbb{N}$ can be defined using binomial
+formula and keeping in mind that $\varepsilon^n = 0$ if $n>1$:
+\begin{equation}
+  (x + y\varepsilon)^n = \sum_{k=0}^n \binom{n}{k} x^k (y\varepsilon)^{n-k} =
+  x^n + n x^{n-1} y \varepsilon
+\end{equation}
+This formula can be extended to $n \in \mathbb{Q}$ as well.
+
+Elementary functions can be extended to dual numbers using Taylor series (here
+$a$ is some point at which $f$ is differentiable):
+\begin{equation}
+  \begin{aligned}
+    f(x + y\varepsilon) &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x + y\varepsilon)^2 \\
+    & \qquad + \frac{f'''(a)}{3!}(x + y\varepsilon)^3 + \dots \\
+    &= f(a) + f'(a)(x + y\varepsilon) + \frac{f''(a)}{2!}(x^2 + 2xy\varepsilon) \\
+    & \qquad + \frac{f'''(a)}{3!}(x^3 + 3x^2y\varepsilon) + \dots \\
+    &= f(a) + f'(a)x + \frac{f''(a)}{2!}x^2 + \frac{f'''(a)}{3!}x^3 + \dots \\
+    & \quad y\varepsilon(f'(a) + f''(a)x + \frac{f'''(a)}{2!}x^2 + \dots) \\
+    &= f(x) + yf'(x)\varepsilon
+  \end{aligned}
+\end{equation}
+
+Most useful basic rules for working with dual numbers can be summarized as follows:
+\begin{itemize}
+\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
+\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
+\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
+\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
+\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
+\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
+\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
+\end{itemize}
+
+As is evident from these rules, dual numbers are connected with
+differentiation. Using a dual argument $a + \varepsilon$ we can compute a value
+of a function at point $x = a$ and its derivative at that point:
+$f(a + \varepsilon) = f(a) + f'(a)\varepsilon$. Also, we can compute a partial
+derivative of a multivariate function. For example:
+\begin{equation}
+  \begin{aligned}
+    \frac{\partial}{\partial x} f(x, y) \vert_{x = a, y = b} &= f(a + \varepsilon,
+    b) \\
+    \frac{\partial}{\partial y} f(x, y) \vert_{x = a, y = b} &= f(a, b +
+    \varepsilon)
+  \end{aligned}
+  \label{eq:autonormals}
+\end{equation}
+This last equation is the main result of this appendix and can be used for
+computation of normals to the interface.
+
 \bibliography{paper}

### 2023-05-17 paper.tex
Try to explain more about 'zero error'

@@
 
-We conclude that continuous approach has zero error against analytical solution
-around can be used to assess the quality of digital approach for discretized
-sets. As expected, digital approach performance depends on the image resolution
-with new edge filter outperforming $H$.
+We conclude that if a theoretical solution is known for the correlation function
+$F_{ss}$ or $F_{sss}$, then evaluation of this function using our continuous
+approach does not differ from this theoretical solution if all crossings of
+the interface with its translated self are found correctly (which is the case
+for all sets described in this paper). This approach can be used to assess the
+quality of the algorithm for discretized sets. As expected, performance of the
+latter depends on the image resolution and the choise of an edge detection
+filter (the new filter $H'$ is preferable than $H$ for images with good
+resolution, see \cref{sec:influence}).
 
@@
 \subsection{Influence of filter $H'$ on computation accuracy}
-
+\label{sec:influence}
 \begin{figure*}

### 2023-05-17 paper.tex
Major -> basic

@@
 The rest of the manuscript is organized as follows: in \cref{sec:def} we
-introduce some major definitions of CFs necessary for establishing algorithms,
+introduce some basic definitions of CFs necessary for establishing algorithms,
 in \cref{sec:algo} we describe the all methodological details for "discrete"

### 2023-05-17 paper.tex
A few minor improvements

@@
 
-Another function studied in this paper is surface-surface-surface function
-$F_{sss}$. It is defined as follows:
+Another function studied in this paper is three-point surface-surface-surface
+correlation function $F_{sss}$. It is defined as follows:
 \begin{equation}
@@
 \begin{equation}
-  F_{sss}(r_1, r_2, r_3) = F_{sss}(r_1, r_2, \theta) = F_{sss}(\bm{r_1}, \bm{r_2})
+  F_{sss}(\bm{r_1}, \bm{r_2}) = F_{sss}(r_1, r_2, r_3) = F_{sss}(r_1, r_2, \theta)
 \end{equation}
@@
 \label{sec:algo}
-Here we briefly describe the algorithm for computation of surface-surface,
-surface-void and surface-surface-surface correlation functions for digital
-images of porous media \cite{Samarin}. This discrete algorithm can calculate
-surface correlation functions for all possible directions and correlation
-lengths. It consists of two steps: edge detection and computation of
-autocorrelation. Next, we present some improvements in this approach that later
-will be verified with the help of exact continuous method.
+Here we briefly describe the algorithm for computation of $F_{ss}$, $F_{sv}$ and
+$F_{sss}$ correlation functions for digital images of porous media
+\cite{Samarin}. This discrete algorithm calculates surface correlation functions
+for all possible directions and correlation lengths. It consists of two steps:
+edge detection and computation of autocorrelation. Next, we present some
+improvements in this approach that later will be verified with the help of exact
+continuous method.
 
@@
 ``rotates'' content of the array, if periodic boundary conditions are
-desired. For our purpose we use $F_{sss}$ function in the form
+desired. For our purpose we represent $F_{sss}$ function in the form
 $F_{sss}(r_1, r_2, \theta)$ and fix $\theta = \pi/2$. This leads us to a
@@
 $1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
-better than $H$. Why this is important will be explained in the next section.
+better than $H$. Why this is important will be explained in \cref{sec:fss-2d}.
 \begin{figure}

### 2023-05-17 paper.tex
More minor improvements

@@
 \subsection{Discrete method details}
-We consider an image of porous medium in the form of two- or three-dimensional bit
-array $A$ as the input to our algorithm. In the first stage, we convolve the
-input with high-pass filter to extract edges from the image. In our previous
-paper \cite{Samarin} we used the following filter kernel $H$:
+We consider a binary image (i.~e. an image which uses only two colors) in the
+form of two- or three-dimensional bit array $A$ as the input to our
+algorithm. In the first stage, we convolve the input with high-pass filter to
+extract edges from the image. In our previous paper \cite{Samarin} we used the
+following filter kernel $H$:
 \begin{equation}
@@
 
-\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
+\subsection{$F_{ss}$ function for two-dimensional sets with smooth boundary}
 \label{sec:fss-2d}
@@
 $\bm{r}$. These normals can be found using automatic differentiation and dual
-numbers described in \cref{sec:dual}. Then we normalize these normals (i.e. make
-their length equal to $1$) and use \cref{eq:fss-2d} to calculate $F_{ss}$.
+numbers described in \ref{sec:dual}. Then we normalize these vectors and use
+\cref{eq:fss-2d} to calculate $F_{ss}$.
 
@@
 
-\subsection{Surface-surface-surface function for three-dimensional sets with
-  smooth boundary}
+\subsection{$F_{sss}$ function for three-dimensional sets with smooth boundary}
 \label{sec:fsss-3d}
@@
 \cref{sec:fsss-3d}. There is no known analytical solution for 3D ball (one could
-derive a solution in analogy with 2D case \cite{Torquato_book}, but this is a
-non-trivial task well beyond the scope of the current work).
+derive a solution in analogy with 2D case \cite{Torquato_book}, but this is
+beyond the scope of the current work).
 \begin{figure*}[!hpt]
@@
 where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
-$\epsilon = 0.01$ we obtain the +$error = 0.05$ for filter $H$ and $error = 0.03$ for
-filter $H'$, respectively. Calculation of surface-void function also benefits from the new
-filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
-
-However, the $H'$ filter has some drawbacks as compared to
-$H$. Firstly, $H$ has faster convergence with increase of image resolution. 
-Secondly, $H'$ behaves worse that $H$ in points
-of discontinuity of $F_{ss}$ for low resolutions as can be seen on \cref{fig:fss-disk}.
-To explore such effects we appeal to the criterion $C_{0.5}$ \cite{Samarin} developed to
-determine if an image is suitable for robust surface correlation functions assessment. This
-parameter is defined as:
+$\epsilon = 0.01$ we obtain the error equal to 0.05 for filter $H$ and 0.03 for
+filter $H'$, respectively. Calculation of surface-void function also benefits
+from the new filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
+
+However, the $H'$ filter has some drawbacks as compared to $H$. Firstly, $H$ has
+faster convergence with increase of image resolution.  Secondly, $H'$ behaves
+worse that $H$ in points of discontinuity of $F_{ss}$ for low resolutions as can
+be seen on \cref{fig:fss-disk}.  To explore such effects we appeal to the
+criterion $C_{0.5}$ \cite{Samarin} developed to determine if an image is
+suitable for robust surface correlation functions assessment. This parameter is
+defined as:
 \begin{equation}
@@
 \end{equation}
-In this expression the part of ``Power of the image'' refers to $L^2$ norm
-of the image and ``the lower half of the \dots spectrum'' is the part of the
+In this expression the part of ``Power of the image'' refers to $L^2$ norm of
+the image and ``the lower half of the \dots spectrum'' is the part of the
 spectrum (Fourier image) with frequencies $[-\omega_N/2, \omega_N/2]$ where
 $\omega_N$ is a Nyquist frequency of the image. It's important to firstly
-subtract the zeroth frequency (mean value) from the image before the calculation of
-$C_{0.5}$ is executed. The image is suitable for processing if the acceptance criterion
-$C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and $H'$, but
-$H$ results in smaller error when $C_{0.5}$ is slightly less than 0.97. For
-example, consider images of a disk used for calculation of $F_{ss}$ on
-\cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for
-this image (for variety of resolutions) and relative errors in $F_{ss}$ (\cref{eq:error}) 
-for both filters. It can be seen that $H$ gives twice the lower error than $H'$ when used
-for an image with $C_{0.5} \approx 0.82$.
-
-In short, for images of acceptable quality the $H'$ filter is superior. Images with insufficient
-resolution benefit from downscaling prior to correlation functions evalution \cite{Samarin} (and 
-then again new filter will provide better results).
+subtract the zeroth frequency (mean value) from the image before the calculation
+of $C_{0.5}$ is executed. The image is suitable for processing if the acceptance
+criterion $C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and
+$H'$, but $H$ results in smaller error when $C_{0.5}$ is slightly less than
+0.97. For example, consider images of a disk used for calculation of $F_{ss}$ on
+\cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for this
+image (for variety of resolutions) and relative errors in $F_{ss}$
+(\cref{eq:error}) for both filters. It can be seen that $H$ gives twice the
+lower error than $H'$ when used for an image with $C_{0.5} \approx 0.82$.
+
+In short, for images of acceptable quality the $H'$ filter is superior. Images
+with insufficient resolution benefit from downscaling prior to correlation
+functions evalution \cite{Samarin} (and then again new filter will provide
+better results).
 
@@
 An implementation of the precise continuous algorithm in Common Lisp for sets
-with smooth boundary is available on GitHub\cite{diff-boundary-corrfn}. Improved
-digital approach for both $F_{ss}$ and $F_{sss}$ is now part of open source
-package CorrelationFunctions.jl written in Julia \cite{CFs.jl}.
+with smooth boundary is available on GitHub
+\cite{diff-boundary-corrfn}. Improved digital approach for both $F_{ss}$ and
+$F_{sss}$ is now part of open source package CorrelationFunctions.jl written in
+Julia \cite{CFs.jl}.
 

### 2023-05-18 paper.tex
Remove enumitem package

@@
 \usepackage{hyperref}
-\usepackage[inline]{enumitem}
 \usepackage{resizegather}
@@
 rationale behind this improvement is that:
-\begin{enumerate*}[label=\alph*)]
+\begin{itemize}
 \item a filter of width 3 may turn to be too narrow to give a good approximation
   for particular structures;
-\item filter $H$ is not invariant under rotations, i.e.
+\item The filter $H$ is not invariant under rotations, i.e.
   $H*R(A) \ne R(H*A)$, where $R$ is a rotation operator.
-\end{enumerate*}
+\end{itemize}
 Filter $H'$ has a length $7$ and all coefficients with exception to the central

### 2023-05-19 paper.tex
Add inset images (1/3)
Fix a typo
Change sizes of graphics
Swap bibliography and appendix
More academy-like stuff instead of just words

@@
-\documentclass[preprint]{elsarticle}
+\documentclass[1p]{elsarticle}
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/pattern.png}
+  \includegraphics[width=0.6\linewidth]{images/pattern.png}
   \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
+  \includegraphics[width=\linewidth]{images/experiment-setup.png}
   \caption[]{Left, center: images $Q_1$ and $Q_2$ used in the demonstration of
@@
     line segments which intersect each other at angle $\phi$. Shaded area is
-    where $|(H*Q_1\cdot(H*Q_2)|$ has non-zero values. Sum of all values in this
+    where $|(H*Q_1)\cdot(H*Q_2)|$ has non-zero values. Sum of all values in this
     area approximates $1 / \sin \phi$.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
+  \includegraphics[width=0.6\linewidth]{images/filter-comparison.png}
   \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/Fss.png}
+  \includegraphics[width=0.6\linewidth]{images/Fss.png}
   \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/fss-zoomed.png}
+  \includegraphics[width=0.6\linewidth]{images/fss-zoomed.png}
   \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
@@
 \label{sec:influence}
-\begin{figure*}
+\begin{figure*}[!hpt]
   \centering
@@
     $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
-    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
+    \includegraphics[width=0.45\linewidth]{images/ball-3d-ss.png}
     \label{fig:fss-ball}}
@@
     $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
-    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
+    \includegraphics[width=0.45\linewidth]{images/fsv-disk.png}
     \label{fig:fsv-disk}}
-  \hfill
+  \vskip\baselineskip
   \subfigure[Surface-void function calculated for a ball with radius
     $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
-    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
+    \includegraphics[width=0.45\linewidth]{images/fsv-ball.png}
     \label{fig:fsv-ball}}
@@
 faster convergence with increase of image resolution. Secondly, $H'$ behaves
-worse that $H$ in points of discontinuity of $F_{ss}$ for low resolutions as can
-be seen on \cref{fig:fss-disk}.  To explore such effects we appeal to the
-criterion $C_{0.5}$ \cite{Samarin} developed to determine if an image is
-suitable for robust surface correlation functions assessment. This parameter is
-defined as:
-\begin{equation}
-  C_{0.5} = \frac{\text{Power of the lower half of the image's
-      spectrum}}{\text{Power of the image}}
-\end{equation}
-In this expression the part of ``Power of the image'' refers to $L^2$ norm of
-the image and ``the lower half of the \dots spectrum'' is the part of the
-spectrum (Fourier image) with frequencies $[-\omega_N/2, \omega_N/2]$ where
-$\omega_N$ is a Nyquist frequency of the image. It's important to firstly
-subtract the zeroth frequency (mean value) from the image before the calculation
-of $C_{0.5}$ is executed. The image is suitable for processing if the acceptance
-criterion $C_{0.5} > 0.97$ holds. This criterion works for both filters $H$ and
-$H'$, but $H$ results in smaller error when $C_{0.5}$ is slightly less than
-0.97. For example, consider images of a disk used for calculation of $F_{ss}$ on
-\cref{fig:fss-disk}. On \cref{fig:error} we provide values of $C_{0.5}$ for this
-image (for variety of resolutions) and relative errors in $F_{ss}$
-(\cref{eq:error}) for both filters. It can be seen that $H$ gives twice the
-lower error than $H'$ when used for an image with $C_{0.5} \approx 0.82$.
-
-In short, for images of acceptable quality the $H'$ filter is superior. Images
-with insufficient resolution benefit from downscaling prior to correlation
-functions evalution \cite{Samarin} (and then again new filter will provide
-better results).
+worse than $H$ in points of discontinuity of $F_{ss}$ as can be seen on
+\cref{fig:fss-disk}. To explore such effects we appeal to the parameter
+$C_\alpha$ \cite{Samarin} developed to determine if an image is suitable for
+robust assessment of surface correlation functions. To introduce this parameter,
+consider a continuos band-limited signal $f(t)$ with support in frequency domian
+$[-\omega_0, \omega_0]$. The $L^2$ norm of this signal is
+\begin{equation}
+  \|f\| = \sqrt{\int_{-\omega_0}^{\omega_0} |\hat{f}(\omega)|^2 d\omega}
+\end{equation}
+where $\hat{f}(\omega)$ is a Fourier transform of $f(t)$. The idea behind the
+parameter is to determine how much low-frequency domain contributes to the total
+power of a signal. $C_\alpha$ parameter is defined as
+\begin{equation}
+  \begin{aligned}
+    C_\alpha &= \sqrt{\frac{\int_{-\alpha\omega_0}^{\alpha\omega_0}
+        |\hat{f}(\omega)|^2 d\omega}{\int_{-\omega_0}^{\omega_0}
+        |\hat{f}(\omega)|^2 d\omega}} \\
+    \alpha &\in [0, 1]
+  \end{aligned}
+  \label{eq:parameter}
+\end{equation}
+For two- and three-dimensional discrete images $f(t)$ is replaced with the input
+array $A$ minus its mean, integrals in \cref{eq:parameter} are replaced with
+double and triple sums respectively and $\omega_0$ is equal to the Nyquist
+frequency for the image. Our empirical criterion says that the image is suitable
+for evaluation of surface correlation functions if
+\begin{equation}
+  C_{0.5} > 0.97
+\end{equation}
+This criterion works for both filters $H$ and $H'$, but $H$ results in smaller
+error when $C_{0.5}$ is slightly less than 0.97. For example, consider images of
+a disk used for calculation of $F_{ss}$ on \cref{fig:fss-disk}. On
+\cref{fig:error} we provide values of $C_{0.5}$ for this image (for variety of
+resolutions) and relative errors in $F_{ss}$ (\cref{eq:error}) for both
+filters. It can be seen that $H$ gives twice the lower error than $H'$ when used
+for an image with $C_{0.5} \approx 0.82$. In short, for images of acceptable
+quality the $H'$ filter is superior.
 
@@
 
+\bibliography{pape}
+
 \appendix
@@
 
-\bibliography{paper}
 \end{document}

### 2023-05-19 paper.tex
Addition from Alexey Kh.

@@
 disciplines and applications: from material sciences
-\cite{Cecen,chen2022quantifying}, to rock \cite{ledesma2018effect} and soil
+\cite{Cecen,chen2022}, to rock \cite{ledesma2018effect} and soil
 physics \cite{Euras2012,PLoS_ONE,KarsaninaEJSS}, cosmology \cite{TakadaJain} and
@@
     CFs reach plateau;
-  \item comparison of different structures \cite{jiao2014chawla,EPL1,REVpaper},
+  \item comparison of different structures \cite{10.1063/1.4867611,EPL1,REVpaper},
     usually by computing L-2 norm difference between CFs for two or more images,
@@
   \item describing structural dynamics and evolution
-    \cite{chen2015dynamic,PLoS_ONE,xu2022correlation},
+    \cite{PhysRevE.92.023301,PLoS_ONE,xu2022correlation},
   \item extracting features for deep learning
@@
 
+Heterogeneous materials possess complex microstructures that play a crucial role
+in determining their macroscopic properties. To gain a deeper understanding of
+these materials and accurately estimate their properties, the consideration of
+higher-order correlation functions becomes essential. Several n-point
+correlation functions have been proposed and developed to effectively
+characterize disordered materials, ranging from second-order functions like the
+radial distribution function to higher-order functions involving correlations
+among three or more reference points
+\cite{Jiao_2012,PhysRevB.42.4453,10.1063/1.4865966}.
+
+While certain cases may be adequately addressed by two-point correlation
+functions \cite{LIU2015177,PhysRevE.77.031135}, situations demanding a higher
+degree of accuracy require the higher-order correlations to construct precise
+models. These higher-order correlation functions, although computationally
+demanding and analytically intricate, yield valuable information and estimations
+for various material properties. For instance, the effective diffusion
+coefficient, a crucial transport property, can be approximated by considering a
+three-point microstructural parameter expressed in terms of integrals over the
+three-point probability function \cite{Jiao_2012}. Furthermore, the combination
+of such functions can serve as target functions for reconstructing models of
+disordered materials, enhancing the accuracy of the reconstruction process
+\cite{JIAO20133370,PhysRevE.92.023301,10.1063/1.4867611,chen2016stochastic}.
+
+Analytical approaches have been proposed to compute only n-point functions $S_n$
+\cite{PhysRevB.42.4453,10.1063/1.4865966}. but studying n-point surface
+correlations faces lack of analytical solutions. Availability of analytical
+solutions for correlation functions holds significant importance and serves as a
+desirable benchmark for evaluating and validating numerical algorithms. However,
+a comprehensive computational framework for calculating higher-order correlation
+functions in heterogeneous media is still lacking. In their study
+\cite{malmir2018}, the authors proposed an algorithm for computing third-order
+correlation functions and compared its performance with existing analytical
+solutions and asymptotic cases. Although the algorithm demonstrates good
+performance for the computation of S3 functions, the authors themselves
+acknowledge that there is room for further improvement, particularly in the case
+of surface correlation functions. To address this limitation, they suggest
+employing a method similar to the one used in the work of Ma and Torquato
+\cite{ma2018SS}, where a digitized image is converted into a scalar field. In
+our current study, we advance beyond these findings and significantly enhance
+the numerical solution for the three-point correlation function of surfaces by
+incorporating and developing ideas from the work of Samarin et al
+\cite{Samarin}.
+
 In this contribution we continue to build upon foundational work of Ma and
@@
 values can be also used for anisotropic structures
-\cite{jiao2014chawla,EPL1}. These functions are defined for media with
+\cite{10.1063/1.4867611,EPL1}. These functions are defined for media with
 dimensionality of 2 and higher. $F_{sv}$ is a physical quantity inversely
@@
 
-\bibliography{pape}
+\bibliography{paper}
 

### 2023-08-03 scripts&data/calc-disk.jl
Replase Fss plots for disks

@@ -46,7 +46,7 @@ function do_it!()
     errors = Float64[]
     criteria = Float64[]
 
-    for side in 100:100:3100
+    for side in [100, 500, 1000, 2000, 3000]
         disk = draw_ball((side, side), R*side)
         println(side)
         ss = M.surf2(disk, false; periodic = true, filter = U.ConvKernel(7)) |> M.average_directions

### 2023-08-03 scripts&data/plot-ss-inset.py

@@ -15,11 +15,11 @@ for side in [100, 500, 1000, 2000, 3000]:
     legend = legend + [str(side)]
 
 xs = np.linspace(0, 0.5, 1000)
-plt.xlim([0, 0.1])
-plt.ylim([0, 6])
+plt.xlim([0.03, 0.06])
+plt.ylim([2.0, 2.4])
 plt.plot(xs, ss(xs, 0.0334), linewidth = 1.8)
 plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(legend + ['Theory'], loc = 3)
+#plt.legend(legend + ['Theory'])
 plt.xlabel('Correlation length $r$')
 plt.ylabel('$F_{ss}(r)$')
-plt.savefig('../images/fss-disk-7x7.png', bbox_inches = 'tight')
+plt.savefig('../images/fss-disk-7x7-inset.png', bbox_inches = 'tight')

### 2023-08-03 scripts&data/splice.sh

@@ -1,0 +1,21 @@
+#!/bin/sh
+
+arrow_head="path 'M 0,0 l -15,-5  +5,+5  -5,+5  +15,-5 z'"
+
+montage ../images/fss-disk-3x3.png ../images/fss-disk-3x3-inset.png -tile 2x1 -geometry +0+0 tmp.png
+convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+        -draw "rectangle 900,750 1600,830" \
+        -draw "line 1600,830 2700,1200" \
+        -draw "line 1600,750 2700,100" \
+        -draw "fill black translate 2700,1200 rotate 20 scale 2,2 $arrow_head" \
+        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
+        ../images/fss-disk-3x3-final.png
+
+montage ../images/fss-disk-7x7.png ../images/fss-disk-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
+convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+        -draw "rectangle 900,750 1600,830" \
+        -draw "line 1600,830 2700,1200" \
+        -draw "line 1600,750 2700,100" \
+        -draw "fill black translate 2700,1200 rotate 20 scale 2,2 $arrow_head" \
+        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
+        ../images/fss-disk-7x7-final.png

### 2023-08-03 scripts&data/calc-blob.jl
Update plots (ellipses)

@@ -13,7 +13,7 @@ const foo = [1 1 1; 1 -8 1; 1 1 1]
 U.extract_edges(array :: AbstractArray, filter :: FuckKernel, topology :: U.AbstractTopology) =
     abs.(imfilter(array, centered(foo / 6), U.edge2pad(topology)))
 
-for side in 500:500:3000
+for side in [500, 1000, 2000, 3000]
     data = load("field-$(side).pbm") .|> Gray |> BitArray;
     npzwrite("field-ss-$(side).npy",
              fftshift(M.surf2(data, false; periodic = true, filter = U.ConvKernel(7))) * side^2)

### 2023-08-03 scripts&data/compare-blob-inset.py

@@ -26,6 +26,7 @@ for side in [500, 1000, 2000, 3000]:
 plt.plot(phi, data_def[:, 0], linewidth = 1.5)
 plt.xlabel('$\phi$')
 plt.ylabel('$F_{ss}(R, \phi)$')
-plt.ylim([6, 36])
-plt.legend(legend + ['Precise'], loc = 1)
-plt.savefig('../images/fss-blob-7x7.png', bbox_inches = 'tight')
+plt.xlim([1.5, 3])
+plt.ylim([7, 10])
+#plt.legend(legend + ['Precise'])
+plt.savefig('../images/fss-blob-7x7-inset.png', bbox_inches = 'tight')

### 2023-08-03 scripts&data/splice.sh

@@ -2,20 +2,38 @@
 
 arrow_head="path 'M 0,0 l -15,-5  +5,+5  -5,+5  +15,-5 z'"
 
-montage ../images/fss-disk-3x3.png ../images/fss-disk-3x3-inset.png -tile 2x1 -geometry +0+0 tmp.png
-convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
-        -draw "rectangle 900,750 1600,830" \
-        -draw "line 1600,830 2700,1200" \
-        -draw "line 1600,750 2700,100" \
-        -draw "fill black translate 2700,1200 rotate 20 scale 2,2 $arrow_head" \
-        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
-        ../images/fss-disk-3x3-final.png
+#montage ../images/fss-disk-3x3.png ../images/fss-disk-3x3-inset.png -tile 2x1 -geometry +0+0 tmp.png
+#convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+#        -draw "rectangle 900,750 1600,830" \
+#        -draw "line 1600,830 2700,1200" \
+#        -draw "line 1600,750 2700,100" \
+#        -draw "fill black translate 2700,1200 rotate 20 scale 2,2 $arrow_head" \
+#        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
+#        ../images/fss-disk-3x3-final.png
 
-montage ../images/fss-disk-7x7.png ../images/fss-disk-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
+#montage ../images/fss-disk-7x7.png ../images/fss-disk-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
+#convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+#        -draw "rectangle 900,750 1600,830" \
+#        -draw "line 1600,830 2700,1200" \
+#        -draw "line 1600,750 2700,100" \
+#        -draw "fill black translate 2700,1200 rotate 20 scale 2,2 $arrow_head" \
+#        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
+#        ../images/fss-disk-7x7-final.png
+
+montage ../images/fss-blob-7x7.png ../images/fss-blob-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
[…]

### 2023-08-03 scripts&data/splice.sh
Update plots (blobs)

@@ -20,20 +20,38 @@ arrow_head="path 'M 0,0 l -15,-5  +5,+5  -5,+5  +15,-5 z'"
 #        -draw "fill black translate 2700,100 rotate -30 scale 2,2 $arrow_head" \
 #        ../images/fss-disk-7x7-final.png
 
-montage ../images/fss-blob-7x7.png ../images/fss-blob-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
-convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
-        -draw "rectangle 1350,1050 2350,1150" \
-        -draw "line 2350,1150 2700,1200" \
-        -draw "line 2350,1050 2700,100" \
-        -draw "fill black translate 2700,1200 rotate 10 scale 2,2 $arrow_head" \
-        -draw "fill black translate 2700,100 rotate -70 scale 2,2 $arrow_head" \
-        ../images/fss-blob-7x7-final.png
+#montage ../images/fss-blob-7x7.png ../images/fss-blob-7x7-inset.png -tile 2x1 -geometry +0+0 tmp.png
+#convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+#        -draw "rectangle 1350,1050 2350,1150" \
+#        -draw "line 2350,1150 2700,1200" \
+#        -draw "line 2350,1050 2700,100" \
+#        -draw "fill black translate 2700,1200 rotate 10 scale 2,2 $arrow_head" \
+#        -draw "fill black translate 2700,100 rotate -70 scale 2,2 $arrow_head" \
+#        ../images/fss-blob-7x7-final.png
+
+#montage ../images/fss-blob-3x3.png ../images/fss-blob-3x3-inset.png -tile 2x1 -geometry +0+0 tmp.png
+#convert tmp.png -stroke black -strokewidth 3 -fill none -gravity center \
+#        -draw "rectangle 1350,1050 2350,1150" \
+#        -draw "line 2350,1150 2700,1200" \
+#        -draw "line 2350,1050 2700,100" \
+#        -draw "fill black translate 2700,1200 rotate 10 scale 2,2 $arrow_head" \
+#        -draw "fill black translate 2700,100 rotate -70 scale 2,2 $arrow_head" \
+#        ../images/fss-blob-3x3-final.png
 
 montage ../images/fss-blob-3x3.png ../images/fss-blob-3x3-inset.png -tile 2x1 -geometry +0+0 tmp.png
[…]

### 2023-08-04 paper.tex
Replase Fss plots for disks
Update plots (ellipses)
Update plots (blobs)
Last edits from Kirill

@@
   propose a better edge detection filter that allowed to improve the quality of
-  assessment of surface correlation functions, both surface-surface and
+  assessment of surface correlation functions, both surface-surface ($F_{ss}$) and
   surface-void ($F_{sv}$), for digital images. The code for continuous and
@@
 somewhat crude approximate approaches \cite{seaton1986spatial} were developed
-until Ma and Torquato laid foundation for such a robust computational
+until Ma and Torquato laid foundation for a robust computational
 methodology \cite{ma2018SS}. They proposed an elegant solution for infinite
@@
 closer to analytical solutions for overlapping disks/spheres and to suppress
-perturbation, in particular for $F_{ss}$. The perturbation in Ma and Torquato
+noise, in particular for $F_{ss}$. The noise in Ma and Torquato
 method resulted from $1/cos(\theta)$ computations during random line segment
@@
 solutions and asymptotic cases. Although the algorithm demonstrates good
-performance for the computation of S3 functions, the authors themselves
+performance for the computation of $S_3$ functions, the authors themselves
 acknowledge that there is room for further improvement, particularly in the case
@@
 our current study, we advance beyond these findings and significantly enhance
-the numerical solution for the three-point correlation function of surfaces by
-incorporating and developing ideas from the work of Samarin et al
-\cite{Samarin}.
-
-In this contribution we continue to build upon foundational work of Ma and
+the numerical solution for the three-point correlation function of surfaces.
+
+All in all, we continue to build upon foundational work of Ma and
 Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{Samarin} to
@@
 values can be also used for anisotropic structures
-\cite{10.1063/1.4867611,EPL1}. These functions are defined for media with
-dimensionality of 2 and higher. $F_{sv}$ is a physical quantity inversely
+\cite{10.1063/1.4867611,EPL1}. $F_{sv}$ is a physical quantity inversely
 proportional to length and $F_{ss}$ is inversely proportional to surface
@@
 \end{equation}
-This function is defined for media with dimensionality 3 or higher and is a
-physical quantity inversely proportional to volume. SI units for $F_{sss}$ are
-$m^{-3}$, but relative units can be used in practice. For three-dimensional media
+SI units for $F_{sss}$ are $m^{-3}$, but relative units can be used in practice. For three-dimensional media
 $F_{sss}$ is a function of six scalar arguments:
@@
 consider a continuos band-limited signal $f(t)$ with support in frequency domian
-$[-\omega_0, \omega_0]$. The $L^2$ norm of this signal is
+$[-\omega_0, \omega_0]$. The $L^2$ norm of this signal is:
 \begin{equation}
@@
 parameter is to determine how much low-frequency domain contributes to the total
-power of a signal. $C_\alpha$ parameter is defined as
+power of a signal. $C_\alpha$ parameter is defined as:
 \begin{equation}
@@
 frequency for the image. Our empirical criterion says that the image is suitable
-for evaluation of surface correlation functions if
+for evaluation of surface correlation functions if:
 \begin{equation}
@@
 
+\section{Acknowledgements}
+This research was supported by the Russian Science Foundation grant 23-74-00061. Collaborative effort of the authors is within the FaT iMP 
+(Flow and Transport in Media with Pores) research group (www.porenetwork.com). We thank our colleague Konstantin Romanenko for suggestions 
+and administrative work.
+
 \bibliography{paper}

### 2023-08-21 paper.tex
Forgot apostrophe
Weather -> whether

@@
   \Comment{Apply DFT to $A'$.}
-  \State \textbf{return} $F^{-1}[ |\hat{A}|^2 / N]$
+  \State \textbf{return} $F^{-1}[ |\hat{A'}|^2 / N]$
   \Comment{$N$ is a number of elements in $A$}
@@
   \Comment{Apply DFT to $V$.}
-  \State \textbf{return} $F^{-1}[ \hat{A}\overline{\hat{V}} / N]$
+  \State \textbf{return} $F^{-1}[ \hat{A'}\overline{\hat{V}} / N]$
   \Comment{$N$ is a number of elements in $A$}
@@
 analytic solutions. Although we obtained good results in the cases of
-overlapping balls and disks, weather our algorithm performs with the same high
-accuracy in general is still an open question. In this section we develop a
+overlapping balls and disks, whether or not our algorithm performs with the same
+high accuracy in general is still an open question. In this section we develop a
 universal test case and novel exact algorithm for calculation of $F_{ss}$ and
@@
   \subfigure[$3\times 3$ kernel $H$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-disk-3x3.png}
+    \includegraphics[width=\linewidth]{images/fss-disk-3x3.png}
     \label{fig:fss-disk-3x3}}
-  \hfill
+  \vskip\baselineskip
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-disk-7x7.png}
+    \includegraphics[width=\linewidth]{images/fss-disk-7x7.png}
     \label{fig:fss-disk-5x5}}
@@
     $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
-    $3100\times 3100$.}
+    $3000\times 3000$.}
   \label{fig:fss-disk}
@@
   \subfigure[$3\times 3$ kernel $H$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
+    \includegraphics[width=\linewidth]{images/fss-blob-3x3.png}
     \label{fig:fss-blob-3x3}}
-  \hfill
+  \vskip\baselineskip
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-blob-7x7.png}
+    \includegraphics[width=\linewidth]{images/fss-blob-7x7.png}
     \label{fig:fss-blob-5x5}}
@@
   \subfigure[$3\times 3$ kernel $H$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-3x3.png}
+    \includegraphics[width=\linewidth]{images/fss-ellipses-3x3.png}
     \label{fig:fss-ellipses-3x3}}
-  \hfill
+  \vskip\baselineskip
   \subfigure[$7\times 7$ kernel $H'$]{
-    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-7x7.png}
+    \includegraphics[width=\linewidth]{images/fss-ellipses-7x7.png}
     \label{fig:fss-ellipses-5x5}}
